### 2013-06-20 trunk/network-science/paper.tex

\documentclass[a4paper,twocolumn,10pt]{article}
\usepackage{multicol}
\usepackage{listings}
\usepackage{fourier}
\usepackage{amsmath}

\usepackage{tikz}
\tikzstyle{every picture}+=[remember picture]
\usetikzlibrary{arrows,decorations.pathreplacing,decorations.markings}
\usepackage{listings}
\lstset{
	numbers=left,
	basicstyle=\small\ttfamily,
	numberstyle=\it\scriptsize\sffamily,
	keywordstyle=\bf,
	commentstyle=\color{red!50!green!50!blue!50},
	frame=single,
	%breaklines=true,
}

\usepackage{geometry}
\geometry{left=0.7cm,right=0.7cm,top=0.7cm,bottom=1.3cm}
%\linespread{1.0}

\AtBeginDocument{%
	\setlength\abovedisplayskip{3pt}
	\setlength\belowdisplayskip{3pt}
}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{5pt}{5pt}
\titlespacing{\subsection}{0pt}{5pt}{5pt}
\titlespacing{\subsubsection}{0pt}{5pt}{3pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
\newcommand{\ang}[1]{\left\langle {#1} \right\rangle}
\newcommand{\lc}{\left(}
\newcommand{\rc}{\right)}
\newcommand{\parentheses}[1]{\left({#1}\right)}
\newcommand{\pte}[1]{\left({#1}\right)}
\newcommand{\labs}{\left|}
\newcommand{\rabs}{\right|}
\newcommand{\abs}[1]{\left|{#1}\right|}
\newcommand{\op}{\operatorname}
\newcommand{\E}{\operatorname{E}}
\newcommand{\spt}{\operatorname{support}}
\newcommand{\mA}{\mathcal{A}}
\newcommand{\mB}{\mathcal{B}}
\newcommand{\mC}{\mathcal{C}}
\newcommand{\mD}{\mathcal{D}}
\newcommand{\mE}{\mathcal{E}}
\newcommand{\mJ}{\mathcal{J}}
\newcommand{\mK}{\mathcal{K}}
\newcommand{\mL}{\mathcal{L}}
\newcommand{\mM}{\mathcal{M}}
\newcommand{\mU}{\mathcal{U}}
\newcommand{\mV}{\mathcal{V}}
\newcommand{\mW}{\mathcal{W}}
\newcommand{\mX}{\mathcal{X}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\bZ}{\mathbb{Z}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\bC}{\mathbb{C}}
\newcommand{\uge}{\succcurlyeq}
\newcommand{\Tr}{\op{Tr}}
\newcommand{\dd}{\mathrm{d}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%\begin{multicols}{3}
\section*{\textsc{Net Science}'s Sheet {\large by Feng Qiwei}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Biblographic Coupling}
	B.C. of $(i,j)$ is $\#$ of other nodes to which both $i,j$ point:
	$B=A^T A$.

\subsection{Degree}
	\[
		k_i=\# \textrm{ of edges connected to }i, \\
	\]
	\[
		\rho(G)=\frac{m}{\binom{n}{2}} = \frac{c}{n-1}\textrm{ where }c=\ang{k_i}.
	\]

\subsection{Transitivity}
	\[
	\textrm{clustering cofficient} =
		\frac{\#\textrm{ closed paths of len 2}} {\#\textrm{ paths of len 2}}, \\
	\]
	\[
	\textrm{local c.c.} =
		\frac{\#\textrm{ pairs of connected neighbors}} {\#\textrm{ pairs of neighbors}}.
	\]

\subsection{Centrality}
	\subsubsection{Eigenvector}
		Let $x(t)=A^t x(0)$ where $x(0)=\sum_i c_i v_i$,
		then $x(t)=\sum_i c_i \lambda_i^t v_i=\lambda_1^t \sum_i c_i (\lambda_i/\lambda_1)^tv_i$.
		For $t\to\infty$, know $(\lambda_i/\lambda_1)^t\to 0$ so $x(t)\to c_1\lambda_1^t v_1$, so
		\[
			\pte{Ax = \lambda_1 x} \Longrightarrow
			\pte{x_i=\lambda_1^{-1} \sum_j A_{ij} x_j}.
		\]
		\textbf{Prob.}
		Only vertices in out-component(s) of SCC of two or more vertices can have
			non-zero E.C..

	\subsubsection{Katz}
		\[
			\pte{x_i = \alpha\sum_j A_{ij} x_j + \beta}
			\Longleftrightarrow
			\pte{x=\alpha Ax+\beta 1}.
		\]
		Set $\beta=1$ (should have $\alpha<\lambda_1^{-1}$):
			$x=(I-\alpha A)^{-1} \cdot 1$.

	\subsubsection{Pagerank}
		\[
			\pte{x_i = \alpha \sum_j A_{ij} \frac{x_j}{k_j^{out}} + \beta}
			\Longleftrightarrow
			\pte{x=D(D-\alpha A)^{-1}\cdot \beta1}.
		\]

	\subsubsection{Hubs and Authorities}
		\[
			x=\alpha A y, y=\beta A^T x.
		\]

	\subsubsection{Closeness}
		\[
			d_{ij}=\textrm{ len of SP bet. $i$ and $j$},
			\textrm{~~~~}
			l_i=\frac{1}{n-1} \sum_{j\neq i} d_{ij},
			\textrm{~~~~}
			c_i=\frac{1}{l_i}.
		\]

	\subsubsection{Betweeness}
		\[
			n_{s,t}^i=\#\textrm{ of SP $s\to t$ through $i$},
			\textrm{~~~~}
			g_{s,t}=\#\textrm{ of SP $s\to t$},
		\] \[
			\textrm{B.C. of $i$}=x_i=\sum_{s,t} \frac{n_{s,t}^i}{g_{s,t}}.
		\]

	\subsubsection{Flow}
		\[
			x_i = \sum_{s,t} m_{s,t},
			\textrm{~~~~}
			m_{s,t}=\textrm{ flow through $i$ in a max $s$-$t$ flow}.
		\]

\subsection{Similarity}
	\textbf{Structral s.:} if share many of the same neighbors.
	\textbf{Regular s.:} if neighbors are similar.

	\subsubsection{Consine}
		\[
			\sigma_{ij} = \frac{\sum_k A_{ik} A_{kj}} {\sqrt{\sum_k A_{ik}^2}\sqrt{\sum_k A_{kj}^2}}
			=\textrm{(in unweight G)}=\frac{n_{ij}}{\sqrt{k_i k_j}}.
		\]
	\subsubsection{Pearson Coefficients}
		\[ \begin{split}
			\op{cov}(A_i,A_j)
			&= \#\textrm{common neighbors} - \#\textrm{exp. com. neighs} \\
			&= \sum_k A_{ik} A_{jk} - \frac{k_i k_j}{n} 
			= \sum_k \pte{A_{ik}-\ang{A_i}} \pte{A_{jk}-\ang{A_j}}, \\
		\end{split} \]
		\[ \begin{split}
			r_{ij}
			&= \textrm{standard Pearson corellation coefficient} \\
			&= \frac{\sum_k \pte{A_{ik}-\ang{A_i}} \pte{A_{jk}-\ang{A_j}}}
				{\sqrt{\pte{A_{ik}-\ang{A_i}}^2} \sqrt{\pte{A_{jk}-\ang{A_j}}^2}}. \\
		\end{split} \]

\subsection{Homiphily and Assortive Mixing}
	\subsubsection{A.M. by Enumerative Characteristics}
		\[ \begin{split}
			Q &= \textrm{modularity} \\
			&= \frac{1}{m} \pte{\#\textrm{same type edges} - \#\textrm{exp. same type edges}} \\
			&= \frac{1}{2m} \sum_{ij} \pte{A_{ij} - \frac{k_i k_j}{2m}} \delta(c_i,c_j)
			=\sum_r e_{rr} - a_r^2. \\
			e_{rs} &= \frac{1}{2m} \sum_{ij} A_{ij} \delta(c_i,r) \delta(c_j,s), \\
			a_r &= \frac{1}{2m} \sum_i k_i \delta(c_i,r). \\
		\end{split} \]

	\subsubsection{A.M. by Scalar Characteristics}
		\[ \begin{split}
			r &= \textrm{assortativity coefficient} \\
			&= \frac{\textrm{covariances over nodes}}{\textrm{cov. in perfectly mixed network}} \\
			&= \frac{\sum_{ij} \pte{A_{ij} - k_i k_j / 2m} x_i x_j}
				{\sum_{ij} \pte{k_i \delta_{ij} - k_i k_j /2m} x_i x_j}.
		\end{split} \]

\subsection{Power Law Distribution}
	\[
		p_k = C k^{-\alpha} \textrm{ where $\alpha$ in $[2,3]$ are typical}.
	\]
	\[
		P_k = \sum_{i=k}^\infty p_i
			\approx C \int_k^\infty x^{-\alpha} \dd x
			=\frac{C}{\alpha-1} k^{-(\alpha-1)}.
	\]
	\[ \begin{split}
		\alpha &= 1 + N\left[ \sum_i \ln \frac{k_i}{k_{min} - 1/2} \right]^{-1}, \\
		\sigma &= \sqrt{N} \left[ \sum_i \ln \frac{k_i}{k_{min} - 1/2} \right]^{-1}
			= \frac{\alpha-1}{\sqrt{N}}.
	\end{split} \]

\subsection{Graph Laplacian}
	Diffusion $\frac{\dd \psi_i}{\dd t}=c \sum_j A_{ij} (\psi_j-\psi_i)
		=c\sum_j(A_{ij}-\delta_{ij}k_i)\psi_j
		\Longrightarrow \frac{\dd \psi}{\dd t}=c(A-D)\psi$.
	Define $L=D-A$, then $\frac{\dd \psi}{\dd t}+cL\psi=0$.
	Need to solve $\psi(t)=\sum_i a_i(t) v_i$.
	Have $\sum_i (\frac{\dd a_i}{\dd t} + c\lambda_i a_i) v_i = 0$,
	then $\frac{\dd a_i}{\dd t} + c \lambda_i a_i=0$ since $v_i\perp v_j$.
	So $a_i(t)=a_i(0) e^{-c\lambda_i t}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Big Things}

\subsection{Random Graph}
	\subsubsection{Poisson Random Graph}
		Poisson r. g. $G(n,p)$:
		$n$ nodes where $\forall u,v$, $\Pr[\exists (u,v)\in G]=p$:
		\begin{itemize}
			\item mean $\#$ edges: $\binom{n}{2} p$;
			\item avg. deg.: $(n-1)p=c$;
			\item deg. distr.: $p_k=\binom{n-1}{k} p^k (1-p)^{n-1-k}$,
				and for large $n$: $p_k=e^{-c} \frac{c^k}{k!}$ (Poisson deg. distr.);
			\item cluster coefficient $= p = \frac{c}{n-1} \to 0$.
		\end{itemize}

	\subsubsection{Giant Component}
		$u$: fraction of vertices that do \textbf{NOT} belong to the giant $T$.
		If $i\notin T$, then $\forall j$, either
		\begin{itemize}
			\item $i$ is not connected to $j$: $1-p$;
			\item $i$ is connected to $j$ but $j\notin T$: $pu$.
		\end{itemize}
		Total: $1-p+pu$. Probability that $i\notin T$ is
		\[
			u=(1-p+pu)^{n-1}=\pte{1-\frac{c}{n-1}(1-u)}^{n-1},
		\]
		%= (n-1) \ln\pte{1-\frac{c}{n-1}(1-u)}
		\[
			\ln u 
			\approx -(n-1) \frac{c}{n-1} (1-u) = -c(1-u)
		\]
		\[
			\Longrightarrow u=e^{-c(1-u)}
			\Longrightarrow 1-u=S=1-e^{-cS}.
		\]
		Phase transition takes place when
		\[
			\left.\frac{\dd}{\dd S} \pte{1-e^{-cS}} = c e^{-cS} = 1 \right|_{S=0}
			\Longrightarrow c=1.
		\]
		Core $C(Q)$ and periphery $P(Q)$: $s=|C(Q)|+|P(Q)|$.
		A node in $P(Q)$ has $p(n-s)\approx c$ neighbors outside, so
		\[
			P(Q') \approx c P(Q), C(Q') = Q.
		\]
		If $c>1$, periphery grows; if $c<1$, it shrinks.

	\subsubsection{Small Components}
		$\pi_s$: prob that a randomly selected node belongs to a small component of size $s$.
		Fraction of nodes not in the giant: $\sum_{s=0}^\infty \pi_s = 1-S$.

		Observation: s.c. are trees.
		Consider tree of $s$ nodes.
		Remain place of edge: $\binom s 2 - (s-1) = \frac 1 2 (s-1)(s-2)$,
			so exp $\#$ non-tree edges: $\frac 1 2 (s-1)(s-2) p =
			\frac 1 2 (s-1)(s-2) c / (n-1) \to 0$,
			if $s$ increase slowly than $\sqrt n$.

		Consider $i$'s neighbors $n_1,...,n_k$ with component size $s_1,...,s_k$.
		$P(s|k)$: $i$ belongs to component of size $s$.
		\[
			P(s|k)=\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j).
		\]
		Know $\pi_s = \sum_{k=0}^\infty p_k P(s|k)$.
		(Generating function now!)
		Let $h(z)=\sum_{s=1}^\infty \pi_s z^s$,
			then $\pi_s=\left. \frac{1}{s!} \frac{\dd^s h}{\dd z^s} \right|_{z=0}$.
		Consider $h(z)$:
		\[ \begin{split}
			h(z) &= \sum_{s=1}^\infty z^s \sum_{k=0}^\infty p_k
			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j) \\
			&= \sum_{s=1}^\infty z^s e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j) \\
			&= e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j}} z^{1+\sum_j s_j} \\
			&= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
			\pte{\prod_{j=1}^k \pi_{s_j} z^{s_j}} \\
			&= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
			\pte{\sum_{s=1}^\infty \pi_{s} z^{s}}^k 
			= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!} h^k(z) 
			= z e^{c(h(z)-1)}.
		\end{split} \]

		No closed-form solution for $h(z)$.
		$\ang{s}=\frac{\sum_s s\pi_s}{\sum_s \pi_s}=\frac{h'(1)}{1-S}$.
		Know
		\[
			h'(z)=e^{c(h(z)-1)} + czh'(z)e^{c(h(z)-1)} = \frac{h(z)}{z} + ch(z)h'(z)
		\]
		\[
			\Longrightarrow h'(z)=\frac{h(z)}{z(1-ch(z))}.
		\]
		$h(1)=\sum_s \pi_s=1-S \Longrightarrow \ang{s}=\frac{1}{1-c+cS}$.
		If $c<1$, no giant so $\ang{s}=\frac{1}{1-c}$.

		$n_s$: $\#$ components of size $s$. $\pi_s = s n_s/n$.
		Avg size of component: $$R=\frac{\sum_s s n_s}{\sum_s n_s}
			= \frac{n \sum_s \pi_s}{n \sum_s \pi_s / s}
			= \frac{1-S}{\sum_s \pi_s/s}.$$
		Noting that
		\[
			\int_0^1 \frac{h(z)}{z} \dd z = \sum_{s=1}^\infty \int_0^1 z^{s-1} \dd z
			= \sum_{s=1}^\infty \frac{\pi_s}{s}.
		\]
		Have $\frac{h(z)}{z} = (1-ch(z)) \frac{\dd h}{\dd z}$,
			so $$\sum_{s=1}^\infty \frac{\pi_s}{s}
			=\int_0^1 (1-ch(z)) \frac{\dd h}{\dd z} \dd z
			=\int_0^{1-S}(1-ch) \dd h = 1-S-\frac 1 2 c(1-S)^2.$$
		(Upper integration limit $ = h(1)= 1-S$.)
		Finally $R=\frac{2}{2-c+cS}$.
		(\textbf{NOTE:}
		$G(n,p)$ is connected if $p(n)=\frac{\log n}{n}$,
			then diameter $D=A+\frac{\ln n}{\ln c}$.)

	\subsubsection{Configuration Model}
		Specify degree distr $p$, randomly pick endpoints to form edges.

\subsection{Preferential Attachment}
	Each new paper cite $c$ old papers randomly:
	\[ \begin{split}
		p_q(n) &= \textrm{fraction of nodes with deg $q$}, \\
		q_i &= \textrm{in-degree of node $i$}, \\
	\end{split} \]
	\[
		\Pr[i\textrm{ get citation}] = \frac{q_i+a}{\sum_j (q_j+a)} = \frac{q_i+a}{n(c+a)}. \\
	\]
	\[
		\E[\textrm{new cites deg $q$ nodes}]
			=n p_q(n) c \frac{q+a}{n(c+a)} = \frac{c(q+a)}{c+a} p_q(n).
	\]
	\subsubsection{Master Equation}
		\[ \begin{split}
			(n+1)p_q(n+1)&=np_q(n)
				+\frac{c(q-1+a)}{c+a}p_{q-1}(n)- \frac{c(q+a)}{c+a}p_q(n) \\
			(n+1)p_0(n+1)&=np_0(n)+1-\frac{ca}{c+a}p_0(n).
		\end{split} \]
		\[
			n\to\infty\Longrightarrow
			p_0=\frac{1+\frac{a}{c}}{a+1+\frac{a}{c}},
			p_q=\frac{q+a-1}{q+a+1+\frac{a}{c}}p_{q-1},
		\]
		\[
			\Longrightarrow
			p_q=\frac{(q+a-1)(q+a-2)\cdots a}{(a+a+1+\frac{a}{c})\cdots(a+1+\frac{a}{c})}.
		\]
		% TODO: Gamma Beta
		For large $q$,
			$p_q\sim (q+a)^{-\alpha}$ or simply $p_q\sim q^{-\alpha}$,
			where $\alpha=2+\frac{a}{c}$.

	\subsubsection{Mean-Field Approximation}
		One link with $p$ choose uniform, $q=1-p$ choose by P.A..
		\[ \begin{split}
			x_i(t) &= \textrm{in-degree of $i$ at time $t$ with $x_i(i)=0$}, \\
			\Delta_t &= \E[x_i(t+1)-x_i(t)]  = \frac{p}{t} + \frac{(1-p)x_i(t)}{t}.
		\end{split} \]
		Consider a deterministic process in which a nodes degree increased by exact $\Delta_t$.
		Find distribution of expected degrees.
		\[
			d_i(i) = 0, \frac{\partial d_i(t)}{\partial t} = \frac{p}{t} + \frac{(1-p)d_i(t)}{t}.
		\]
		\[
			\Longrightarrow \int \frac{1}{p+q d_i} \frac{\partial d_i}{\partial t} \dd t = \int \frac{1}{t} \dd t \\
		\] \[
			\Longrightarrow \ln(p+q d_i) = q \ln t + c \\
		\] \[
			\Longrightarrow p+q d_i = A t^q, \\
		\] \[
			\textrm{set $d_i(i)=0$,}\Longrightarrow d_i(t) = \frac{p}{q}\pte{\pte{\frac{t}{i}}^q-1}.
		\]
		$i_t(k)$: node with expected degree exactly $k$ at time $t$:
		\[
			d_{i_t(k)}(t) = k = \frac{p}{q}\pte{\pte{\frac{t}{i_t(k)}}^q-1}
			\Longrightarrow
			i_t(k)=t\pte{\frac{p}{q}k+1}^{-\frac{1}{q}}.
		\]
		Fraction of nodes with degree $>k$:
			$F_k(t) = \pte{\frac{q}{p}k+1} ^ {-\frac{1}{q}}$,
		\[
			\Longrightarrow
			p_k=-\frac{\partial F_k}{\partial k}
			=\frac{1}{p}\pte{\frac{q}{p}k+1}^{-1-\frac{1}{q}}
			\sim k^{-\pte{1+\frac{1}{q}}}.
		\]

\subsection{Small World}
	Each node is connected with all neighbors of distance $\le c/2$.
	For $nc/2$ times pick random pair and add shortcut w.p. $p$.

	\subsubsection{Degree Distribution}
		\[
			k_i = c + s_i = c + (\#\textrm{shortcuts attacked to $v_i$}).
		\]
		There are $ncp$ endpoints of shortcuts. $s_i$ is Poisson distributed
			with mean $cp$:
		\[
			p_s = e^{-cp}\frac{(cp)^s}{s!} \Longrightarrow
			p_k = e^{-cp}\frac{(cp)^{k - c}}{(k - c)!}, \textrm{ for }k \ge c.
		\]

	\subsubsection{Clustering Coefficient}
		$C=(\#\textrm{triangles}\times 3)/(\#\textrm{connected tripes})$.
		\begin{enumerate}
			\item $\#$ triangles
			\begin{enumerate}
				\item in ring: $n\binom{c/2}{2}=\frac{1}{4}nc(\frac{c}{2} - 1)$.
				\item due to shortcuts:
					prob $u,v$ connected by shortcut$=\frac{ncp/2}{n(n-1)/2}\approx \frac{cp}{n}$.
					A shortcut complete a triangle for $u,v$ with dist $\frac{c}{2}\sim c$,
						$\#$ of such $u,v$ is proportional to $n$.
					$\Longrightarrow \sim n\cdot \frac{cp}{n} = cp =$
					const $\to$ ignore.

			\end{enumerate}
			\item $\#$ connected tripes
			\begin{enumerate}
				\item in ring: $n\binom{c}{2}=\frac{1}{2}nc(c - 1)$.
				\item through shortcuts: $(ncp/2)\times 2\times c$.
				\item through pairs of shortcuts: for node with $m$ shortcuts,
					has $\binom{m}{2}$ triples.
					Let $m=cp$ (mean of Poisson distr) then total triples
					$=(nc^2p^2)/2$.
			\end{enumerate}
		\end{enumerate}
		\[
			C=\frac{3(c-2)}{4(c-1)+8cp+4cp^2}.
		\]

	\subsubsection{Path length}
		No exact expr for mean distance in WS model.
		Consider $c=2$. Let $l=$ average len of SP.
		$s=\#$ shortcuts.

		Avg dist between shortcuts on ring $\tau=\frac{n}{2s}$
			$\Longrightarrow$ $n,\tau$ completely specify the model.

		Consider dimensionless $\frac{l}{n}$.
		$\frac{l}{n}=F(\frac{n}{\tau})=F(2s)$
		($F$: universal).
		If density of shortcuts is low then for general $c$:
		$l=\frac{2n}{c} F(2s) = \frac{n}{c} f(ncp)$.
		Simulate $f$:
		\[
			f(x) = \frac{2}{\sqrt{x^2+4x}}\op{tanh}^{-1}\sqrt{\frac{x}{x+4}}
		\]
		\[
			\Rightarrow x\to\infty
			\Rightarrow f(x) = \frac{\ln x}{x}
			\Rightarrow l = \frac{\ln(ncp)}{c^2p}.
		\]

	\subsubsection{Milgram}
		Short paths exists and can be found efficiently in decentralized way.
		WS model: $c=2$; $K=$ nodes with dist $\le\sqrt{n}$ of $t$.
		$\Pr[\textrm{a shortcut points into $K$}]=2/\sqrt{n}$
			$\to$ need at least $\sqrt{n}/2$ steps into $K$.
		Crossing $K$ step-by-step at least $\sqrt{n}/2$ steps.
		Thus need $\Omega(\sqrt n)$ steps.

	\subsubsection{Kleinberg}
		Choose shortcuts s.t.
			$\Pr[\textrm{shortcut between $u,v$ at dist $r$}]=\kappa r^{-\alpha}$.
		Choose shortcut len from distribution.
		Place edge randomly in network.
		Total prob that shortcut between two nodes is $p\kappa r^{-\alpha}$.
		Normalization const $\kappa$:
		\[
			\kappa\sum_{r = 1}^{\frac{1}{2}(n - 1)}r^{-\alpha} = 1.
		\]
		We can approximate the sum:
		\[
			\sum\limits_{r= 1}^{\frac{1}{2}(n - 1)} r^{-\alpha}
			\approx\int_{1}^{\frac{1}{2}(n - 1)} r^{-\alpha}\dd r
			+\frac{1}{2}+\frac{1}{2}\pte{\frac{1}{2}(n - 1)}^{-\alpha},
		\]
		where $\int_{1}^{(n - 1)/2} r^{-\alpha}\dd r=((n-1)/2)^{1-\alpha}/(1-\alpha)$.
		For $n\to\infty$:
		\[
			\kappa\approx\left\{\begin{array}{ll}
				(1-\alpha)(\frac{1}{2}n)^{\alpha - 1} &\alpha<1\\
				\ln^{-1}(\frac{1}{2}n) &\alpha = 1\\
				\frac{2(\alpha-1)}{\alpha+1} &\alpha>1
			\end{array}\right..
		\]
		Divide nodes into classes that $C_k$ consists of $v_i$ with
			$2^{k-1}\le d(v_i,t)<2^k$.
		Nodes in $C_0,...,C_{k-1}$:
			$\sum_{m=0}^{k-1}n_m = \sum_{m=0}^{k-1}2^m = 2^k-1 > 2^{k-1}$.
		All these are at most a dist $3 * 2^k < 2^{k+2}$ from $v_{\mathrm{cur}}$ in $C_k$.
		Prob of having a shortcut to one of the nodes:
		\[
			p\kappa 2^{-(k+2)\alpha}*2^{k-1}=p\kappa 2^{k-1-(k+2)\alpha}.
		\]
		If $v_{\mathrm{cur}}$ has no shortcut, pass msg to neighbor.
		Exp $\#$ moves until find a shortcut to $C_0,...,C_{k-1}$ is 
		\[
			\frac{1}{p\kappa} 2^{2\alpha+1} 2^{(\alpha-1)k}.
		\]
		In wrost case msg goes through all classes:
		\[
			l \le \frac{1}{p\kappa}*2^{2\alpha+1}*
				\sum_{k=0}^{\log(m+1)}2^{(\alpha-1)k}
			= \frac{1}{p\kappa}*2^{2\alpha+1}
				\frac{(2(n+1))^{\alpha-1}-1}{2^{\alpha-1}-1}.
		\]
		Plugging the value of $\kappa$ for $n\to\infty$:
		\[
			l=\left\{\begin{array}{ll}
				A n^{1-\alpha} &\alpha<1\\
				B \log^2 n &\alpha = 1\\
				C n^{\alpha-1} &\alpha>1
			\end{array}\right..
		\]

\subsection{Stable Outcome}
	\subsubsection{Nash Bargain Solution}
		$A$ and $B$ with outside option $x$ and $y$.
		If $x+y>1$ then no agreement possible.
		If $x+y\le 1$ then has surplus $s=1-x-y$.

		NBS: devide surplus evenly.

	\subsubsection{Stable Outcome}
		$G=(V,E)$, edge weight $w:E\to R^+$. Each $v\in V$ is a player.

		\textbf{Outcome}: matching $M$ among players and vector $x$
			describing each players payoff.
			$\forall(u,v)\in M$, $x_u+x_v=w_{u,v}$; $\forall u\notin M$, $x_u=0$.

		\textbf{Stable outcome}: outcome with no unstable edge.

		\textbf{Balanced outcome} (generalization of NBS):
			$\forall (u,v)\in M$, split of money represents the NBS
				for $u,v$ given the best outside option for $u,v$
				provided by values in the rest of the network.

		$\to$ A balanced outcome exists iff a stable outcome exists.

		$\to$ A balanced outcome can be computed in poly-time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Unknown}

\subsection{Cascades}
	\subsubsection{Network Effects \textsc{(Things That I Cannot Understand!)}}
		Decisions: $\{R,A\}$;
		States: $\{G,B\}$ w.p. $\{p,1-p\}$.
		Payoffs: $0$ for reject and $(G ? v_g>0 : v_b<0)$ for accept
			($p v_g + (1-p) v_b = 0$).

		Signals: gets a private signal before decision:
			$H$ (high sig) = "accepting is good",
			$L$ (low) = "..is bad".
			$\Pr[H|G]=\Pr[L|B]=q>1/2$, 
			$\Pr[L|G]=\Pr[H|B]=1-q$.

		Know sequence $S$ of independently generated signals.
		$a=\# H\in S$, $b=\# L\in S$.
		\[
			\Pr[G|S]=\frac{\Pr[G]\Pr[S|G]}{\Pr[S]}
				=\frac{pq^a(1-q)^b}{pq^a(1-q)^b+(1-p)(1-q)^aq^b}.
		\]
		For $a>b$, $\Pr[G|S]>p$.
		For $a<b$, $\Pr[G|S]<p$.
		For $a=b$, $\Pr[G|S]=p$.

	\subsubsection{Economy with Network Effect}
		When $z$-fraction of customers buy, ceservation price of $x$ is $r(x)f(z)$.
		$r$: intrinsic interest ($r(1)=0$).
		$f$: benefit (increasing in $z$, $f(0)=0$).

		Everyone expect $z=0$ $\to$ R.P.$=0<p$ $\to$ no one will buy.
		Everyone expect $z\in(0,1)$ $\to$ $0..z$ will buy
			$\to$ R.P.$=r(z)f(z)=p$.
		Stability: strong equlibrium OR tripping point.

		If $[0,\hat z]$ buy, then $r(\hat z)=\frac{p^*}{f(z)} \Longrightarrow
			\hat z=r^{-1}\pte{\frac{p^*}{f(z)}}$.
		If $z\ge 0$ then $\hat z=g(z)$ where $g(z)=r^{-1}\pte{\frac{p^*}{f(z)}}$
			for $\frac{p^*}{f(z)}\le r(0)$, $=0$ otherwise.

		NOW, consider $f(0)>0$. Let $r(x)f(z)=(1-x)(1+az^2)$.
		If exp $\hat z$ then $g(z)=r^{-1}\pte{\frac{p^*}{f(z)}}=1-\frac{p^*}{f(z)}$.
		Samll changes in price can have big effects,
		$\to$ slightly lower price $\tilde p,\tilde g(z)=$
			shifts curve upwards $\to$ only one equlibrium remains.

	\subsubsection{Network Cascades}
		$A,B$ have qualities $a,b$.
		Initially everyone except $S$ choose $B$.
		A node adopts $A$ if at least $q=\frac{b}{a+b}$ of his neighbors adopt $A$.

		\textbf{Def (Density of Cluster).}
			Cluster $C\subseteq V$ is density $x$ if $\forall v\in C$,
				$|N(v)\in C|/|N(v)| \ge x$.

		\textbf{Thm.}
			A complete cascade occurs iff $\nexists$ cluster of density $\ge 1-q$
				in $G\setminus S$.

		Given an infinite network,
		the \textbf{cascade capacity} is largest threshold $q$ at which
		$\exists$ finite set of initial adopters that cause a complete cascade.

	\subsubsection{Compatibility}
		Allow $AB$ (bilingual) with fixed cost $c$.
		Set $b=1$ and scale $a$ and $c$.

	\subsubsection{Locality in Networks}
		$G=(V,E)$, each node is a decision maker.
		Nodes have goal to compute min dominating set (greedy gives $O(\log n)$-approx,
			better is NP-hard).
		Every node knows its $k$-hoo neighbors.

		\textbf{Thm.}
		With local neighborhood info, no algorithm can approximate
			MDS, MVC, MMatching within $\Omega(n^{c/k^2})$ and $\Omega(\Delta^{1/k})$
			($\Delta=$max degree).

		\textbf{Cor.}
		In order to get a constant or poly-log approx, every algo has to  have knowledge
			of $\Omega(\sqrt{\log n})$ or $\Omega(\log \Delta)$ neighborhood.

\subsection{Epidemics}
	\subsubsection{Branch Model}
		Beginning: one person infected.
		Step: each contacts $k$ person, infected w.p. $p$.
		Claim: if $R_0=pk<1$ disease stop in finite steps.

		Let $q_n=\Pr[\textrm{some person in level $n$ get infected}]$,
		$q^*=\lim_{n\to\infty} q_n$.
		Let $Y_{nj}=1$ iff $j$-th person in level $n$ get infected,
			$X_n=\sum_j Y_{nj}$.
		Then 
		\[
			\E[X_n]=\sum_{1\le j\le k^{n}} \E[Y_{nj}]=
			\E[X_n]=\sum_{1\le j\le k^{n}} p^{n-1} = R_0^{n}.
		\]
		Since $\E[X_n]=\sum_{a\ge 1} \Pr[X_n\ge a]$,
			know $q_n=\Pr[X_n\ge 1]\le \E[X_n]=R_0^n$.
		Thus $q^*=0$ when $R_0<1$.

		For $R_0>1$, have $q_n=(1-p q_{n-1})^k$.
		Let $f(x)=1-(1-px)^k$, then $q^*=f(f(...f(1)))>0$. (Plot to see.)

	\subsubsection{SI Model}
		S=susceptible, I=infectious.
		Assume all people are in a clique.
		Let $S(t)=$number of S at time $t$, $X(t)=$number of I at $t$.
		At each time, each person will meet another $\beta$ person.
		\[ \begin{split}
			\frac{\dd X}{\dd t} &= X \beta \frac{S}{n} \\
			\frac{\dd S}{\dd t} &= -X \beta \frac{S}{n}. \\
		\end{split} \]
		Let $s=S/n,x=X/n$, have
		\[
			\pte{\frac{\dd x}{\dd t} = \beta(1-x)x}
			\Longrightarrow
			\pte{x(t)=\frac{x_0 e^{\beta t}}{1-x_0+x_0 e^{\beta t}}}.
		\]

	\subsubsection{SIR Model}
		R=recovered. Let $\gamma=$ recover rate and $r=$ prop of recover people.
		\[ \begin{split}
			\frac{\dd s}{\dd t} &= -\beta s x \\
			\frac{\dd x}{\dd t} &= \beta s x - \gamma x \\
			\frac{\dd r}{\dd t} &= \gamma x.
		\end{split} \]
		Get differential eq which is hard to solve (only numerically):
		\[
			\frac{\dd r}{\dd t} =
				r\pte{1-r-s_0 e^{-\beta r/\gamma}}.
		\]

	\subsubsection{Genealogy and Mitochondrial Eve}
		$N=$ population. Consider $k$ individuals($k\ll N$).
		\[
		\Pr[\textrm{no collision}] = \pte{1-\frac{1}{N}} \pte{1-\frac{2}{N}}
		... \pte{1-\frac{k-1}{N}} \approx 1 - \frac{k(k-1)}{2N} + O\pte{\frac{1}{N^2}}.
		\]
		Let $W_i$ be number of generations it takes to generate collision when
			number of interesting nodes is $i$.
		Then
		\[
			\E[W_i]\approx \frac{2N}{i(i-1)},
		\]
		\[
			\E[W]=\E\left[\sum_{2\le i\le k} W_i\right]\approx 2N\pte{1-\frac{1}{k}}.
		\]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Appendix}
\begin{align*}
	&\sum_{k=a}^br^k=\frac{r^{b+1}-r^a}{r-1}\\
	&\sum_{k=a}^bkr^k=\frac{r^{b+1}(br-b-1)-r^a(ar-a-r)}{(r-1)^2}\\
	&\sum_{k=a}^bk^2r^k=\frac{r^{b+1}((br-b-1)^2+r)-r^a((ar-a-r)^2+r)}{(r-1)^3}\\
	&\sum_{k=1}^nk^2=\frac{1}{6}n(n+1)(2n+1)\\
	&\sum_{k=1}^nk^3=\frac{1}{4}n^2(n+1)^2\\
	&\sum_{k=1}^nk^4=\frac{1}{30}n(n+1)(2n+1)(3n^2+3n-1)\\
	&\sum_{k=1}^nk^5=\frac{1}{12}n^2(n+1)^2(2n+1)(2n^2+2n-1)\\
	&k^{\overline{m}}=k(k+1)(k+2)\dots(k+m-1)\\
	&\sum_{k=1}^nk^{\overline{m}}=\frac{n^{\overline{m+1}}}{m+1}\\
\end{align*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\end{multicols}
%\end{landscape}
%\end{multicols}
\end{document}

% vim: set ts=8 sw=8 noet sts=8 tw=79 indentexpr=:

### 2013-06-20 network-science/paper.tex
clear

--- 2013-06-20 trunk/network-science/paper.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title
+{
+	Centrality and Activity for Envolving Networks
+}
+\author
+{
+	Pufan He\\\href{mailto:hpfdf@126.com}
+}
 \begin{document}
-%\begin{multicols}{3}
-\section*{\textsc{Net Science}'s Sheet {\large by Feng Qiwei}}
+\maketitle
+\begin{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Biblographic Coupling}
-	B.C. of $(i,j)$ is $\#$ of other nodes to which both $i,j$ point:
-	$B=A^T A$.
+\end{abstract}
 
-\subsection{Degree}
-	\[
-		k_i=\# \textrm{ of edges connected to }i, \\
-	\]
-	\[
-		\rho(G)=\frac{m}{\binom{n}{2}} = \frac{c}{n-1}\textrm{ where }c=\ang{k_i}.
-	\]
+\section{Introduction}
+\section{}
+\section{}
+\section{Conclusion}
 
-\subsection{Transitivity}
-	\[
-	\textrm{clustering cofficient} =
-		\frac{\#\textrm{ closed paths of len 2}} {\#\textrm{ paths of len 2}}, \\
-	\]
-	\[
-	\textrm{local c.c.} =
-		\frac{\#\textrm{ pairs of connected neighbors}} {\#\textrm{ pairs of neighbors}}.
-	\]
-
-\subsection{Centrality}
-	\subsubsection{Eigenvector}
-		Let $x(t)=A^t x(0)$ where $x(0)=\sum_i c_i v_i$,
-		then $x(t)=\sum_i c_i \lambda_i^t v_i=\lambda_1^t \sum_i c_i (\lambda_i/\lambda_1)^tv_i$.
-		For $t\to\infty$, know $(\lambda_i/\lambda_1)^t\to 0$ so $x(t)\to c_1\lambda_1^t v_1$, so
-		\[
-			\pte{Ax = \lambda_1 x} \Longrightarrow
-			\pte{x_i=\lambda_1^{-1} \sum_j A_{ij} x_j}.
-		\]
-		\textbf{Prob.}
-		Only vertices in out-component(s) of SCC of two or more vertices can have
-			non-zero E.C..
-
-	\subsubsection{Katz}
-		\[
-			\pte{x_i = \alpha\sum_j A_{ij} x_j + \beta}
-			\Longleftrightarrow
-			\pte{x=\alpha Ax+\beta 1}.
-		\]
-		Set $\beta=1$ (should have $\alpha<\lambda_1^{-1}$):
-			$x=(I-\alpha A)^{-1} \cdot 1$.
-
-	\subsubsection{Pagerank}
-		\[
-			\pte{x_i = \alpha \sum_j A_{ij} \frac{x_j}{k_j^{out}} + \beta}
-			\Longleftrightarrow
-			\pte{x=D(D-\alpha A)^{-1}\cdot \beta1}.
-		\]
-
-	\subsubsection{Hubs and Authorities}
-		\[
-			x=\alpha A y, y=\beta A^T x.
-		\]
-
-	\subsubsection{Closeness}
-		\[
-			d_{ij}=\textrm{ len of SP bet. $i$ and $j$},
-			\textrm{~~~~}
-			l_i=\frac{1}{n-1} \sum_{j\neq i} d_{ij},
-			\textrm{~~~~}
-			c_i=\frac{1}{l_i}.
-		\]
-
-	\subsubsection{Betweeness}
-		\[
-			n_{s,t}^i=\#\textrm{ of SP $s\to t$ through $i$},
-			\textrm{~~~~}
-			g_{s,t}=\#\textrm{ of SP $s\to t$},
-		\] \[
-			\textrm{B.C. of $i$}=x_i=\sum_{s,t} \frac{n_{s,t}^i}{g_{s,t}}.
-		\]
-
-	\subsubsection{Flow}
-		\[
-			x_i = \sum_{s,t} m_{s,t},
-			\textrm{~~~~}
-			m_{s,t}=\textrm{ flow through $i$ in a max $s$-$t$ flow}.
-		\]
-
-\subsection{Similarity}
-	\textbf{Structral s.:} if share many of the same neighbors.
-	\textbf{Regular s.:} if neighbors are similar.
-
-	\subsubsection{Consine}
-		\[
-			\sigma_{ij} = \frac{\sum_k A_{ik} A_{kj}} {\sqrt{\sum_k A_{ik}^2}\sqrt{\sum_k A_{kj}^2}}
-			=\textrm{(in unweight G)}=\frac{n_{ij}}{\sqrt{k_i k_j}}.
-		\]
-	\subsubsection{Pearson Coefficients}
-		\[ \begin{split}
-			\op{cov}(A_i,A_j)
-			&= \#\textrm{common neighbors} - \#\textrm{exp. com. neighs} \\
-			&= \sum_k A_{ik} A_{jk} - \frac{k_i k_j}{n} 
-			= \sum_k \pte{A_{ik}-\ang{A_i}} \pte{A_{jk}-\ang{A_j}}, \\
-		\end{split} \]
-		\[ \begin{split}
-			r_{ij}
-			&= \textrm{standard Pearson corellation coefficient} \\
-			&= \frac{\sum_k \pte{A_{ik}-\ang{A_i}} \pte{A_{jk}-\ang{A_j}}}
-				{\sqrt{\pte{A_{ik}-\ang{A_i}}^2} \sqrt{\pte{A_{jk}-\ang{A_j}}^2}}. \\
-		\end{split} \]
-
-\subsection{Homiphily and Assortive Mixing}
-	\subsubsection{A.M. by Enumerative Characteristics}
-		\[ \begin{split}
-			Q &= \textrm{modularity} \\
-			&= \frac{1}{m} \pte{\#\textrm{same type edges} - \#\textrm{exp. same type edges}} \\
-			&= \frac{1}{2m} \sum_{ij} \pte{A_{ij} - \frac{k_i k_j}{2m}} \delta(c_i,c_j)
-			=\sum_r e_{rr} - a_r^2. \\
-			e_{rs} &= \frac{1}{2m} \sum_{ij} A_{ij} \delta(c_i,r) \delta(c_j,s), \\
-			a_r &= \frac{1}{2m} \sum_i k_i \delta(c_i,r). \\
-		\end{split} \]
-
-	\subsubsection{A.M. by Scalar Characteristics}
-		\[ \begin{split}
-			r &= \textrm{assortativity coefficient} \\
-			&= \frac{\textrm{covariances over nodes}}{\textrm{cov. in perfectly mixed network}} \\
-			&= \frac{\sum_{ij} \pte{A_{ij} - k_i k_j / 2m} x_i x_j}
-				{\sum_{ij} \pte{k_i \delta_{ij} - k_i k_j /2m} x_i x_j}.
-		\end{split} \]
-
-\subsection{Power Law Distribution}
-	\[
-		p_k = C k^{-\alpha} \textrm{ where $\alpha$ in $[2,3]$ are typical}.
-	\]
-	\[
-		P_k = \sum_{i=k}^\infty p_i
-			\approx C \int_k^\infty x^{-\alpha} \dd x
-			=\frac{C}{\alpha-1} k^{-(\alpha-1)}.
-	\]
-	\[ \begin{split}
-		\alpha &= 1 + N\left[ \sum_i \ln \frac{k_i}{k_{min} - 1/2} \right]^{-1}, \\
-		\sigma &= \sqrt{N} \left[ \sum_i \ln \frac{k_i}{k_{min} - 1/2} \right]^{-1}
-			= \frac{\alpha-1}{\sqrt{N}}.
-	\end{split} \]
-
-\subsection{Graph Laplacian}
-	Diffusion $\frac{\dd \psi_i}{\dd t}=c \sum_j A_{ij} (\psi_j-\psi_i)
-		=c\sum_j(A_{ij}-\delta_{ij}k_i)\psi_j
-		\Longrightarrow \frac{\dd \psi}{\dd t}=c(A-D)\psi$.
-	Define $L=D-A$, then $\frac{\dd \psi}{\dd t}+cL\psi=0$.
-	Need to solve $\psi(t)=\sum_i a_i(t) v_i$.
-	Have $\sum_i (\frac{\dd a_i}{\dd t} + c\lambda_i a_i) v_i = 0$,
-	then $\frac{\dd a_i}{\dd t} + c \lambda_i a_i=0$ since $v_i\perp v_j$.
-	So $a_i(t)=a_i(0) e^{-c\lambda_i t}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Big Things}
-
-\subsection{Random Graph}
-	\subsubsection{Poisson Random Graph}
-		Poisson r. g. $G(n,p)$:
-		$n$ nodes where $\forall u,v$, $\Pr[\exists (u,v)\in G]=p$:
-		\begin{itemize}
-			\item mean $\#$ edges: $\binom{n}{2} p$;
-			\item avg. deg.: $(n-1)p=c$;
-			\item deg. distr.: $p_k=\binom{n-1}{k} p^k (1-p)^{n-1-k}$,
-				and for large $n$: $p_k=e^{-c} \frac{c^k}{k!}$ (Poisson deg. distr.);
-			\item cluster coefficient $= p = \frac{c}{n-1} \to 0$.
-		\end{itemize}
-
-	\subsubsection{Giant Component}
-		$u$: fraction of vertices that do \textbf{NOT} belong to the giant $T$.
-		If $i\notin T$, then $\forall j$, either
-		\begin{itemize}
-			\item $i$ is not connected to $j$: $1-p$;
-			\item $i$ is connected to $j$ but $j\notin T$: $pu$.
-		\end{itemize}
-		Total: $1-p+pu$. Probability that $i\notin T$ is
-		\[
-			u=(1-p+pu)^{n-1}=\pte{1-\frac{c}{n-1}(1-u)}^{n-1},
-		\]
-		%= (n-1) \ln\pte{1-\frac{c}{n-1}(1-u)}
-		\[
-			\ln u 
-			\approx -(n-1) \frac{c}{n-1} (1-u) = -c(1-u)
-		\]
-		\[
-			\Longrightarrow u=e^{-c(1-u)}
-			\Longrightarrow 1-u=S=1-e^{-cS}.
-		\]
-		Phase transition takes place when
-		\[
-			\left.\frac{\dd}{\dd S} \pte{1-e^{-cS}} = c e^{-cS} = 1 \right|_{S=0}
-			\Longrightarrow c=1.
-		\]
-		Core $C(Q)$ and periphery $P(Q)$: $s=|C(Q)|+|P(Q)|$.
-		A node in $P(Q)$ has $p(n-s)\approx c$ neighbors outside, so
-		\[
-			P(Q') \approx c P(Q), C(Q') = Q.
-		\]
-		If $c>1$, periphery grows; if $c<1$, it shrinks.
-
-	\subsubsection{Small Components}
-		$\pi_s$: prob that a randomly selected node belongs to a small component of size $s$.
-		Fraction of nodes not in the giant: $\sum_{s=0}^\infty \pi_s = 1-S$.
-
-		Observation: s.c. are trees.
-		Consider tree of $s$ nodes.
-		Remain place of edge: $\binom s 2 - (s-1) = \frac 1 2 (s-1)(s-2)$,
-			so exp $\#$ non-tree edges: $\frac 1 2 (s-1)(s-2) p =
-			\frac 1 2 (s-1)(s-2) c / (n-1) \to 0$,
-			if $s$ increase slowly than $\sqrt n$.
-
-		Consider $i$'s neighbors $n_1,...,n_k$ with component size $s_1,...,s_k$.
-		$P(s|k)$: $i$ belongs to component of size $s$.
-		\[
-			P(s|k)=\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j).
-		\]
-		Know $\pi_s = \sum_{k=0}^\infty p_k P(s|k)$.
-		(Generating function now!)
-		Let $h(z)=\sum_{s=1}^\infty \pi_s z^s$,
-			then $\pi_s=\left. \frac{1}{s!} \frac{\dd^s h}{\dd z^s} \right|_{z=0}$.
-		Consider $h(z)$:
-		\[ \begin{split}
-			h(z) &= \sum_{s=1}^\infty z^s \sum_{k=0}^\infty p_k
-			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j) \\
-			&= \sum_{s=1}^\infty z^s e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
-			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j) \\
-			&= e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
-			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j}} z^{1+\sum_j s_j} \\
-			&= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
-			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j} z^{s_j}} \\
-			&= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
-			\pte{\sum_{s=1}^\infty \pi_{s} z^{s}}^k 
-			= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!} h^k(z) 
-			= z e^{c(h(z)-1)}.
-		\end{split} \]
-
-		No closed-form solution for $h(z)$.
-		$\ang{s}=\frac{\sum_s s\pi_s}{\sum_s \pi_s}=\frac{h'(1)}{1-S}$.
-		Know
-		\[
-			h'(z)=e^{c(h(z)-1)} + czh'(z)e^{c(h(z)-1)} = \frac{h(z)}{z} + ch(z)h'(z)
-		\]
-		\[
-			\Longrightarrow h'(z)=\frac{h(z)}{z(1-ch(z))}.
-		\]
-		$h(1)=\sum_s \pi_s=1-S \Longrightarrow \ang{s}=\frac{1}{1-c+cS}$.
-		If $c<1$, no giant so $\ang{s}=\frac{1}{1-c}$.
-
-		$n_s$: $\#$ components of size $s$. $\pi_s = s n_s/n$.
-		Avg size of component: $$R=\frac{\sum_s s n_s}{\sum_s n_s}
-			= \frac{n \sum_s \pi_s}{n \sum_s \pi_s / s}
-			= \frac{1-S}{\sum_s \pi_s/s}.$$
-		Noting that
-		\[
-			\int_0^1 \frac{h(z)}{z} \dd z = \sum_{s=1}^\infty \int_0^1 z^{s-1} \dd z
-			= \sum_{s=1}^\infty \frac{\pi_s}{s}.
-		\]
-		Have $\frac{h(z)}{z} = (1-ch(z)) \frac{\dd h}{\dd z}$,
-			so $$\sum_{s=1}^\infty \frac{\pi_s}{s}
-			=\int_0^1 (1-ch(z)) \frac{\dd h}{\dd z} \dd z
-			=\int_0^{1-S}(1-ch) \dd h = 1-S-\frac 1 2 c(1-S)^2.$$
-		(Upper integration limit $ = h(1)= 1-S$.)
-		Finally $R=\frac{2}{2-c+cS}$.
-		(\textbf{NOTE:}
-		$G(n,p)$ is connected if $p(n)=\frac{\log n}{n}$,
-			then diameter $D=A+\frac{\ln n}{\ln c}$.)
-
-	\subsubsection{Configuration Model}
-		Specify degree distr $p$, randomly pick endpoints to form edges.
-
-\subsection{Preferential Attachment}
-	Each new paper cite $c$ old papers randomly:
-	\[ \begin{split}
-		p_q(n) &= \textrm{fraction of nodes with deg $q$}, \\
-		q_i &= \textrm{in-degree of node $i$}, \\
-	\end{split} \]
-	\[
-		\Pr[i\textrm{ get citation}] = \frac{q_i+a}{\sum_j (q_j+a)} = \frac{q_i+a}{n(c+a)}. \\
-	\]
-	\[
-		\E[\textrm{new cites deg $q$ nodes}]
-			=n p_q(n) c \frac{q+a}{n(c+a)} = \frac{c(q+a)}{c+a} p_q(n).
-	\]
-	\subsubsection{Master Equation}
-		\[ \begin{split}
-			(n+1)p_q(n+1)&=np_q(n)
-				+\frac{c(q-1+a)}{c+a}p_{q-1}(n)- \frac{c(q+a)}{c+a}p_q(n) \\
-			(n+1)p_0(n+1)&=np_0(n)+1-\frac{ca}{c+a}p_0(n).
-		\end{split} \]
-		\[
-			n\to\infty\Longrightarrow
-			p_0=\frac{1+\frac{a}{c}}{a+1+\frac{a}{c}},
-			p_q=\frac{q+a-1}{q+a+1+\frac{a}{c}}p_{q-1},
-		\]
-		\[
-			\Longrightarrow
-			p_q=\frac{(q+a-1)(q+a-2)\cdots a}{(a+a+1+\frac{a}{c})\cdots(a+1+\frac{a}{c})}.
-		\]
-		% TODO: Gamma Beta
-		For large $q$,
-			$p_q\sim (q+a)^{-\alpha}$ or simply $p_q\sim q^{-\alpha}$,
-			where $\alpha=2+\frac{a}{c}$.
-
-	\subsubsection{Mean-Field Approximation}
-		One link with $p$ choose uniform, $q=1-p$ choose by P.A..
-		\[ \begin{split}
-			x_i(t) &= \textrm{in-degree of $i$ at time $t$ with $x_i(i)=0$}, \\
-			\Delta_t &= \E[x_i(t+1)-x_i(t)]  = \frac{p}{t} + \frac{(1-p)x_i(t)}{t}.
-		\end{split} \]
-		Consider a deterministic process in which a nodes degree increased by exact $\Delta_t$.
-		Find distribution of expected degrees.
-		\[
-			d_i(i) = 0, \frac{\partial d_i(t)}{\partial t} = \frac{p}{t} + \frac{(1-p)d_i(t)}{t}.
-		\]
-		\[
-			\Longrightarrow \int \frac{1}{p+q d_i} \frac{\partial d_i}{\partial t} \dd t = \int \frac{1}{t} \dd t \\
-		\] \[
-			\Longrightarrow \ln(p+q d_i) = q \ln t + c \\
-		\] \[
-			\Longrightarrow p+q d_i = A t^q, \\
-		\] \[
-			\textrm{set $d_i(i)=0$,}\Longrightarrow d_i(t) = \frac{p}{q}\pte{\pte{\frac{t}{i}}^q-1}.
-		\]
-		$i_t(k)$: node with expected degree exactly $k$ at time $t$:
-		\[
-			d_{i_t(k)}(t) = k = \frac{p}{q}\pte{\pte{\frac{t}{i_t(k)}}^q-1}
-			\Longrightarrow
-			i_t(k)=t\pte{\frac{p}{q}k+1}^{-\frac{1}{q}}.
-		\]
-		Fraction of nodes with degree $>k$:
-			$F_k(t) = \pte{\frac{q}{p}k+1} ^ {-\frac{1}{q}}$,
-		\[
-			\Longrightarrow
-			p_k=-\frac{\partial F_k}{\partial k}
-			=\frac{1}{p}\pte{\frac{q}{p}k+1}^{-1-\frac{1}{q}}
-			\sim k^{-\pte{1+\frac{1}{q}}}.
-		\]
-
-\subsection{Small World}
-	Each node is connected with all neighbors of distance $\le c/2$.
-	For $nc/2$ times pick random pair and add shortcut w.p. $p$.
-
-	\subsubsection{Degree Distribution}
-		\[
-			k_i = c + s_i = c + (\#\textrm{shortcuts attacked to $v_i$}).
-		\]
-		There are $ncp$ endpoints of shortcuts. $s_i$ is Poisson distributed
-			with mean $cp$:
-		\[
-			p_s = e^{-cp}\frac{(cp)^s}{s!} \Longrightarrow
-			p_k = e^{-cp}\frac{(cp)^{k - c}}{(k - c)!}, \textrm{ for }k \ge c.
-		\]
-
-	\subsubsection{Clustering Coefficient}
-		$C=(\#\textrm{triangles}\times 3)/(\#\textrm{connected tripes})$.
-		\begin{enumerate}
-			\item $\#$ triangles
-			\begin{enumerate}
-				\item in ring: $n\binom{c/2}{2}=\frac{1}{4}nc(\frac{c}{2} - 1)$.
-				\item due to shortcuts:
-					prob $u,v$ connected by shortcut$=\frac{ncp/2}{n(n-1)/2}\approx \frac{cp}{n}$.
-					A shortcut complete a triangle for $u,v$ with dist $\frac{c}{2}\sim c$,
-						$\#$ of such $u,v$ is proportional to $n$.
-					$\Longrightarrow \sim n\cdot \frac{cp}{n} = cp =$
-					const $\to$ ignore.
-
-			\end{enumerate}
-			\item $\#$ connected tripes
-			\begin{enumerate}
-				\item in ring: $n\binom{c}{2}=\frac{1}{2}nc(c - 1)$.
-				\item through shortcuts: $(ncp/2)\times 2\times c$.
-				\item through pairs of shortcuts: for node with $m$ shortcuts,
-					has $\binom{m}{2}$ triples.
-					Let $m=cp$ (mean of Poisson distr) then total triples
-					$=(nc^2p^2)/2$.
-			\end{enumerate}
-		\end{enumerate}
-		\[
-			C=\frac{3(c-2)}{4(c-1)+8cp+4cp^2}.
-		\]
-
-	\subsubsection{Path length}
-		No exact expr for mean distance in WS model.
-		Consider $c=2$. Let $l=$ average len of SP.
-		$s=\#$ shortcuts.
-
-		Avg dist between shortcuts on ring $\tau=\frac{n}{2s}$
-			$\Longrightarrow$ $n,\tau$ completely specify the model.
-
-		Consider dimensionless $\frac{l}{n}$.
-		$\frac{l}{n}=F(\frac{n}{\tau})=F(2s)$
-		($F$: universal).
-		If density of shortcuts is low then for general $c$:
-		$l=\frac{2n}{c} F(2s) = \frac{n}{c} f(ncp)$.
-		Simulate $f$:
-		\[
-			f(x) = \frac{2}{\sqrt{x^2+4x}}\op{tanh}^{-1}\sqrt{\frac{x}{x+4}}
-		\]
-		\[
-			\Rightarrow x\to\infty
-			\Rightarrow f(x) = \frac{\ln x}{x}
-			\Rightarrow l = \frac{\ln(ncp)}{c^2p}.
-		\]
-
-	\subsubsection{Milgram}
-		Short paths exists and can be found efficiently in decentralized way.
-		WS model: $c=2$; $K=$ nodes with dist $\le\sqrt{n}$ of $t$.
-		$\Pr[\textrm{a shortcut points into $K$}]=2/\sqrt{n}$
-			$\to$ need at least $\sqrt{n}/2$ steps into $K$.
-		Crossing $K$ step-by-step at least $\sqrt{n}/2$ steps.
-		Thus need $\Omega(\sqrt n)$ steps.
-
-	\subsubsection{Kleinberg}
-		Choose shortcuts s.t.
-			$\Pr[\textrm{shortcut between $u,v$ at dist $r$}]=\kappa r^{-\alpha}$.
-		Choose shortcut len from distribution.
-		Place edge randomly in network.
-		Total prob that shortcut between two nodes is $p\kappa r^{-\alpha}$.
-		Normalization const $\kappa$:
-		\[
-			\kappa\sum_{r = 1}^{\frac{1}{2}(n - 1)}r^{-\alpha} = 1.
-		\]
-		We can approximate the sum:
-		\[
-			\sum\limits_{r= 1}^{\frac{1}{2}(n - 1)} r^{-\alpha}
-			\approx\int_{1}^{\frac{1}{2}(n - 1)} r^{-\alpha}\dd r
-			+\frac{1}{2}+\frac{1}{2}\pte{\frac{1}{2}(n - 1)}^{-\alpha},
-		\]
-		where $\int_{1}^{(n - 1)/2} r^{-\alpha}\dd r=((n-1)/2)^{1-\alpha}/(1-\alpha)$.
-		For $n\to\infty$:
-		\[
-			\kappa\approx\left\{\begin{array}{ll}
-				(1-\alpha)(\frac{1}{2}n)^{\alpha - 1} &\alpha<1\\
-				\ln^{-1}(\frac{1}{2}n) &\alpha = 1\\
-				\frac{2(\alpha-1)}{\alpha+1} &\alpha>1
-			\end{array}\right..
-		\]
-		Divide nodes into classes that $C_k$ consists of $v_i$ with
-			$2^{k-1}\le d(v_i,t)<2^k$.
-		Nodes in $C_0,...,C_{k-1}$:
-			$\sum_{m=0}^{k-1}n_m = \sum_{m=0}^{k-1}2^m = 2^k-1 > 2^{k-1}$.
-		All these are at most a dist $3 * 2^k < 2^{k+2}$ from $v_{\mathrm{cur}}$ in $C_k$.
-		Prob of having a shortcut to one of the nodes:
-		\[
-			p\kappa 2^{-(k+2)\alpha}*2^{k-1}=p\kappa 2^{k-1-(k+2)\alpha}.
-		\]
-		If $v_{\mathrm{cur}}$ has no shortcut, pass msg to neighbor.
-		Exp $\#$ moves until find a shortcut to $C_0,...,C_{k-1}$ is 
-		\[
-			\frac{1}{p\kappa} 2^{2\alpha+1} 2^{(\alpha-1)k}.
-		\]
-		In wrost case msg goes through all classes:
-		\[
-			l \le \frac{1}{p\kappa}*2^{2\alpha+1}*
-				\sum_{k=0}^{\log(m+1)}2^{(\alpha-1)k}
-			= \frac{1}{p\kappa}*2^{2\alpha+1}
-				\frac{(2(n+1))^{\alpha-1}-1}{2^{\alpha-1}-1}.
-		\]
-		Plugging the value of $\kappa$ for $n\to\infty$:
-		\[
-			l=\left\{\begin{array}{ll}
-				A n^{1-\alpha} &\alpha<1\\
-				B \log^2 n &\alpha = 1\\
-				C n^{\alpha-1} &\alpha>1
-			\end{array}\right..
-		\]
-
-\subsection{Stable Outcome}
-	\subsubsection{Nash Bargain Solution}
-		$A$ and $B$ with outside option $x$ and $y$.
-		If $x+y>1$ then no agreement possible.
-		If $x+y\le 1$ then has surplus $s=1-x-y$.
-
-		NBS: devide surplus evenly.
-
-	\subsubsection{Stable Outcome}
-		$G=(V,E)$, edge weight $w:E\to R^+$. Each $v\in V$ is a player.
-
-		\textbf{Outcome}: matching $M$ among players and vector $x$
-			describing each players payoff.
-			$\forall(u,v)\in M$, $x_u+x_v=w_{u,v}$; $\forall u\notin M$, $x_u=0$.
-
-		\textbf{Stable outcome}: outcome with no unstable edge.
-
-		\textbf{Balanced outcome} (generalization of NBS):
-			$\forall (u,v)\in M$, split of money represents the NBS
-				for $u,v$ given the best outside option for $u,v$
-				provided by values in the rest of the network.
-
-		$\to$ A balanced outcome exists iff a stable outcome exists.
-
-		$\to$ A balanced outcome can be computed in poly-time.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Unknown}
-
-\subsection{Cascades}
-	\subsubsection{Network Effects \textsc{(Things That I Cannot Understand!)}}
-		Decisions: $\{R,A\}$;
-		States: $\{G,B\}$ w.p. $\{p,1-p\}$.
-		Payoffs: $0$ for reject and $(G ? v_g>0 : v_b<0)$ for accept
-			($p v_g + (1-p) v_b = 0$).
-
-		Signals: gets a private signal before decision:
-			$H$ (high sig) = "accepting is good",
-			$L$ (low) = "..is bad".
-			$\Pr[H|G]=\Pr[L|B]=q>1/2$, 
-			$\Pr[L|G]=\Pr[H|B]=1-q$.
-
-		Know sequence $S$ of independently generated signals.
-		$a=\# H\in S$, $b=\# L\in S$.
-		\[
-			\Pr[G|S]=\frac{\Pr[G]\Pr[S|G]}{\Pr[S]}
-				=\frac{pq^a(1-q)^b}{pq^a(1-q)^b+(1-p)(1-q)^aq^b}.
-		\]
-		For $a>b$, $\Pr[G|S]>p$.
-		For $a<b$, $\Pr[G|S]<p$.
-		For $a=b$, $\Pr[G|S]=p$.
-
-	\subsubsection{Economy with Network Effect}
-		When $z$-fraction of customers buy, ceservation price of $x$ is $r(x)f(z)$.
-		$r$: intrinsic interest ($r(1)=0$).
-		$f$: benefit (increasing in $z$, $f(0)=0$).
-
-		Everyone expect $z=0$ $\to$ R.P.$=0<p$ $\to$ no one will buy.
-		Everyone expect $z\in(0,1)$ $\to$ $0..z$ will buy
-			$\to$ R.P.$=r(z)f(z)=p$.
-		Stability: strong equlibrium OR tripping point.
-
-		If $[0,\hat z]$ buy, then $r(\hat z)=\frac{p^*}{f(z)} \Longrightarrow
-			\hat z=r^{-1}\pte{\frac{p^*}{f(z)}}$.
-		If $z\ge 0$ then $\hat z=g(z)$ where $g(z)=r^{-1}\pte{\frac{p^*}{f(z)}}$
-			for $\frac{p^*}{f(z)}\le r(0)$, $=0$ otherwise.
-
-		NOW, consider $f(0)>0$. Let $r(x)f(z)=(1-x)(1+az^2)$.
-		If exp $\hat z$ then $g(z)=r^{-1}\pte{\frac{p^*}{f(z)}}=1-\frac{p^*}{f(z)}$.
-		Samll changes in price can have big effects,
-		$\to$ slightly lower price $\tilde p,\tilde g(z)=$
-			shifts curve upwards $\to$ only one equlibrium remains.
-
-	\subsubsection{Network Cascades}
-		$A,B$ have qualities $a,b$.
-		Initially everyone except $S$ choose $B$.
-		A node adopts $A$ if at least $q=\frac{b}{a+b}$ of his neighbors adopt $A$.
-
-		\textbf{Def (Density of Cluster).}
-			Cluster $C\subseteq V$ is density $x$ if $\forall v\in C$,
-				$|N(v)\in C|/|N(v)| \ge x$.
-
-		\textbf{Thm.}
-			A complete cascade occurs iff $\nexists$ cluster of density $\ge 1-q$
-				in $G\setminus S$.
-
-		Given an infinite network,
-		the \textbf{cascade capacity} is largest threshold $q$ at which
-		$\exists$ finite set of initial adopters that cause a complete cascade.
-
-	\subsubsection{Compatibility}
-		Allow $AB$ (bilingual) with fixed cost $c$.
-		Set $b=1$ and scale $a$ and $c$.
-
-	\subsubsection{Locality in Networks}
-		$G=(V,E)$, each node is a decision maker.
-		Nodes have goal to compute min dominating set (greedy gives $O(\log n)$-approx,
-			better is NP-hard).
-		Every node knows its $k$-hoo neighbors.
-
-		\textbf{Thm.}
-		With local neighborhood info, no algorithm can approximate
-			MDS, MVC, MMatching within $\Omega(n^{c/k^2})$ and $\Omega(\Delta^{1/k})$
-			($\Delta=$max degree).
-
-		\textbf{Cor.}
-		In order to get a constant or poly-log approx, every algo has to  have knowledge
-			of $\Omega(\sqrt{\log n})$ or $\Omega(\log \Delta)$ neighborhood.
-
-\subsection{Epidemics}
-	\subsubsection{Branch Model}
-		Beginning: one person infected.
-		Step: each contacts $k$ person, infected w.p. $p$.
-		Claim: if $R_0=pk<1$ disease stop in finite steps.
-
-		Let $q_n=\Pr[\textrm{some person in level $n$ get infected}]$,
-		$q^*=\lim_{n\to\infty} q_n$.
-		Let $Y_{nj}=1$ iff $j$-th person in level $n$ get infected,
-			$X_n=\sum_j Y_{nj}$.
-		Then 
-		\[
-			\E[X_n]=\sum_{1\le j\le k^{n}} \E[Y_{nj}]=
-			\E[X_n]=\sum_{1\le j\le k^{n}} p^{n-1} = R_0^{n}.
-		\]
-		Since $\E[X_n]=\sum_{a\ge 1} \Pr[X_n\ge a]$,
-			know $q_n=\Pr[X_n\ge 1]\le \E[X_n]=R_0^n$.
-		Thus $q^*=0$ when $R_0<1$.
-
-		For $R_0>1$, have $q_n=(1-p q_{n-1})^k$.
-		Let $f(x)=1-(1-px)^k$, then $q^*=f(f(...f(1)))>0$. (Plot to see.)
-
-	\subsubsection{SI Model}
-		S=susceptible, I=infectious.
-		Assume all people are in a clique.
-		Let $S(t)=$number of S at time $t$, $X(t)=$number of I at $t$.
-		At each time, each person will meet another $\beta$ person.
-		\[ \begin{split}
-			\frac{\dd X}{\dd t} &= X \beta \frac{S}{n} \\
-			\frac{\dd S}{\dd t} &= -X \beta \frac{S}{n}. \\
-		\end{split} \]
-		Let $s=S/n,x=X/n$, have
-		\[
-			\pte{\frac{\dd x}{\dd t} = \beta(1-x)x}
-			\Longrightarrow
-			\pte{x(t)=\frac{x_0 e^{\beta t}}{1-x_0+x_0 e^{\beta t}}}.
-		\]
-
-	\subsubsection{SIR Model}
-		R=recovered. Let $\gamma=$ recover rate and $r=$ prop of recover people.
-		\[ \begin{split}
-			\frac{\dd s}{\dd t} &= -\beta s x \\
-			\frac{\dd x}{\dd t} &= \beta s x - \gamma x \\
-			\frac{\dd r}{\dd t} &= \gamma x.
-		\end{split} \]
-		Get differential eq which is hard to solve (only numerically):
-		\[
-			\frac{\dd r}{\dd t} =
-				r\pte{1-r-s_0 e^{-\beta r/\gamma}}.
-		\]
-
-	\subsubsection{Genealogy and Mitochondrial Eve}
-		$N=$ population. Consider $k$ individuals($k\ll N$).
-		\[
-		\Pr[\textrm{no collision}] = \pte{1-\frac{1}{N}} \pte{1-\frac{2}{N}}
-		... \pte{1-\frac{k-1}{N}} \approx 1 - \frac{k(k-1)}{2N} + O\pte{\frac{1}{N^2}}.
-		\]
-		Let $W_i$ be number of generations it takes to generate collision when
-			number of interesting nodes is $i$.
-		Then
-		\[
-			\E[W_i]\approx \frac{2N}{i(i-1)},
-		\]
-		\[
-			\E[W]=\E\left[\sum_{2\le i\le k} W_i\right]\approx 2N\pte{1-\frac{1}{k}}.
-		\]
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Appendix}
-\begin{align*}
-	&\sum_{k=a}^br^k=\frac{r^{b+1}-r^a}{r-1}\\
-	&\sum_{k=a}^bkr^k=\frac{r^{b+1}(br-b-1)-r^a(ar-a-r)}{(r-1)^2}\\
-	&\sum_{k=a}^bk^2r^k=\frac{r^{b+1}((br-b-1)^2+r)-r^a((ar-a-r)^2+r)}{(r-1)^3}\\
-	&\sum_{k=1}^nk^2=\frac{1}{6}n(n+1)(2n+1)\\
-	&\sum_{k=1}^nk^3=\frac{1}{4}n^2(n+1)^2\\
-	&\sum_{k=1}^nk^4=\frac{1}{30}n(n+1)(2n+1)(3n^2+3n-1)\\
-	&\sum_{k=1}^nk^5=\frac{1}{12}n^2(n+1)^2(2n+1)(2n^2+2n-1)\\
-	&k^{\overline{m}}=k(k+1)(k+2)\dots(k+m-1)\\
-	&\sum_{k=1}^nk^{\overline{m}}=\frac{n^{\overline{m+1}}}{m+1}\\
-\end{align*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\end{multicols}
-%\end{landscape}
-%\end{multicols}
 \end{document}

### 2013-06-20 network-science/paper.tex
1

@@
-\documentclass[a4paper,twocolumn,10pt]{article}
+\documentclass[12pt]{scrartcl}
+
+%<<< Preamble
+\usepackage{tikz}
+\usepackage{array}
+\usepackage{pifont}
+\usepackage{engord}
+\usepackage{listings}
+\usepackage{titlesec}
+\usepackage{fancyhdr}
+\usepackage{fancyvrb}
 \usepackage{multicol}
-\usepackage{listings}
-\usepackage{fourier}
-\usepackage{amsmath}
+\usepackage{pgfplots}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage[plain]{fancyref}
+\usepackage[unicode]{hyperref}
+\usepackage{graphicx,tabularx}
+\usepackage[shortlabels]{enumitem}
+\usepackage[retainorgcmds]{IEEEtrantools}
+\usepackage{amsmath,amssymb,amsthm,amscd,amstext}
+\usepackage{mathtools}
+\usepackage{exscale}
+\usepackage{relsize}
+\usepackage{mathrsfs}
 
-\usepackage{tikz}
-\tikzstyle{every picture}+=[remember picture]
-\usetikzlibrary{arrows,decorations.pathreplacing,decorations.markings}
-\usepackage{listings}
-\lstset{
-	numbers=left,
-	basicstyle=\small\ttfamily,
-	numberstyle=\it\scriptsize\sffamily,
-	keywordstyle=\bf,
-	commentstyle=\color{red!50!green!50!blue!50},
-	frame=single,
-	%breaklines=true,
+\usepackage{setspace}
+\usepackage{lastpage}
+\usepackage{extramarks}
+\usepackage{chngpage}
+
+\usepackage{lmodern}
+\usepackage{mathpazo}
+
+\pgfplotsset{compat=1.6}
+\usetikzlibrary{arrows}
+\usetikzlibrary{patterns}
+\usetikzlibrary{positioning}
+\usetikzlibrary{automata}
+\usepackage{tikz-3dplot}
+
+\tikzset{ alert/.style={ very thick, draw=red!80, fill=red!20 } }
+\tikzset{ fancy/.style={ very thick, draw=blue!80, fill=blue!20 } }
+\tikzset{
+  dot/.style={
+    very thick,circle,draw=black,fill=black,inner sep=0,minimum size=5pt
   }
+}
+\tikzset { every state/.style={fancy} }
+\tikzset {
+  general/.style = {
+    shorten >=2pt, node distance=2.5cm, on grid, thick,>=stealth', auto
+  }
+}
+\newcommand{\mathhuge}[1]{\mathlarger{\mathlarger{\mathlarger{#1}}}}
+% \newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}
+\numberwithin{equation}{section}
+\mathtoolsset{centercolon}
 
-\usepackage{geometry}
-\geometry{left=0.7cm,right=0.7cm,top=0.7cm,bottom=1.3cm}
-%\linespread{1.0}
+% Theorem environment <<<
+\theoremstyle{definition}   \newtheorem{definition}{Definition}[section]
+\theoremstyle{plain}        \newtheorem{theorem}{Theorem}[section]
+\theoremstyle{plain}        \newtheorem{observation}{Observation}[section]
+\theoremstyle{plain}        \newtheorem{fact}{Fact}[section]
+\theoremstyle{plain}        \newtheorem{claim}{Claim}[section]
+\theoremstyle{plain}        \newtheorem{lemma}[theorem]{Lemma}
+\theoremstyle{plain}        \newtheorem{corollary}[theorem]{Corollary}
+\theoremstyle{remark}       \newtheorem{example}{Example}[section]
+\theoremstyle{remark}       \newtheorem{remark}{Remark}[section]
+\newcommand*{\fancyrefdeflabelprefix}{def}
+\newcommand*{\fancyrefthmlabelprefix}{thm}
+\newcommand*{\fancyreflemlabelprefix}{lem}
+\newcommand*{\fancyrefcorlabelprefix}{cor}
+\newcommand*{\fancyrefalglabelprefix}{alg}
+\newcommand*{\fancyreflnlabelprefix}{ln}
+\frefformat{plain}{\fancyreflnlabelprefix}{line #1}
+\Frefformat{plain}{\fancyreflnlabelprefix}{Line #1}
+\frefformat{plain}{\fancyrefalglabelprefix}{algorithm (#1)}
+\Frefformat{plain}{\fancyrefalglabelprefix}{Algorithm (#1)}
+\frefformat{plain}{\fancyrefdeflabelprefix}{definition (#1)}
+\Frefformat{plain}{\fancyrefdeflabelprefix}{Definition (#1)}
+\frefformat{plain}{\fancyrefthmlabelprefix}{theorem (#1)}
+\Frefformat{plain}{\fancyrefthmlabelprefix}{Theorem (#1)}
+\frefformat{plain}{\fancyreflemlabelprefix}{lemma (#1)}
+\Frefformat{plain}{\fancyreflemlabelprefix}{Lemma (#1)}
+\frefformat{plain}{\fancyrefcorlabelprefix}{corollary (#1)}
+\Frefformat{plain}{\fancyrefcorlabelprefix}{Corollary (#1)}
+%>>>
+% Alter some LaTeX Float for better treatment of figures: <<<
+% See p.105 of "TeX Unbound" for suggested values.
+% See pp. 199-200 of Lamport's "LaTeX" book for details.
+%   General parameters, for ALL pages:
+\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
+\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}     % 2 may work better
+\setcounter{dbltopnumber}{2}    % for 2-column pages
+\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
+\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
+\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
+\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages
 
-\AtBeginDocument{%
-	\setlength\abovedisplayskip{3pt}
-	\setlength\belowdisplayskip{3pt}
-}
-\usepackage{titlesec}
-\titlespacing{\section}{0pt}{5pt}{5pt}
-\titlespacing{\subsection}{0pt}{5pt}{5pt}
-\titlespacing{\subsubsection}{0pt}{5pt}{3pt}
+\allowdisplaybreaks[4]
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
-\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
-\newcommand{\ang}[1]{\left\langle {#1} \right\rangle}
-\newcommand{\lc}{\left(}
-\newcommand{\rc}{\right)}
-\newcommand{\parentheses}[1]{\left({#1}\right)}
-\newcommand{\pte}[1]{\left({#1}\right)}
-\newcommand{\labs}{\left|}
-\newcommand{\rabs}{\right|}
-\newcommand{\abs}[1]{\left|{#1}\right|}
-\newcommand{\op}{\operatorname}
-\newcommand{\E}{\operatorname{E}}
-\newcommand{\spt}{\operatorname{support}}
-\newcommand{\mA}{\mathcal{A}}
-\newcommand{\mB}{\mathcal{B}}
-\newcommand{\mC}{\mathcal{C}}
-\newcommand{\mD}{\mathcal{D}}
-\newcommand{\mE}{\mathcal{E}}
-\newcommand{\mJ}{\mathcal{J}}
-\newcommand{\mK}{\mathcal{K}}
-\newcommand{\mL}{\mathcal{L}}
-\newcommand{\mM}{\mathcal{M}}
-\newcommand{\mU}{\mathcal{U}}
-\newcommand{\mV}{\mathcal{V}}
-\newcommand{\mW}{\mathcal{W}}
-\newcommand{\mX}{\mathcal{X}}
-\newcommand{\bR}{\mathbb{R}}
-\newcommand{\bZ}{\mathbb{Z}}
-\newcommand{\bN}{\mathbb{N}}
-\newcommand{\bC}{\mathbb{C}}
-\newcommand{\uge}{\succcurlyeq}
-\newcommand{\Tr}{\op{Tr}}
-\newcommand{\dd}{\mathrm{d}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title
+%>>>
+%>>>
+\title %<<< Title Region
 {
@@
 \author
+{ \normalfont
+	Pufan He\\
+	\href{mailto:hpfdf@126.com}{hpfdf@126.com}\\
+	Tsinghua University.
+	\and
+	Yichao Zhou\\
+	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}\\
+	Tsinghua University.
+	\and
+	Qiwei Feng\\
+	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}\\
+	Tsinghua University.
+	\and
+	Yu Yan\\
+	\href{mailto:}{}\\
+	Tsinghua University.
+	\and
+	Qingyang Li\\
+	\href{mailto:}{}\\
+	Tsinghua University.
+	\and
+	Xin Xing\\
+	\href{mailto:}{}\\
+	Tsinghua University.
+}
+\date
 {
-	Pufan He\\\href{mailto:hpfdf@126.com}
+	June 25, 2013
 }
+%>>>
+
 \begin{document}
 \maketitle
+\newpage
 \begin{abstract}
@@
 
-% vim: set ts=8 sw=8 noet sts=8 tw=79 indentexpr=:
+% vim: set ts=8 sw=8 noet sts=8 tw=79 indentexpr= fdm=marker foldmarker=<<<,>>>:

### 2013-06-20 network-science/paper.tex
2

@@
 
-\pgfplotsset{compat=1.6}
+%\pgfplotsset{compat=1.6}
 \usetikzlibrary{arrows}
@@
 {
-	Centrality and Activity for Envolving Networks
+	Metrics and Algorithms for Envolving Social Networks
 }
 \author
-{ \normalfont
+{
 	Pufan He\\
-	\href{mailto:hpfdf@126.com}{hpfdf@126.com}\\
-	Tsinghua University.
+	\href{mailto:hpfdf@126.com}{hpfdf@126.com}
 	\and
 	Yichao Zhou\\
-	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}\\
-	Tsinghua University.
+	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}
 	\and
 	Qiwei Feng\\
-	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}\\
-	Tsinghua University.
+	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}
 	\and
 	Yu Yan\\
-	\href{mailto:}{}\\
-	Tsinghua University.
+	\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com}
 	\and
 	Qingyang Li\\
-	\href{mailto:}{}\\
-	Tsinghua University.
+	\href{mailto:591527324@qq.com}{591527324@qq.com}
 	\and
 	Xin Xing\\
-	\href{mailto:}{}\\
-	Tsinghua University.
+	\href{mailto:823291634@qq.com}{823291634@qq.com}
 }
-\date
-{
-	June 25, 2013
-}
+\date{}
 %>>>
@@
 \begin{abstract}
-
+We address the dynamic properties of typical social networks, in which person
+is considered to be vertex while friendship is considered to be edge.
 \end{abstract}

### 2013-06-20 network-science/paper.tex
3

@@
 {
-	Metrics and Algorithms for Envolving Social Networks
+	Metrics and Algorithms for Evolving Social Networks
 }
@@
 We address the dynamic properties of typical social networks, in which person
-is considered to be vertex while friendship is considered to be edge.
+is considered to be vertex while friendship is considered to be edge. We
+suppose the evolution of a social network overtime only includes bidirectional
+new connections between exsisting or newly created nodes, and we assume the
+graph will evolve as a typical social network. We study the centrality and
+activity metrics for nodes in such graphs by regulate a series of reasonable
+properties the metrics should satisfy. We then formally define our metrics and
+give their mathematical analysis. We have developped a practical based
+framework to maintain the evolving network and the algorithm to compute our
+metrics with preferable time and space consumption, including historical
+queries. Finally, we put the result of experiment with a couple of authentic
+data.
+
+\textbf{Keywords.} social network, dynamic graph, centrality, activity, algorithm. 
 \end{abstract}
@@
 \section{Introduction}
+social network
 \section{}

### 2013-06-20 network-science/paper.tex
5

@@
 We address the dynamic properties of typical social networks, in which person
-is considered to be vertex while friendship is considered to be edge. We
-suppose the evolution of a social network overtime only includes bidirectional
-new connections between exsisting or newly created nodes, and we assume the
-graph will evolve as a typical social network. We study the centrality and
-activity metrics for nodes in such graphs by regulate a series of reasonable
-properties the metrics should satisfy. We then formally define our metrics and
-give their mathematical analysis. We have developped a practical based
-framework to maintain the evolving network and the algorithm to compute our
-metrics with preferable time and space consumption, including historical
-queries. Finally, we put the result of experiment with a couple of authentic
-data.
+is considered as vertex while friendship is considered as edge. We suppose the
+evolution of a social network overtime only includes bidirectional new
+connections between existing or newly created nodes, and we assume the graph
+will evolve as a typical social network. We study the centrality and activity
+metrics for nodes in such graphs by regulate a series of reasonable properties
+the metrics should satisfy. We then formally define our metrics and give their
+mathematical analysis. We have developed a practical based framework to
+maintain the evolving network and the algorithm to compute our metrics with
+preferable time and space consumption, including historical queries. Finally,
+we put the result of experiment with a couple of authentic data.
 
-\textbf{Keywords.} social network, dynamic graph, centrality, activity, algorithm. 
+\smallskip
+\noindent \textbf{Keywords.} social network, dynamic graph, centrality,
+activity, algorithm.
 \end{abstract}

### 2013-06-20 network-science/paper.tex
6

@@
 
-%\pgfplotsset{compat=1.6}
+\pgfplotsset{compat=1.6}
 \usetikzlibrary{arrows}
@@
 \mathtoolsset{centercolon}
+\bibliographystyle{plain}
 
@@
 \date{}
+
 %>>>
@@
 We address the dynamic properties of typical social networks, in which person
-is considered as vertex while friendship is considered as edge. We suppose the
+is considered as vertex while relation is considered as edge. We suppose the
 evolution of a social network overtime only includes bidirectional new
@@
 \section{Conclusion}
-
+\nocite{*}
+\bibliography{paper.bib}
 \end{document}

### 2013-06-20 network-science/paper.tex

@@
-\documentclass[12pt]{scrartcl}
+\documentclass[12pt,abstract=true]{scrartcl}
 
@@
 \newcommand{\mathhuge}[1]{\mathlarger{\mathlarger{\mathlarger{#1}}}}
-% \newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}
+\newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}
+
+\newcommand\Mark[1]{\textsuperscript#1}
 \numberwithin{equation}{section}
@@
 %>>>
-\title %<<< Title Region
-{
-	Metrics and Algorithms for Evolving Social Networks
-}
-\author
-{
-	Pufan He\\
-	\href{mailto:hpfdf@126.com}{hpfdf@126.com}
-	\and
-	Yichao Zhou\\
-	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}
-	\and
-	Qiwei Feng\\
-	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}
-	\and
-	Yu Yan\\
-	\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com}
-	\and
-	Qingyang Li\\
-	\href{mailto:591527324@qq.com}{591527324@qq.com}
-	\and
-	Xin Xing\\
-	\href{mailto:823291634@qq.com}{823291634@qq.com}
-}
-\date{}
-
-%>>>
 
 \begin{document}
-\maketitle
-\newpage
+
+\begin{center}
+	\Large \textbf{\textsf{
+		Metrics and Algorithms for Evolving Social Networks}} \\[1.5em]
+	\small
+		Pufan He\Mark{1}, Yichao Zhou\Mark{2}, Qiwei Feng\Mark{3},
+		Yu Yan\Mark{4}, Qingyang Li\Mark{5} and Xin Xing\Mark{6}\\[1em]
+	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
+		\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
+		\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
+		\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
+
+		\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
+		\href{mailto:591527324@qq.com}{591527324@qq.com} &
+		\href{mailto:823291634@qq.com}{823291634@qq.com}
+	\end{tabular} \\[1em]
+
+	\normalsize IIIS, Tsinghua University \\[1em]
+\end{center} \par
+
 \begin{abstract}

### 2013-06-20 trunk/network-science/paper.tex

@@
-\documentclass[a4paper,twocolumn,10pt]{article}
+\documentclass[12pt,abstract=true]{scrartcl}
+
+%<<< Preamble
+\usepackage{tikz}
+\usepackage{array}
+\usepackage{pifont}
+\usepackage{engord}
+\usepackage{listings}
+\usepackage{titlesec}
+\usepackage{fancyhdr}
+\usepackage{fancyvrb}
 \usepackage{multicol}
-\usepackage{listings}
-\usepackage{fourier}
-\usepackage{amsmath}
+\usepackage{pgfplots}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage[plain]{fancyref}
+\usepackage[unicode]{hyperref}
+\usepackage{graphicx,tabularx}
+\usepackage[shortlabels]{enumitem}
+\usepackage[retainorgcmds]{IEEEtrantools}
+\usepackage{amsmath,amssymb,amsthm,amscd,amstext}
+\usepackage{mathtools}
+\usepackage{exscale}
+\usepackage{relsize}
+\usepackage{mathrsfs}
 
-\usepackage{tikz}
-\tikzstyle{every picture}+=[remember picture]
-\usetikzlibrary{arrows,decorations.pathreplacing,decorations.markings}
-\usepackage{listings}
-\lstset{
-	numbers=left,
-	basicstyle=\small\ttfamily,
-	numberstyle=\it\scriptsize\sffamily,
-	keywordstyle=\bf,
-	commentstyle=\color{red!50!green!50!blue!50},
-	frame=single,
-	%breaklines=true,
+\usepackage{setspace}
+\usepackage{lastpage}
+\usepackage{extramarks}
+\usepackage{chngpage}
+
+\usepackage{lmodern}
+\usepackage{mathpazo}
+
+\pgfplotsset{compat=1.6}
+\usetikzlibrary{arrows}
+\usetikzlibrary{patterns}
+\usetikzlibrary{positioning}
+\usetikzlibrary{automata}
+\usepackage{tikz-3dplot}
+
+\tikzset{ alert/.style={ very thick, draw=red!80, fill=red!20 } }
+\tikzset{ fancy/.style={ very thick, draw=blue!80, fill=blue!20 } }
+\tikzset{
+  dot/.style={
+    very thick,circle,draw=black,fill=black,inner sep=0,minimum size=5pt
   }
+}
+\tikzset { every state/.style={fancy} }
+\tikzset {
+  general/.style = {
+    shorten >=2pt, node distance=2.5cm, on grid, thick,>=stealth', auto
+  }
+}
+\newcommand{\mathhuge}[1]{\mathlarger{\mathlarger{\mathlarger{#1}}}}
+\newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}
 
-\usepackage{geometry}
-\geometry{left=0.7cm,right=0.7cm,top=0.7cm,bottom=1.3cm}
-%\linespread{1.0}
+\newcommand\Mark[1]{\textsuperscript#1}
+\numberwithin{equation}{section}
+\mathtoolsset{centercolon}
+\bibliographystyle{plain}
 
-\AtBeginDocument{%
-	\setlength\abovedisplayskip{3pt}
-	\setlength\belowdisplayskip{3pt}
-}
-\usepackage{titlesec}
-\titlespacing{\section}{0pt}{5pt}{5pt}
-\titlespacing{\subsection}{0pt}{5pt}{5pt}
-\titlespacing{\subsubsection}{0pt}{5pt}{3pt}
+% Theorem environment <<<
+\theoremstyle{definition}   \newtheorem{definition}{Definition}[section]
+\theoremstyle{plain}        \newtheorem{theorem}{Theorem}[section]
+\theoremstyle{plain}        \newtheorem{observation}{Observation}[section]
+\theoremstyle{plain}        \newtheorem{fact}{Fact}[section]
+\theoremstyle{plain}        \newtheorem{claim}{Claim}[section]
+\theoremstyle{plain}        \newtheorem{lemma}[theorem]{Lemma}
+\theoremstyle{plain}        \newtheorem{corollary}[theorem]{Corollary}
+\theoremstyle{remark}       \newtheorem{example}{Example}[section]
+\theoremstyle{remark}       \newtheorem{remark}{Remark}[section]
+\newcommand*{\fancyrefdeflabelprefix}{def}
+\newcommand*{\fancyrefthmlabelprefix}{thm}
+\newcommand*{\fancyreflemlabelprefix}{lem}
+\newcommand*{\fancyrefcorlabelprefix}{cor}
+\newcommand*{\fancyrefalglabelprefix}{alg}
+\newcommand*{\fancyreflnlabelprefix}{ln}
+\frefformat{plain}{\fancyreflnlabelprefix}{line #1}
+\Frefformat{plain}{\fancyreflnlabelprefix}{Line #1}
+\frefformat{plain}{\fancyrefalglabelprefix}{algorithm (#1)}
+\Frefformat{plain}{\fancyrefalglabelprefix}{Algorithm (#1)}
+\frefformat{plain}{\fancyrefdeflabelprefix}{definition (#1)}
+\Frefformat{plain}{\fancyrefdeflabelprefix}{Definition (#1)}
+\frefformat{plain}{\fancyrefthmlabelprefix}{theorem (#1)}
+\Frefformat{plain}{\fancyrefthmlabelprefix}{Theorem (#1)}
+\frefformat{plain}{\fancyreflemlabelprefix}{lemma (#1)}
+\Frefformat{plain}{\fancyreflemlabelprefix}{Lemma (#1)}
+\frefformat{plain}{\fancyrefcorlabelprefix}{corollary (#1)}
+\Frefformat{plain}{\fancyrefcorlabelprefix}{Corollary (#1)}
+%>>>
+% Alter some LaTeX Float for better treatment of figures: <<<
+% See p.105 of "TeX Unbound" for suggested values.
+% See pp. 199-200 of Lamport's "LaTeX" book for details.
+%   General parameters, for ALL pages:
+\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
+\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}     % 2 may work better
+\setcounter{dbltopnumber}{2}    % for 2-column pages
+\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
+\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
+\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
+\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\allowdisplaybreaks[4]
 
-\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
-\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
-\newcommand{\ang}[1]{\left\langle {#1} \right\rangle}
-\newcommand{\lc}{\left(}
-\newcommand{\rc}{\right)}
-\newcommand{\parentheses}[1]{\left({#1}\right)}
-\newcommand{\pte}[1]{\left({#1}\right)}
-\newcommand{\labs}{\left|}
-\newcommand{\rabs}{\right|}
-\newcommand{\abs}[1]{\left|{#1}\right|}
-\newcommand{\op}{\operatorname}
-\newcommand{\E}{\operatorname{E}}
-\newcommand{\spt}{\operatorname{support}}
-\newcommand{\mA}{\mathcal{A}}
-\newcommand{\mB}{\mathcal{B}}
-\newcommand{\mC}{\mathcal{C}}
-\newcommand{\mD}{\mathcal{D}}
-\newcommand{\mE}{\mathcal{E}}
-\newcommand{\mJ}{\mathcal{J}}
-\newcommand{\mK}{\mathcal{K}}
-\newcommand{\mL}{\mathcal{L}}
-\newcommand{\mM}{\mathcal{M}}
-\newcommand{\mU}{\mathcal{U}}
-\newcommand{\mV}{\mathcal{V}}
-\newcommand{\mW}{\mathcal{W}}
-\newcommand{\mX}{\mathcal{X}}
-\newcommand{\bR}{\mathbb{R}}
-\newcommand{\bZ}{\mathbb{Z}}
-\newcommand{\bN}{\mathbb{N}}
-\newcommand{\bC}{\mathbb{C}}
-\newcommand{\uge}{\succcurlyeq}
-\newcommand{\Tr}{\op{Tr}}
-\newcommand{\dd}{\mathrm{d}}
+%>>>
+%>>>
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
-%\begin{multicols}{3}
-\section*{\textsc{Net Science}'s Sheet {\large by Feng Qiwei}}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Biblographic Coupling}
-	B.C. of $(i,j)$ is $\#$ of other nodes to which both $i,j$ point:
-	$B=A^T A$.
+\begin{center} %<<< Title
+	\Large \textbf{\textsf{
+		Metrics and Algorithms for Evolving Social Networks}} \\[1.5em]
+	\small
+		Pufan He\Mark{1}, Yichao Zhou\Mark{2}, Qiwei Feng\Mark{3},
+		Yu Yan\Mark{4}, Qingyang Li\Mark{5} and Xin Xing\Mark{6}\\[1em]
+	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
+		\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
+		\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
+		\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
 
-\subsection{Degree}
-	\[
-		k_i=\# \textrm{ of edges connected to }i, \\
-	\]
-	\[
-		\rho(G)=\frac{m}{\binom{n}{2}} = \frac{c}{n-1}\textrm{ where }c=\ang{k_i}.
-	\]
+		\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
+		\href{mailto:591527324@qq.com}{591527324@qq.com} &
+		\href{mailto:823291634@qq.com}{823291634@qq.com}
+	\end{tabular} \\[1em]
 
-\subsection{Transitivity}
-	\[
-	\textrm{clustering cofficient} =
-		\frac{\#\textrm{ closed paths of len 2}} {\#\textrm{ paths of len 2}}, \\
-	\]
-	\[
-	\textrm{local c.c.} =
-		\frac{\#\textrm{ pairs of connected neighbors}} {\#\textrm{ pairs of neighbors}}.
-	\]
+	\normalsize IIIS, Tsinghua University \\[1em]
+\end{center} \par %>>>
 
-\subsection{Centrality}
-	\subsubsection{Eigenvector}
-		Let $x(t)=A^t x(0)$ where $x(0)=\sum_i c_i v_i$,
-		then $x(t)=\sum_i c_i \lambda_i^t v_i=\lambda_1^t \sum_i c_i (\lambda_i/\lambda_1)^tv_i$.
-		For $t\to\infty$, know $(\lambda_i/\lambda_1)^t\to 0$ so $x(t)\to c_1\lambda_1^t v_1$, so
-		\[
-			\pte{Ax = \lambda_1 x} \Longrightarrow
-			\pte{x_i=\lambda_1^{-1} \sum_j A_{ij} x_j}.
-		\]
-		\textbf{Prob.}
-		Only vertices in out-component(s) of SCC of two or more vertices can have
-			non-zero E.C..
+\begin{abstract}
+We address the dynamic properties of typical social networks, in which person
+is considered as vertex while relation is considered as edge. We suppose the
+evolution of a social network overtime only includes bidirectional new
+connections between existing or newly created nodes, and we assume the graph
+will evolve as a typical social network. We study the centrality and activity
+metrics for nodes in such graphs by regulate a series of reasonable properties
+the metrics should satisfy. We then formally define our metrics and give their
+mathematical analysis. We have developed a practical based framework to
+maintain the evolving network and the algorithm to compute our metrics with
+preferable time and space consumption, including historical queries. Finally,
+we put the result of experiment with a couple of authentic data.
 
-	\subsubsection{Katz}
-		\[
-			\pte{x_i = \alpha\sum_j A_{ij} x_j + \beta}
-			\Longleftrightarrow
-			\pte{x=\alpha Ax+\beta 1}.
-		\]
-		Set $\beta=1$ (should have $\alpha<\lambda_1^{-1}$):
-			$x=(I-\alpha A)^{-1} \cdot 1$.
+\smallskip
+\noindent \textbf{Keywords.} social network, dynamic graph, centrality,
+activity, algorithm.
+\end{abstract}
 
-	\subsubsection{Pagerank}
-		\[
-			\pte{x_i = \alpha \sum_j A_{ij} \frac{x_j}{k_j^{out}} + \beta}
-			\Longleftrightarrow
-			\pte{x=D(D-\alpha A)^{-1}\cdot \beta1}.
-		\]
-
-	\subsubsection{Hubs and Authorities}
-		\[
-			x=\alpha A y, y=\beta A^T x.
-		\]
-
-	\subsubsection{Closeness}
-		\[
-			d_{ij}=\textrm{ len of SP bet. $i$ and $j$},
-			\textrm{~~~~}
-			l_i=\frac{1}{n-1} \sum_{j\neq i} d_{ij},
-			\textrm{~~~~}
-			c_i=\frac{1}{l_i}.
-		\]
-
-	\subsubsection{Betweeness}
-		\[
-			n_{s,t}^i=\#\textrm{ of SP $s\to t$ through $i$},
-			\textrm{~~~~}
-			g_{s,t}=\#\textrm{ of SP $s\to t$},
-		\] \[
-			\textrm{B.C. of $i$}=x_i=\sum_{s,t} \frac{n_{s,t}^i}{g_{s,t}}.
-		\]
-
-	\subsubsection{Flow}
-		\[
-			x_i = \sum_{s,t} m_{s,t},
-			\textrm{~~~~}
-			m_{s,t}=\textrm{ flow through $i$ in a max $s$-$t$ flow}.
-		\]
-
-\subsection{Similarity}
-	\textbf{Structral s.:} if share many of the same neighbors.
-	\textbf{Regular s.:} if neighbors are similar.
-
-	\subsubsection{Consine}
-		\[
-			\sigma_{ij} = \frac{\sum_k A_{ik} A_{kj}} {\sqrt{\sum_k A_{ik}^2}\sqrt{\sum_k A_{kj}^2}}
-			=\textrm{(in unweight G)}=\frac{n_{ij}}{\sqrt{k_i k_j}}.
-		\]
-	\subsubsection{Pearson Coefficients}
-		\[ \begin{split}
-			\op{cov}(A_i,A_j)
-			&= \#\textrm{common neighbors} - \#\textrm{exp. com. neighs} \\
-			&= \sum_k A_{ik} A_{jk} - \frac{k_i k_j}{n} 
-			= \sum_k \pte{A_{ik}-\ang{A_i}} \pte{A_{jk}-\ang{A_j}}, \\
-		\end{split} \]
-		\[ \begin{split}
-			r_{ij}
-			&= \textrm{standard Pearson corellation coefficient} \\
-			&= \frac{\sum_k \pte{A_{ik}-\ang{A_i}} \pte{A_{jk}-\ang{A_j}}}
-				{\sqrt{\pte{A_{ik}-\ang{A_i}}^2} \sqrt{\pte{A_{jk}-\ang{A_j}}^2}}. \\
-		\end{split} \]
-
-\subsection{Homiphily and Assortive Mixing}
-	\subsubsection{A.M. by Enumerative Characteristics}
-		\[ \begin{split}
-			Q &= \textrm{modularity} \\
-			&= \frac{1}{m} \pte{\#\textrm{same type edges} - \#\textrm{exp. same type edges}} \\
-			&= \frac{1}{2m} \sum_{ij} \pte{A_{ij} - \frac{k_i k_j}{2m}} \delta(c_i,c_j)
-			=\sum_r e_{rr} - a_r^2. \\
-			e_{rs} &= \frac{1}{2m} \sum_{ij} A_{ij} \delta(c_i,r) \delta(c_j,s), \\
-			a_r &= \frac{1}{2m} \sum_i k_i \delta(c_i,r). \\
-		\end{split} \]
-
-	\subsubsection{A.M. by Scalar Characteristics}
-		\[ \begin{split}
-			r &= \textrm{assortativity coefficient} \\
-			&= \frac{\textrm{covariances over nodes}}{\textrm{cov. in perfectly mixed network}} \\
-			&= \frac{\sum_{ij} \pte{A_{ij} - k_i k_j / 2m} x_i x_j}
-				{\sum_{ij} \pte{k_i \delta_{ij} - k_i k_j /2m} x_i x_j}.
-		\end{split} \]
-
-\subsection{Power Law Distribution}
-	\[
-		p_k = C k^{-\alpha} \textrm{ where $\alpha$ in $[2,3]$ are typical}.
-	\]
-	\[
-		P_k = \sum_{i=k}^\infty p_i
-			\approx C \int_k^\infty x^{-\alpha} \dd x
-			=\frac{C}{\alpha-1} k^{-(\alpha-1)}.
-	\]
-	\[ \begin{split}
-		\alpha &= 1 + N\left[ \sum_i \ln \frac{k_i}{k_{min} - 1/2} \right]^{-1}, \\
-		\sigma &= \sqrt{N} \left[ \sum_i \ln \frac{k_i}{k_{min} - 1/2} \right]^{-1}
-			= \frac{\alpha-1}{\sqrt{N}}.
-	\end{split} \]
-
-\subsection{Graph Laplacian}
-	Diffusion $\frac{\dd \psi_i}{\dd t}=c \sum_j A_{ij} (\psi_j-\psi_i)
-		=c\sum_j(A_{ij}-\delta_{ij}k_i)\psi_j
-		\Longrightarrow \frac{\dd \psi}{\dd t}=c(A-D)\psi$.
-	Define $L=D-A$, then $\frac{\dd \psi}{\dd t}+cL\psi=0$.
-	Need to solve $\psi(t)=\sum_i a_i(t) v_i$.
-	Have $\sum_i (\frac{\dd a_i}{\dd t} + c\lambda_i a_i) v_i = 0$,
-	then $\frac{\dd a_i}{\dd t} + c \lambda_i a_i=0$ since $v_i\perp v_j$.
-	So $a_i(t)=a_i(0) e^{-c\lambda_i t}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Big Things}
-
-\subsection{Random Graph}
-	\subsubsection{Poisson Random Graph}
-		Poisson r. g. $G(n,p)$:
-		$n$ nodes where $\forall u,v$, $\Pr[\exists (u,v)\in G]=p$:
-		\begin{itemize}
-			\item mean $\#$ edges: $\binom{n}{2} p$;
-			\item avg. deg.: $(n-1)p=c$;
-			\item deg. distr.: $p_k=\binom{n-1}{k} p^k (1-p)^{n-1-k}$,
-				and for large $n$: $p_k=e^{-c} \frac{c^k}{k!}$ (Poisson deg. distr.);
-			\item cluster coefficient $= p = \frac{c}{n-1} \to 0$.
-		\end{itemize}
-
-	\subsubsection{Giant Component}
-		$u$: fraction of vertices that do \textbf{NOT} belong to the giant $T$.
-		If $i\notin T$, then $\forall j$, either
-		\begin{itemize}
-			\item $i$ is not connected to $j$: $1-p$;
-			\item $i$ is connected to $j$ but $j\notin T$: $pu$.
-		\end{itemize}
-		Total: $1-p+pu$. Probability that $i\notin T$ is
-		\[
-			u=(1-p+pu)^{n-1}=\pte{1-\frac{c}{n-1}(1-u)}^{n-1},
-		\]
-		%= (n-1) \ln\pte{1-\frac{c}{n-1}(1-u)}
-		\[
-			\ln u 
-			\approx -(n-1) \frac{c}{n-1} (1-u) = -c(1-u)
-		\]
-		\[
-			\Longrightarrow u=e^{-c(1-u)}
-			\Longrightarrow 1-u=S=1-e^{-cS}.
-		\]
-		Phase transition takes place when
-		\[
-			\left.\frac{\dd}{\dd S} \pte{1-e^{-cS}} = c e^{-cS} = 1 \right|_{S=0}
-			\Longrightarrow c=1.
-		\]
-		Core $C(Q)$ and periphery $P(Q)$: $s=|C(Q)|+|P(Q)|$.
-		A node in $P(Q)$ has $p(n-s)\approx c$ neighbors outside, so
-		\[
-			P(Q') \approx c P(Q), C(Q') = Q.
-		\]
-		If $c>1$, periphery grows; if $c<1$, it shrinks.
-
-	\subsubsection{Small Components}
-		$\pi_s$: prob that a randomly selected node belongs to a small component of size $s$.
-		Fraction of nodes not in the giant: $\sum_{s=0}^\infty \pi_s = 1-S$.
-
-		Observation: s.c. are trees.
-		Consider tree of $s$ nodes.
-		Remain place of edge: $\binom s 2 - (s-1) = \frac 1 2 (s-1)(s-2)$,
-			so exp $\#$ non-tree edges: $\frac 1 2 (s-1)(s-2) p =
-			\frac 1 2 (s-1)(s-2) c / (n-1) \to 0$,
-			if $s$ increase slowly than $\sqrt n$.
-
-		Consider $i$'s neighbors $n_1,...,n_k$ with component size $s_1,...,s_k$.
-		$P(s|k)$: $i$ belongs to component of size $s$.
-		\[
-			P(s|k)=\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j).
-		\]
-		Know $\pi_s = \sum_{k=0}^\infty p_k P(s|k)$.
-		(Generating function now!)
-		Let $h(z)=\sum_{s=1}^\infty \pi_s z^s$,
-			then $\pi_s=\left. \frac{1}{s!} \frac{\dd^s h}{\dd z^s} \right|_{z=0}$.
-		Consider $h(z)$:
-		\[ \begin{split}
-			h(z) &= \sum_{s=1}^\infty z^s \sum_{k=0}^\infty p_k
-			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j) \\
-			&= \sum_{s=1}^\infty z^s e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
-			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j}} \delta(s-1,\sum_j s_j) \\
-			&= e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
-			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j}} z^{1+\sum_j s_j} \\
-			&= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
-			\sum_{s_1=1}^\infty ... \sum_{s_k=1}^\infty
-			\pte{\prod_{j=1}^k \pi_{s_j} z^{s_j}} \\
-			&= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!}
-			\pte{\sum_{s=1}^\infty \pi_{s} z^{s}}^k 
-			= z e^{-c} \sum_{k=0}^\infty \frac{c^k}{k!} h^k(z) 
-			= z e^{c(h(z)-1)}.
-		\end{split} \]
-
-		No closed-form solution for $h(z)$.
-		$\ang{s}=\frac{\sum_s s\pi_s}{\sum_s \pi_s}=\frac{h'(1)}{1-S}$.
-		Know
-		\[
-			h'(z)=e^{c(h(z)-1)} + czh'(z)e^{c(h(z)-1)} = \frac{h(z)}{z} + ch(z)h'(z)
-		\]
-		\[
-			\Longrightarrow h'(z)=\frac{h(z)}{z(1-ch(z))}.
-		\]
-		$h(1)=\sum_s \pi_s=1-S \Longrightarrow \ang{s}=\frac{1}{1-c+cS}$.
-		If $c<1$, no giant so $\ang{s}=\frac{1}{1-c}$.
-
-		$n_s$: $\#$ components of size $s$. $\pi_s = s n_s/n$.
-		Avg size of component: $$R=\frac{\sum_s s n_s}{\sum_s n_s}
-			= \frac{n \sum_s \pi_s}{n \sum_s \pi_s / s}
-			= \frac{1-S}{\sum_s \pi_s/s}.$$
-		Noting that
-		\[
-			\int_0^1 \frac{h(z)}{z} \dd z = \sum_{s=1}^\infty \int_0^1 z^{s-1} \dd z
-			= \sum_{s=1}^\infty \frac{\pi_s}{s}.
-		\]
-		Have $\frac{h(z)}{z} = (1-ch(z)) \frac{\dd h}{\dd z}$,
-			so $$\sum_{s=1}^\infty \frac{\pi_s}{s}
-			=\int_0^1 (1-ch(z)) \frac{\dd h}{\dd z} \dd z
-			=\int_0^{1-S}(1-ch) \dd h = 1-S-\frac 1 2 c(1-S)^2.$$
-		(Upper integration limit $ = h(1)= 1-S$.)
-		Finally $R=\frac{2}{2-c+cS}$.
-		(\textbf{NOTE:}
-		$G(n,p)$ is connected if $p(n)=\frac{\log n}{n}$,
-			then diameter $D=A+\frac{\ln n}{\ln c}$.)
-
-	\subsubsection{Configuration Model}
-		Specify degree distr $p$, randomly pick endpoints to form edges.
-
-\subsection{Preferential Attachment}
-	Each new paper cite $c$ old papers randomly:
-	\[ \begin{split}
-		p_q(n) &= \textrm{fraction of nodes with deg $q$}, \\
-		q_i &= \textrm{in-degree of node $i$}, \\
-	\end{split} \]
-	\[
-		\Pr[i\textrm{ get citation}] = \frac{q_i+a}{\sum_j (q_j+a)} = \frac{q_i+a}{n(c+a)}. \\
-	\]
-	\[
-		\E[\textrm{new cites deg $q$ nodes}]
-			=n p_q(n) c \frac{q+a}{n(c+a)} = \frac{c(q+a)}{c+a} p_q(n).
-	\]
-	\subsubsection{Master Equation}
-		\[ \begin{split}
-			(n+1)p_q(n+1)&=np_q(n)
-				+\frac{c(q-1+a)}{c+a}p_{q-1}(n)- \frac{c(q+a)}{c+a}p_q(n) \\
-			(n+1)p_0(n+1)&=np_0(n)+1-\frac{ca}{c+a}p_0(n).
-		\end{split} \]
-		\[
-			n\to\infty\Longrightarrow
-			p_0=\frac{1+\frac{a}{c}}{a+1+\frac{a}{c}},
-			p_q=\frac{q+a-1}{q+a+1+\frac{a}{c}}p_{q-1},
-		\]
-		\[
-			\Longrightarrow
-			p_q=\frac{(q+a-1)(q+a-2)\cdots a}{(a+a+1+\frac{a}{c})\cdots(a+1+\frac{a}{c})}.
-		\]
-		% TODO: Gamma Beta
-		For large $q$,
-			$p_q\sim (q+a)^{-\alpha}$ or simply $p_q\sim q^{-\alpha}$,
-			where $\alpha=2+\frac{a}{c}$.
-
-	\subsubsection{Mean-Field Approximation}
-		One link with $p$ choose uniform, $q=1-p$ choose by P.A..
-		\[ \begin{split}
-			x_i(t) &= \textrm{in-degree of $i$ at time $t$ with $x_i(i)=0$}, \\
-			\Delta_t &= \E[x_i(t+1)-x_i(t)]  = \frac{p}{t} + \frac{(1-p)x_i(t)}{t}.
-		\end{split} \]
-		Consider a deterministic process in which a nodes degree increased by exact $\Delta_t$.
-		Find distribution of expected degrees.
-		\[
-			d_i(i) = 0, \frac{\partial d_i(t)}{\partial t} = \frac{p}{t} + \frac{(1-p)d_i(t)}{t}.
-		\]
-		\[
-			\Longrightarrow \int \frac{1}{p+q d_i} \frac{\partial d_i}{\partial t} \dd t = \int \frac{1}{t} \dd t \\
-		\] \[
-			\Longrightarrow \ln(p+q d_i) = q \ln t + c \\
-		\] \[
-			\Longrightarrow p+q d_i = A t^q, \\
-		\] \[
-			\textrm{set $d_i(i)=0$,}\Longrightarrow d_i(t) = \frac{p}{q}\pte{\pte{\frac{t}{i}}^q-1}.
-		\]
-		$i_t(k)$: node with expected degree exactly $k$ at time $t$:
-		\[
-			d_{i_t(k)}(t) = k = \frac{p}{q}\pte{\pte{\frac{t}{i_t(k)}}^q-1}
-			\Longrightarrow
-			i_t(k)=t\pte{\frac{p}{q}k+1}^{-\frac{1}{q}}.
-		\]
-		Fraction of nodes with degree $>k$:
-			$F_k(t) = \pte{\frac{q}{p}k+1} ^ {-\frac{1}{q}}$,
-		\[
-			\Longrightarrow
-			p_k=-\frac{\partial F_k}{\partial k}
-			=\frac{1}{p}\pte{\frac{q}{p}k+1}^{-1-\frac{1}{q}}
-			\sim k^{-\pte{1+\frac{1}{q}}}.
-		\]
-
-\subsection{Small World}
-	Each node is connected with all neighbors of distance $\le c/2$.
-	For $nc/2$ times pick random pair and add shortcut w.p. $p$.
-
-	\subsubsection{Degree Distribution}
-		\[
-			k_i = c + s_i = c + (\#\textrm{shortcuts attacked to $v_i$}).
-		\]
-		There are $ncp$ endpoints of shortcuts. $s_i$ is Poisson distributed
-			with mean $cp$:
-		\[
-			p_s = e^{-cp}\frac{(cp)^s}{s!} \Longrightarrow
-			p_k = e^{-cp}\frac{(cp)^{k - c}}{(k - c)!}, \textrm{ for }k \ge c.
-		\]
-
-	\subsubsection{Clustering Coefficient}
-		$C=(\#\textrm{triangles}\times 3)/(\#\textrm{connected tripes})$.
-		\begin{enumerate}
-			\item $\#$ triangles
-			\begin{enumerate}
-				\item in ring: $n\binom{c/2}{2}=\frac{1}{4}nc(\frac{c}{2} - 1)$.
-				\item due to shortcuts:
-					prob $u,v$ connected by shortcut$=\frac{ncp/2}{n(n-1)/2}\approx \frac{cp}{n}$.
-					A shortcut complete a triangle for $u,v$ with dist $\frac{c}{2}\sim c$,
-						$\#$ of such $u,v$ is proportional to $n$.
-					$\Longrightarrow \sim n\cdot \frac{cp}{n} = cp =$
-					const $\to$ ignore.
-
-			\end{enumerate}
-			\item $\#$ connected tripes
-			\begin{enumerate}
-				\item in ring: $n\binom{c}{2}=\frac{1}{2}nc(c - 1)$.
-				\item through shortcuts: $(ncp/2)\times 2\times c$.
-				\item through pairs of shortcuts: for node with $m$ shortcuts,
-					has $\binom{m}{2}$ triples.
-					Let $m=cp$ (mean of Poisson distr) then total triples
-					$=(nc^2p^2)/2$.
-			\end{enumerate}
-		\end{enumerate}
-		\[
-			C=\frac{3(c-2)}{4(c-1)+8cp+4cp^2}.
-		\]
-
-	\subsubsection{Path length}
-		No exact expr for mean distance in WS model.
-		Consider $c=2$. Let $l=$ average len of SP.
-		$s=\#$ shortcuts.
-
-		Avg dist between shortcuts on ring $\tau=\frac{n}{2s}$
-			$\Longrightarrow$ $n,\tau$ completely specify the model.
-
-		Consider dimensionless $\frac{l}{n}$.
-		$\frac{l}{n}=F(\frac{n}{\tau})=F(2s)$
-		($F$: universal).
-		If density of shortcuts is low then for general $c$:
-		$l=\frac{2n}{c} F(2s) = \frac{n}{c} f(ncp)$.
-		Simulate $f$:
-		\[
-			f(x) = \frac{2}{\sqrt{x^2+4x}}\op{tanh}^{-1}\sqrt{\frac{x}{x+4}}
-		\]
-		\[
-			\Rightarrow x\to\infty
-			\Rightarrow f(x) = \frac{\ln x}{x}
-			\Rightarrow l = \frac{\ln(ncp)}{c^2p}.
-		\]
-
-	\subsubsection{Milgram}
-		Short paths exists and can be found efficiently in decentralized way.
-		WS model: $c=2$; $K=$ nodes with dist $\le\sqrt{n}$ of $t$.
-		$\Pr[\textrm{a shortcut points into $K$}]=2/\sqrt{n}$
-			$\to$ need at least $\sqrt{n}/2$ steps into $K$.
-		Crossing $K$ step-by-step at least $\sqrt{n}/2$ steps.
-		Thus need $\Omega(\sqrt n)$ steps.
-
-	\subsubsection{Kleinberg}
-		Choose shortcuts s.t.
-			$\Pr[\textrm{shortcut between $u,v$ at dist $r$}]=\kappa r^{-\alpha}$.
-		Choose shortcut len from distribution.
-		Place edge randomly in network.
-		Total prob that shortcut between two nodes is $p\kappa r^{-\alpha}$.
-		Normalization const $\kappa$:
-		\[
-			\kappa\sum_{r = 1}^{\frac{1}{2}(n - 1)}r^{-\alpha} = 1.
-		\]
-		We can approximate the sum:
-		\[
-			\sum\limits_{r= 1}^{\frac{1}{2}(n - 1)} r^{-\alpha}
-			\approx\int_{1}^{\frac{1}{2}(n - 1)} r^{-\alpha}\dd r
-			+\frac{1}{2}+\frac{1}{2}\pte{\frac{1}{2}(n - 1)}^{-\alpha},
-		\]
-		where $\int_{1}^{(n - 1)/2} r^{-\alpha}\dd r=((n-1)/2)^{1-\alpha}/(1-\alpha)$.
-		For $n\to\infty$:
-		\[
-			\kappa\approx\left\{\begin{array}{ll}
-				(1-\alpha)(\frac{1}{2}n)^{\alpha - 1} &\alpha<1\\
-				\ln^{-1}(\frac{1}{2}n) &\alpha = 1\\
-				\frac{2(\alpha-1)}{\alpha+1} &\alpha>1
-			\end{array}\right..
-		\]
-		Divide nodes into classes that $C_k$ consists of $v_i$ with
-			$2^{k-1}\le d(v_i,t)<2^k$.
-		Nodes in $C_0,...,C_{k-1}$:
-			$\sum_{m=0}^{k-1}n_m = \sum_{m=0}^{k-1}2^m = 2^k-1 > 2^{k-1}$.
-		All these are at most a dist $3 * 2^k < 2^{k+2}$ from $v_{\mathrm{cur}}$ in $C_k$.
-		Prob of having a shortcut to one of the nodes:
-		\[
-			p\kappa 2^{-(k+2)\alpha}*2^{k-1}=p\kappa 2^{k-1-(k+2)\alpha}.
-		\]
-		If $v_{\mathrm{cur}}$ has no shortcut, pass msg to neighbor.
-		Exp $\#$ moves until find a shortcut to $C_0,...,C_{k-1}$ is 
-		\[
-			\frac{1}{p\kappa} 2^{2\alpha+1} 2^{(\alpha-1)k}.
-		\]
-		In wrost case msg goes through all classes:
-		\[
-			l \le \frac{1}{p\kappa}*2^{2\alpha+1}*
-				\sum_{k=0}^{\log(m+1)}2^{(\alpha-1)k}
-			= \frac{1}{p\kappa}*2^{2\alpha+1}
-				\frac{(2(n+1))^{\alpha-1}-1}{2^{\alpha-1}-1}.
-		\]
-		Plugging the value of $\kappa$ for $n\to\infty$:
-		\[
-			l=\left\{\begin{array}{ll}
-				A n^{1-\alpha} &\alpha<1\\
-				B \log^2 n &\alpha = 1\\
-				C n^{\alpha-1} &\alpha>1
-			\end{array}\right..
-		\]
-
-\subsection{Stable Outcome}
-	\subsubsection{Nash Bargain Solution}
-		$A$ and $B$ with outside option $x$ and $y$.
-		If $x+y>1$ then no agreement possible.
-		If $x+y\le 1$ then has surplus $s=1-x-y$.
-
-		NBS: devide surplus evenly.
-
-	\subsubsection{Stable Outcome}
-		$G=(V,E)$, edge weight $w:E\to R^+$. Each $v\in V$ is a player.
-
-		\textbf{Outcome}: matching $M$ among players and vector $x$
-			describing each players payoff.
-			$\forall(u,v)\in M$, $x_u+x_v=w_{u,v}$; $\forall u\notin M$, $x_u=0$.
-
-		\textbf{Stable outcome}: outcome with no unstable edge.
-
-		\textbf{Balanced outcome} (generalization of NBS):
-			$\forall (u,v)\in M$, split of money represents the NBS
-				for $u,v$ given the best outside option for $u,v$
-				provided by values in the rest of the network.
-
-		$\to$ A balanced outcome exists iff a stable outcome exists.
-
-		$\to$ A balanced outcome can be computed in poly-time.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Unknown}
-
-\subsection{Cascades}
-	\subsubsection{Network Effects \textsc{(Things That I Cannot Understand!)}}
-		Decisions: $\{R,A\}$;
-		States: $\{G,B\}$ w.p. $\{p,1-p\}$.
-		Payoffs: $0$ for reject and $(G ? v_g>0 : v_b<0)$ for accept
-			($p v_g + (1-p) v_b = 0$).
-
-		Signals: gets a private signal before decision:
-			$H$ (high sig) = "accepting is good",
-			$L$ (low) = "..is bad".
-			$\Pr[H|G]=\Pr[L|B]=q>1/2$, 
-			$\Pr[L|G]=\Pr[H|B]=1-q$.
-
-		Know sequence $S$ of independently generated signals.
-		$a=\# H\in S$, $b=\# L\in S$.
-		\[
-			\Pr[G|S]=\frac{\Pr[G]\Pr[S|G]}{\Pr[S]}
-				=\frac{pq^a(1-q)^b}{pq^a(1-q)^b+(1-p)(1-q)^aq^b}.
-		\]
-		For $a>b$, $\Pr[G|S]>p$.
-		For $a<b$, $\Pr[G|S]<p$.
-		For $a=b$, $\Pr[G|S]=p$.
-
-	\subsubsection{Economy with Network Effect}
-		When $z$-fraction of customers buy, ceservation price of $x$ is $r(x)f(z)$.
-		$r$: intrinsic interest ($r(1)=0$).
-		$f$: benefit (increasing in $z$, $f(0)=0$).
-
-		Everyone expect $z=0$ $\to$ R.P.$=0<p$ $\to$ no one will buy.
-		Everyone expect $z\in(0,1)$ $\to$ $0..z$ will buy
-			$\to$ R.P.$=r(z)f(z)=p$.
-		Stability: strong equlibrium OR tripping point.
-
-		If $[0,\hat z]$ buy, then $r(\hat z)=\frac{p^*}{f(z)} \Longrightarrow
-			\hat z=r^{-1}\pte{\frac{p^*}{f(z)}}$.
-		If $z\ge 0$ then $\hat z=g(z)$ where $g(z)=r^{-1}\pte{\frac{p^*}{f(z)}}$
-			for $\frac{p^*}{f(z)}\le r(0)$, $=0$ otherwise.
-
-		NOW, consider $f(0)>0$. Let $r(x)f(z)=(1-x)(1+az^2)$.
-		If exp $\hat z$ then $g(z)=r^{-1}\pte{\frac{p^*}{f(z)}}=1-\frac{p^*}{f(z)}$.
-		Samll changes in price can have big effects,
-		$\to$ slightly lower price $\tilde p,\tilde g(z)=$
-			shifts curve upwards $\to$ only one equlibrium remains.
-
-	\subsubsection{Network Cascades}
-		$A,B$ have qualities $a,b$.
-		Initially everyone except $S$ choose $B$.
-		A node adopts $A$ if at least $q=\frac{b}{a+b}$ of his neighbors adopt $A$.
-
-		\textbf{Def (Density of Cluster).}
-			Cluster $C\subseteq V$ is density $x$ if $\forall v\in C$,
-				$|N(v)\in C|/|N(v)| \ge x$.
-
-		\textbf{Thm.}
-			A complete cascade occurs iff $\nexists$ cluster of density $\ge 1-q$
-				in $G\setminus S$.
-
-		Given an infinite network,
-		the \textbf{cascade capacity} is largest threshold $q$ at which
-		$\exists$ finite set of initial adopters that cause a complete cascade.
-
-	\subsubsection{Compatibility}
-		Allow $AB$ (bilingual) with fixed cost $c$.
-		Set $b=1$ and scale $a$ and $c$.
-
-	\subsubsection{Locality in Networks}
-		$G=(V,E)$, each node is a decision maker.
-		Nodes have goal to compute min dominating set (greedy gives $O(\log n)$-approx,
-			better is NP-hard).
-		Every node knows its $k$-hoo neighbors.
-
-		\textbf{Thm.}
-		With local neighborhood info, no algorithm can approximate
-			MDS, MVC, MMatching within $\Omega(n^{c/k^2})$ and $\Omega(\Delta^{1/k})$
-			($\Delta=$max degree).
-
-		\textbf{Cor.}
-		In order to get a constant or poly-log approx, every algo has to  have knowledge
-			of $\Omega(\sqrt{\log n})$ or $\Omega(\log \Delta)$ neighborhood.
-
-\subsection{Epidemics}
-	\subsubsection{Branch Model}
-		Beginning: one person infected.
-		Step: each contacts $k$ person, infected w.p. $p$.
-		Claim: if $R_0=pk<1$ disease stop in finite steps.
-
-		Let $q_n=\Pr[\textrm{some person in level $n$ get infected}]$,
-		$q^*=\lim_{n\to\infty} q_n$.
-		Let $Y_{nj}=1$ iff $j$-th person in level $n$ get infected,
-			$X_n=\sum_j Y_{nj}$.
-		Then 
-		\[
-			\E[X_n]=\sum_{1\le j\le k^{n}} \E[Y_{nj}]=
-			\E[X_n]=\sum_{1\le j\le k^{n}} p^{n-1} = R_0^{n}.
-		\]
-		Since $\E[X_n]=\sum_{a\ge 1} \Pr[X_n\ge a]$,
-			know $q_n=\Pr[X_n\ge 1]\le \E[X_n]=R_0^n$.
-		Thus $q^*=0$ when $R_0<1$.
-
-		For $R_0>1$, have $q_n=(1-p q_{n-1})^k$.
-		Let $f(x)=1-(1-px)^k$, then $q^*=f(f(...f(1)))>0$. (Plot to see.)
-
-	\subsubsection{SI Model}
-		S=susceptible, I=infectious.
-		Assume all people are in a clique.
-		Let $S(t)=$number of S at time $t$, $X(t)=$number of I at $t$.
-		At each time, each person will meet another $\beta$ person.
-		\[ \begin{split}
-			\frac{\dd X}{\dd t} &= X \beta \frac{S}{n} \\
-			\frac{\dd S}{\dd t} &= -X \beta \frac{S}{n}. \\
-		\end{split} \]
-		Let $s=S/n,x=X/n$, have
-		\[
-			\pte{\frac{\dd x}{\dd t} = \beta(1-x)x}
-			\Longrightarrow
-			\pte{x(t)=\frac{x_0 e^{\beta t}}{1-x_0+x_0 e^{\beta t}}}.
-		\]
-
-	\subsubsection{SIR Model}
-		R=recovered. Let $\gamma=$ recover rate and $r=$ prop of recover people.
-		\[ \begin{split}
-			\frac{\dd s}{\dd t} &= -\beta s x \\
-			\frac{\dd x}{\dd t} &= \beta s x - \gamma x \\
-			\frac{\dd r}{\dd t} &= \gamma x.
-		\end{split} \]
-		Get differential eq which is hard to solve (only numerically):
-		\[
-			\frac{\dd r}{\dd t} =
-				r\pte{1-r-s_0 e^{-\beta r/\gamma}}.
-		\]
-
-	\subsubsection{Genealogy and Mitochondrial Eve}
-		$N=$ population. Consider $k$ individuals($k\ll N$).
-		\[
-		\Pr[\textrm{no collision}] = \pte{1-\frac{1}{N}} \pte{1-\frac{2}{N}}
-		... \pte{1-\frac{k-1}{N}} \approx 1 - \frac{k(k-1)}{2N} + O\pte{\frac{1}{N^2}}.
-		\]
-		Let $W_i$ be number of generations it takes to generate collision when
-			number of interesting nodes is $i$.
-		Then
-		\[
-			\E[W_i]\approx \frac{2N}{i(i-1)},
-		\]
-		\[
-			\E[W]=\E\left[\sum_{2\le i\le k} W_i\right]\approx 2N\pte{1-\frac{1}{k}}.
-		\]
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Appendix}
-\begin{align*}
-	&\sum_{k=a}^br^k=\frac{r^{b+1}-r^a}{r-1}\\
-	&\sum_{k=a}^bkr^k=\frac{r^{b+1}(br-b-1)-r^a(ar-a-r)}{(r-1)^2}\\
-	&\sum_{k=a}^bk^2r^k=\frac{r^{b+1}((br-b-1)^2+r)-r^a((ar-a-r)^2+r)}{(r-1)^3}\\
-	&\sum_{k=1}^nk^2=\frac{1}{6}n(n+1)(2n+1)\\
-	&\sum_{k=1}^nk^3=\frac{1}{4}n^2(n+1)^2\\
-	&\sum_{k=1}^nk^4=\frac{1}{30}n(n+1)(2n+1)(3n^2+3n-1)\\
-	&\sum_{k=1}^nk^5=\frac{1}{12}n^2(n+1)^2(2n+1)(2n^2+2n-1)\\
-	&k^{\overline{m}}=k(k+1)(k+2)\dots(k+m-1)\\
-	&\sum_{k=1}^nk^{\overline{m}}=\frac{n^{\overline{m+1}}}{m+1}\\
-\end{align*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\end{multicols}
-%\end{landscape}
-%\end{multicols}
+\section{Introduction}
+social network 
+\section{}
+\section{}
+\section{Conclusion}
+\nocite{*}
+\bibliography{paper.bib}
 \end{document}
 
-% vim: set ts=8 sw=8 noet sts=8 tw=79 indentexpr=:
+% vim: set ts=8 sw=8 noet sts=8 tw=79 indentexpr= fdm=marker foldmarker=<<<,>>>:

### 2013-06-20 trunk/network-science/paper.tex

@@
 
-\newcommand\Mark[1]{\textsuperscript#1}
+\newcommand\upper[1]{\textsuperscript#1}
 \numberwithin{equation}{section}
@@
 	\small
-		Pufan He\Mark{1}, Yichao Zhou\Mark{2}, Qiwei Feng\Mark{3},
-		Yu Yan\Mark{4}, Qingyang Li\Mark{5} and Xin Xing\Mark{6}\\[1em]
+		Pufan He\upper{1}, Yichao Zhou\upper{2}, Qiwei Feng\upper{3},
+		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin Xing\upper{6}\\[1em]
 	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
-		\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
-		\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
-		\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
+		\upper{1}\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
+		\upper{2}\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
+		\upper{3}\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
 
-		\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
-		\href{mailto:591527324@qq.com}{591527324@qq.com} &
-		\href{mailto:823291634@qq.com}{823291634@qq.com}
+		\upper{4}\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
+		\upper{5}\href{mailto:591527324@qq.com}{591527324@qq.com} &
+		\upper{6}\upper{1}\href{mailto:823291634@qq.com}{823291634@qq.com}
 	\end{tabular} \\[1em]
 
-	\normalsize IIIS, Tsinghua University \\[1em]
+	\normalsize IIIS, Tsinghua University \\[1.5em]
 \end{center} \par %>>>

### 2013-06-20 network-science/paper.tex
7

@@
-\documentclass[12pt,abstract=true]{scrartcl}
+\documentclass[a4,12pt,abstract=true]{scrartcl}
 
@@
 
-\begin{center}
+\begin{center} %<<< Title
 	\Large \textbf{\textsf{
@@
 	\small
-		Pufan He\Mark{1}, Yichao Zhou\Mark{2}, Qiwei Feng\Mark{3},
-		Yu Yan\Mark{4}, Qingyang Li\Mark{5} and Xin Xing\Mark{6}\\[1em]
-	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
-		\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
-		\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
-		\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
+		Pufan He\upper{1}, Yichao Zhou\upper{2}, Qiwei Feng\upper{3},
+		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin Xing\upper{6}\\[1em]
+	\begin{tabular}{*{3}{>{\centering}p{.3\textwidth}}}
+		\upper{1}\small\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
+		\upper{2}\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
+		\upper{3}\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
 
-		\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
-		\href{mailto:591527324@qq.com}{591527324@qq.com} &
-		\href{mailto:823291634@qq.com}{823291634@qq.com}
+		\upper{4}\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
+		\upper{5}\href{mailto:591527324@qq.com}{591527324@qq.com} &
+		\upper{6}\href{mailto:823291634@qq.com}{823291634@qq.com}
 	\end{tabular} \\[1em]
 
-	\normalsize IIIS, Tsinghua University \\[1em]
-\end{center} \par
+	\normalsize IIIS, Tsinghua University \\[1.5em]
+\end{center} \par %>>>
 
@@
 mathematical analysis. We have developed a practical based framework to
-maintain the evolving network and the algorithm to compute our metrics with
-preferable time and space consumption, including historical queries. Finally,
-we put the result of experiment with a couple of authentic data.
+maintain the evolving large-scale network and the algorithm to compute our
+metrics with preferable time and space consumption, including historical
+queries. Finally, we put the result of experiment with a couple of authentic
+data.
 
@@
 \section{Introduction}
-social network 
-\section{}
-\section{}
-\section{Conclusion}
+% TODO
+\subsection{Dynamic Metrics}
+% TODO
+\subsection{Algorithms}
+% TODO
+\section{Evolving Social Network}
+% TODO
+\subsection{Definition}
+% TODO
+\subsection{Properties}
+% TODO
+\section{Centrality and Activity}
+% TODO
+\subsection{Desiderata}
+% TODO
+\subsection{Design and Analysis}
+% TODO
+\section{Algorithm}
+% TODO
+\subsection{Maintaining the basic graph structure}
+% TODO
+\subsection{Historical Queries}
+% TODO
+\subsection{Computing Metrics}
+% TODO
+\subsection{Mining Significant Data}
+% TODO
+\subsection{Optimization and Parallelizability}
+% TODO
+\section{Experiment}
+% TODO
+\section{Conclusion and Perspective}
+% TODO
 \nocite{*}

### 2013-06-20 trunk/network-science/paper.tex
8

@@
 \usepackage{mathrsfs}
+\usepackage{tocloft}
 
@@
 \newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}
+
+\renewcommand\cftsecfont{\normalsize}
+\renewcommand\cftsecpagefont{\normalsize}
+\renewcommand\cftsecafterpnum{\par}
+\setlength{\cftbeforesecskip}{0.3em}
+
+\renewcommand\cftsubsecfont{\small}
+\renewcommand\cftsubsecpagefont{\small}
+\renewcommand\cftsubsecafterpnum{\par}
 
@@
 	\Large \textbf{\textsf{
-		Metrics and Algorithms for Evolving Social Networks}} \\[1.5em]
-	\small
+		Metrics and Algorithms for Evolving Social Networks}} \\[1.2em]
+	\normalsize 
 		Pufan He\upper{1}, Yichao Zhou\upper{2}, Qiwei Feng\upper{3},
 		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin Xing\upper{6}\\[1em]
-	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
-		\upper{1}\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
+	\small
+	\begin{tabular}{*{3}{>{\centering}p{.3\textwidth}}}
+		\upper{1}\small\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
 		\upper{2}\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
 		\upper{3}\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
-
 		\upper{4}\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
 		\upper{5}\href{mailto:591527324@qq.com}{591527324@qq.com} &
-		\upper{6}\upper{1}\href{mailto:823291634@qq.com}{823291634@qq.com}
+		\upper{6}\href{mailto:823291634@qq.com}{823291634@qq.com}
 	\end{tabular} \\[1em]
 
-	\normalsize IIIS, Tsinghua University \\[1.5em]
+	\small Institute for Interdisciplinary Information Sciences,
+	Tsinghua University \\[1.5em]
 \end{center} \par %>>>
@@
 mathematical analysis. We have developed a practical based framework to
-maintain the evolving network and the algorithm to compute our metrics with
-preferable time and space consumption, including historical queries. Finally,
-we put the result of experiment with a couple of authentic data.
+maintain the evolving large-scale network and the algorithm to compute our
+metrics with preferable time and space consumption, including historical
+queries. Finally, we put the result of experiment with a couple of authentic
+data.
 
 \smallskip
-\noindent \textbf{Keywords.} social network, dynamic graph, centrality,
+\noindent \textbf{Keywords:} social network, dynamic graph, centrality,
 activity, algorithm.
 \end{abstract}
+\tableofcontents
+\newpage
 
 \section{Introduction}
-social network 
-\section{}
-\section{}
-\section{Conclusion}
+% TODO
+\subsection{Dynamic Metrics}
+% TODO
+\subsection{Algorithms}
+% TODO
+\section{Evolving Social Network}
+% TODO
+\subsection{Definition}
+% TODO
+\subsection{Properties}
+% TODO
+\section{Centrality and Activity}
+% TODO
+\subsection{Desiderata}
+% TODO
+\subsection{Design and Analysis}
+% TODO
+\section{Algorithms}
+% TODO
+\subsection{Maintaining the basic graph structure}
+% TODO
+\subsection{Historical Queries}
+% TODO
+\subsection{Computing Metrics}
+% TODO
+\subsection{Mining Significant Data}
+% TODO
+\subsection{Optimization and Parallelizability}
+% TODO
+\section{Experiment}
+% TODO
+\section{Conclusion and Perspective}
+% TODO
 \nocite{*}

### 2013-06-21 trunk/network-science/paper.tex
x

@@
 \subsection{Dynamic Metrics}
-% TODO
+Centrality, usually defined on vertices, is frequently used to measure the
+importance of a specific node in graphs of all kinds. There are many previous
+studies about the static graph centralities[?], and there are many useful
+network analysis algorithms that used some kind of graph centralities. However,
+most social networks change over time, and even more unfortunately, some of the
+networks are large-scaled, which could make the analysis become hard and
+costly, hence limit the scale of meaningful data mining. The
+
+In Section 3 we will concentrate on centrality and activity in evolving social
+network. We will define what centrality or activity is good, and we will design
+some instance of those metrics by the standard we set. In Section 4, we will
+give the algorithms to compute our designed centrality and activity from the
+online data structure which maintains the evolving social network. We will also
+show how to quickly locate significant vertices that has high activity or
+centrality at a specific time. In Section 5, we will show the metrics make
+sense with real world data.
 \subsection{Algorithms}
-% TODO
+Graph theory is very successful on storing and solving variant problems on
+static networks, we have sophisticated methodology on finding the shortest
+paths, stratch a minimal spanning tree, finding the maximal $S$-$T$ flow, and
+we also have a well-established theoretical system to study problems that do
+not seems to have perfect solutions. However, dynamic on-line queries can be
+very hard for general graphs.
+
+In Section 2 we will discuss the known properties of a typical social network,
+which could be helpful for our algorithm designs. In Section 4, we will
+establish a framework of data structure and algorithms to solve series of
+possible queries about a evolving social network.
 \section{Evolving Social Network}

### 2013-06-21 network-science/paper.tex

@@
-\documentclass[a4,12pt,abstract=true]{scrartcl}
+\documentclass[12pt,abstract=true]{scrartcl}
 
@@
 	\Large \textbf{\textsf{
-		Metrics and Algorithms for Evolving Social Networks}} \\[1.5em]
-	\small
+		Metrics and Algorithms for Evolving Social Networks}} \\[1.2em]
+	\normalsize 
 		Pufan He\upper{1}, Yichao Zhou\upper{2}, Qiwei Feng\upper{3},
 		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin Xing\upper{6}\\[1em]
+	\small
 	\begin{tabular}{*{3}{>{\centering}p{.3\textwidth}}}
@@
 		\upper{3}\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
-
 		\upper{4}\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
@@
 
-	\normalsize IIIS, Tsinghua University \\[1.5em]
+	\small Institute for Interdisciplinary Information Sciences,
+	Tsinghua University \\[1.5em]
 \end{center} \par %>>>
@@
 \smallskip
-\noindent \textbf{Keywords.} social network, dynamic graph, centrality,
+\noindent \textbf{Keywords:} social network, dynamic graph, centrality,
 activity, algorithm.
 \end{abstract}
+\tableofcontents
+\newpage
 
@@
 % TODO
-\section{Algorithm}
+\section{Algorithms}
 % TODO

### 2013-06-21 trunk/network-science/algo.cpp

@@ -1,0 +1,32 @@
+// For Network Science 2013
+// Algorithm Demo
+//
+// Feng Qiwei
+// 2013.06.21
+//
+#include <iostream>
+#include <cstring>
+#include <cstdio>
+using namespace std;
+
+const int MAXN=1000010;
+const int MAXE=1000010;
+
+int n, query_cnt;
+int cur_time;
+
+void add_edge(int x, int y) {
+	// about degree
+	// about con
+}
+
+int deg_query(int t, int x) {
+}
+
+bool con_query(int t, int x, int y) {
+}
+
+int main(int argc, char *argv[]) {
+	cur_time=0;
+	return 0;
+}

### 2013-06-21 trunk/network-science/algo.cpp

@@ -7,26 +7,145 @@
 #include <iostream>
 #include <cstring>
 #include <cstdio>
+#include <vector>
 using namespace std;
 
 const int MAXN=1000010;
-const int MAXE=1000010;
+const int MAXQ=1000010;
 
+bool b_deg, b_con, b_vio;
 int n, query_cnt;
 int cur_time;
 
+int edge_x[MAXQ], edge_y[MAXQ], edge_t[MAXQ], edge_n;
+vector<int> ex[MAXN];
+int ufs_fa[MAXN], ufs_sz[MAXN], ufs_t[MAXN];
+
 void add_edge(int x, int y) {
+	++edge_n;
+	edge_x[edge_n]=x;
+	edge_y[edge_n]=y;
+	edge_t[edge_n]=t;
 	// about degree
-	// about con
+	if(b_deg) {
+		ex[x].push_back(cur_time);
+		ex[y].push_back(cur_time);
+	}
+	// about connecting
+	if(b_con) {
+		while(ufs_fa[x]>0) x=ufs_fa[x];
+		while(ufs_fa[y]>0) y=ufs_fa[y];
+		if(ufs_sz[x]<ufs_sz[y]) swap(x, y);
+		ufs_fa[y]=x;
+		ufs_sz[x]+=ufs_sz[y];
+		ufs_t[y]=cur_time;
+	}
 }
 
 int deg_query(int t, int x) {
+	if(!b_deg) return 0;
+	if(ex[x].size()==0) return 0;
+	return (int)(lower_bound(ex[x].begin(), ex[x].end(), t) - e[x].begin());
+}
+
+int vio_deg_query(int t, int x) {
+	int ans=0;
+	for(int i=1; i<=edge_n && edge_t[i]<=t; ++i)
+		if(edge_x[i]==x || edge_y[i]==x)
+			++ans;
+	return ans;
 }
 
 bool con_query(int t, int x, int y) {
+	if(!b_con) return false;
+	while(ufs_fa[x]>0 && ufs_t[x]<=t) x=ufs_fa[x];
+	while(ufs_fa[y]>0 && ufs_t[y]<=t) y=ufs_fa[y];
+	return x==y;
+}
+
+int uf[MAXN]; int get_uf(int x) {
+	return uf[x]==0 ? x : (uf[x]=get_uf(uf[x]));
+}
+bool vio_con_query(int t, int x, int y) {
+	for(int i=1; i<=n; ++i) uf[i]=0;
[…]

### 2013-06-21 trunk/network-science/data/data-gen.c

@@ -1,0 +1,65 @@
+#include <stdio.h>
+#include <string.h>
+#include <stdlib.h>
+#include <stdbool.h>
+#include <assert.h>
+#include <time.h>
+
+static int state = 1;
+
+int my_rand(void)
+{
+    const int M = 2147483647;
+    const int A = 48271;
+    const int Q = M/A;
+    const int R = M%A;
+
+    state = A*(state%Q) - R*(state/Q);
+
+    if (state < 0)
+        state += M;
+    return state;
+}
+
+void my_srand(time_t seed)
+{
+    state = (int)seed;
+}
+
+int main(int argc, char *argv[])
+{
+    if (argc == 1) {
+        puts("data-gen [number of vertices] [number of edges] [number of question per edge] ");
+        // puts("data-gen -e filename [number of question]");
+        return 0;
+    }
+
+    assert(argc == 4);
+
+    /*
+    if (strcmp(argv[1], "-e") == 0) {
+        freopen(argv, stdin);
+        scanf("%d %d ", &n, &m);
+        for (int i = 0; i < m; ++i) {
+            int src, dst;
+            scanf("%d %d", &src, &dst);
+        }
+    } else {
+    */
+    int n = atoi(argv[1]);
+    int m = atoi(argv[2]);
+    double p = atof(argv[3]);
+
+    my_srand(time(NULL));
+
+    printf("%d %d\n", n, m);
+    for (int i = 0; i < m; ++i) {
+        printf("a %d %d\n", 1+my_rand()%n, 1+my_rand()%n);
+        while ((double)my_rand()/INT_MAX < p) {
+            if (my_rand() & 1)
+                printf("q -c %d %d %d\n", my_rand()%(i+2), 1+my_rand()%n, 1+my_rand()%n);
+            else
+                printf("q -d %d %d\n", my_rand()%(i+2), 1+my_rand()%n);
+        }
+    }
+}

### 2013-06-21 network-science/data/data-gen.c

@@ -29,7 +29,7 @@ void my_srand(time_t seed)
 int main(int argc, char *argv[])
 {
     if (argc == 1) {
-        puts("data-gen [number of vertices] [number of edges] [number of question per edge] ");
+        puts("data-gen [number of vertices] [number of edges] [question density] ");
         // puts("data-gen -e filename [number of question]");
         return 0;
     }

### 2013-06-21 network-science/algo.cpp

@@ -25,7 +25,7 @@ void add_edge(int x, int y) {
 	++edge_n;
 	edge_x[edge_n]=x;
 	edge_y[edge_n]=y;
-	edge_t[edge_n]=t;
+	edge_t[edge_n]=cur_time;
 	// about degree
 	if(b_deg) {
 		ex[x].push_back(cur_time);
@@ -45,7 +45,7 @@ void add_edge(int x, int y) {
 int deg_query(int t, int x) {
 	if(!b_deg) return 0;
 	if(ex[x].size()==0) return 0;
-	return (int)(lower_bound(ex[x].begin(), ex[x].end(), t) - e[x].begin());
+	return (int)(lower_bound(ex[x].begin(), ex[x].end(), t+1) - ex[x].begin());
 }
 
 int vio_deg_query(int t, int x) {
@@ -112,7 +112,7 @@ int main(int argc, char *argv[]) {
 		ufs_sz[i]=1;
 	}
 	FILE *inf=fopen(s_inf, "r");
-	FILE *ouf=(s_ouf==NULL ? stdout : fopen(s_out, "w"));
+	FILE *ouf=(s_ouf==NULL ? stdout : fopen(s_ouf, "w"));
 	fscanf(inf, "%d%d", &n, &query_cnt);
 	for(int cur_q=1; cur_q<=query_cnt; ++cur_q) {
 		char op[99], sop[99]; fscanf(inf, "%s", op);
@@ -121,6 +121,7 @@ int main(int argc, char *argv[]) {
 			fscanf(inf, "%d%d", &x,&y);
 			++cur_time;
 			add_edge(x, y);
+			fprintf(ouf, "%d: a %d %d\n", cur_time, x, y);
 		}
 		if(op[0]=='q') {
 			fscanf(inf, "%s", sop);
@@ -137,7 +138,7 @@ int main(int argc, char *argv[]) {
 			if(sop[1]=='d') {
 				fscanf(inf, "%d%d", &t,&x);
 				bool ans=deg_query(t, x);
-				fprintf(ouf, "%d: qc %d %d -> %d", cur_time, t,x, ans);
+				fprintf(ouf, "%d: qd %d %d -> %d", cur_time, t,x, ans);
 				if(b_vio) {
 					bool std=vio_deg_query(t, x);
 					fprintf(ouf, " / %d [%s]", std, (std==ans)?"yes":"error");

### 2013-06-21 trunk/network-science/data/data-gen.c

@@ -4,6 +4,7 @@
 #include <stdbool.h>
 #include <assert.h>
 #include <time.h>
+#include <limit.h>
 
 static int state = 1;
 

### 2013-06-21 network-science/data/data-gen.c

@@ -4,7 +4,7 @@
 #include <stdbool.h>
 #include <assert.h>
 #include <time.h>
-#include <limit.h>
+#include <limits.h>
 
 static int state = 1;
 

### 2013-06-21 trunk/network-science/data/data-gen.c

@@ -53,7 +53,7 @@ int main(int argc, char *argv[])
 
     my_srand(time(NULL));
 
-    printf("%d %d\n", n, m);
+    printf("%d\n", n);
     for (int i = 0; i < m; ++i) {
         printf("a %d %d\n", 1+my_rand()%n, 1+my_rand()%n);
         while ((double)my_rand()/INT_MAX < p) {

### 2013-06-21 network-science/data/data-gen.c

@@ -7,6 +7,7 @@
 #include <limits.h>
 
 static int state = 1;
+char buffer[1000];
 
 int my_rand(void)
 {
@@ -31,36 +32,48 @@ int main(int argc, char *argv[])
 {
     if (argc == 1) {
         puts("data-gen [number of vertices] [number of edges] [question density] ");
-        // puts("data-gen -e filename [number of question]");
+        puts("data-gen -e filename [question density]");
         return 0;
     }
 
     assert(argc == 4);
 
-    /*
     if (strcmp(argv[1], "-e") == 0) {
-        freopen(argv, stdin);
-        scanf("%d %d ", &n, &m);
+        freopen(argv[2], "r", stdin);
+        int n, m;
+        double p = atof(argv[3]);
+        gets(buffer);
+        gets(buffer);
+        scanf("# Nodes: %d Edges: %d ", &n, &m);
+        printf("%d %d\n", n, m);
+        gets(buffer);
         for (int i = 0; i < m; ++i) {
             int src, dst;
             scanf("%d %d", &src, &dst);
+            printf("a %d %d\n", src, dst);
+            while ((double)my_rand()/INT_MAX < p) {
+                if (my_rand() & 1)
+                    printf("q -c %d %d %d\n", my_rand()%(i+2), 1+my_rand()%n, 1+my_rand()%n);
+                else
+                    printf("q -d %d %d\n", my_rand()%(i+2), 1+my_rand()%n);
+            }
         }
     } else {
-    */
-    int n = atoi(argv[1]);
-    int m = atoi(argv[2]);
-    double p = atof(argv[3]);
+        int n = atoi(argv[1]);
+        int m = atoi(argv[2]);
+        double p = atof(argv[3]);
 
-    my_srand(time(NULL));
+        my_srand(time(NULL));
 
-    printf("%d\n", n);
-    for (int i = 0; i < m; ++i) {
-        printf("a %d %d\n", 1+my_rand()%n, 1+my_rand()%n);
-        while ((double)my_rand()/INT_MAX < p) {
-            if (my_rand() & 1)
-                printf("q -c %d %d %d\n", my_rand()%(i+2), 1+my_rand()%n, 1+my_rand()%n);
-            else
-                printf("q -d %d %d\n", my_rand()%(i+2), 1+my_rand()%n);
+        printf("%d\n", n);
+        for (int i = 0; i < m; ++i) {
[…]

### 2013-06-21 trunk/network-science/data/algo.cpp

@@ -1,0 +1,160 @@
+// For Network Science 2013
+// Algorithm Demo
+//
+// Feng Qiwei
+// 2013.06.21
+//
+#include <iostream>
+#include <cstring>
+#include <cstdio>
+#include <vector>
+using namespace std;
+
+const int MAXN=1000010;
+const int MAXQ=1000010;
+
+bool b_deg, b_con, b_vio;
+int n;
+int cur_time;
+
+int edge_x[MAXQ], edge_y[MAXQ], edge_t[MAXQ], edge_n;
+vector<int> ex[MAXN];
+int ufs_fa[MAXN], ufs_sz[MAXN], ufs_t[MAXN];
+
+void add_edge(int x, int y) {
+	++edge_n;
+	edge_x[edge_n]=x;
+	edge_y[edge_n]=y;
+	edge_t[edge_n]=cur_time;
+	// about degree
+	if(b_deg) {
+		ex[x].push_back(cur_time);
+		ex[y].push_back(cur_time);
+	}
+	// about connecting
+	if(b_con) {
+		while(ufs_fa[x]>0) x=ufs_fa[x];
+		while(ufs_fa[y]>0) y=ufs_fa[y];
+		if(x!=y) {
+			if(ufs_sz[x]<ufs_sz[y]) swap(x, y);
+			ufs_fa[y]=x;
+			ufs_sz[x]+=ufs_sz[y];
+			ufs_t[y]=cur_time;
+		}
+	}
+}
+
+int deg_query(int t, int x) {
+	if(!b_deg) return 0;
+	if(ex[x].size()==0) return 0;
+	return (int)(lower_bound(ex[x].begin(), ex[x].end(), t+1) - ex[x].begin());
+}
+
+int vio_deg_query(int t, int x) {
+	int ans=0;
+	for(int i=1; i<=edge_n && edge_t[i]<=t; ++i)
+		if(edge_x[i]==x || edge_y[i]==x)
+			++ans;
+	return ans;
+}
+
+bool con_query(int t, int x, int y) {
+	if(!b_con) return false;
+	while(ufs_fa[x]>0 && ufs_t[x]<=t) x=ufs_fa[x];
+	while(ufs_fa[y]>0 && ufs_t[y]<=t) y=ufs_fa[y];
+	return x==y;
+}
+
+int uf[MAXN]; int get_uf(int x) {
+	return uf[x]==0 ? x : (uf[x]=get_uf(uf[x]));
+}
[…]

### 2013-06-21 network-science/data/algo.cpp
i finish my job i think

@@ -13,7 +13,7 @@ using namespace std;
 const int MAXN=1000010;
 const int MAXQ=1000010;
 
-bool b_deg, b_con, b_vio;
+bool b_deg, b_con, b_vio, b_info;
 int n;
 int cur_time;
 
@@ -52,9 +52,10 @@ int deg_query(int t, int x) {
 
 int vio_deg_query(int t, int x) {
 	int ans=0;
-	for(int i=1; i<=edge_n && edge_t[i]<=t; ++i)
-		if(edge_x[i]==x || edge_y[i]==x)
-			++ans;
+	for(int i=1; i<=edge_n && edge_t[i]<=t; ++i) {
+		if(edge_x[i]==x) ++ans;
+		if(edge_y[i]==x) ++ans;
+	}
 	return ans;
 }
 
@@ -87,7 +88,7 @@ void print_usage(char *s) {
 }
 
 int main(int argc, char *argv[]) {
-	b_con=b_deg=b_vio=false;
+	b_con=b_deg=b_vio=b_info=false;
 	char *s_inf=NULL;
 	char *s_ouf=NULL;
 	for(int i=1; i<argc; ++i) {
@@ -97,6 +98,8 @@ int main(int argc, char *argv[]) {
 			b_deg=true;
 		if(strcmp(argv[i], "-vio")==0)
 			b_vio=true;
+		if(strcmp(argv[i], "-info")==0)
+			b_info=true;
 		if(strcmp(argv[i], "-i")==0)
 			s_inf=argv[++i];
 		if(strcmp(argv[i], "-o")==0)
@@ -125,36 +128,44 @@ int main(int argc, char *argv[]) {
 			fscanf(inf, "%d%d", &x,&y);
 			++cur_time;
 			add_edge(x, y);
-			fprintf(ouf, "%d: a %d %d\n", cur_time, x, y);
+			if(b_info)
+				fprintf(ouf, "%d: a %d %d\n", cur_time, x, y);
 		}
 		if(op[0]=='q') {
 			fscanf(inf, "%s", sop);
 			if(sop[1]=='c') {
 				fscanf(inf, "%d%d%d", &t,&x,&y);
 				bool ans=con_query(t, x, y);
-				fprintf(ouf, "%d: qc %d %d %d -> %d", cur_time, t,x,y, ans);
+				if(b_info)
+					fprintf(ouf, "%d: qc %d %d %d -> %d", cur_time, t,x,y, ans);
 				if(b_vio) {
[…]

### 2013-06-21 trunk/network-science/data/test-correctness.sh
i finish my job i think

@@ -1,0 +1,2 @@
+./data-gen 5000 100000 0.5 > data.in
+./algo -i data.in -con -deg -vio -info

### 2013-06-21 trunk/network-science/data/test-time.sh

@@ -1,0 +1,2 @@
+./data-gen 500000 1000000 0.5 > data.in
+time ./algo -i data.in -con -deg

### 2013-06-21 network-science/paper.tex
8

@@
 connections between existing or newly created nodes, and we assume the graph
-will evolve as a typical social network. We study the centrality and activity
+will evolve as a typical social network. We study the activity and centrality
 metrics for nodes in such graphs by regulate a series of reasonable properties
@@
 \smallskip
-\noindent \textbf{Keywords:} social network, dynamic graph, centrality,
-activity, algorithm.
+\noindent \textbf{Keywords:} social network, dynamic graph, activity,
+centrality, algorithm.
 \end{abstract}
@@
 \section{Introduction}
-% TODO
+Social networks is a surprising interdisciplinary field of social science and
+computer science, allowing helpful analysis of large-scaled social behavior
+and tendency. In this paper, we will take more information of social networks,
+the time dimension, and make the similar study to the social behaviors. We
+build metrics for evolving social networks and design the algorithm to
+calculate them. We compare how different the outcome by our method would be
+against the classical analysis with un-timestamped data mining.
+
 \subsection{Dynamic Metrics}
+Networks contain too much information to be easily observed by people without
+any abstraction. To study a network, people exploited the basic form of
+quantification to concentrate on specific features of the whole graph, or an
+individual vertex. Our work is to promote this methodology to the dynamic
+graphs. We basically design the new dynamic metrics according to existing
+successful static ones, but we will point out a important metric that can be
+only observed in time evolving networks, the activity. Intuitively speaking,
+a vertex with high activity indicates more frequent recent social actions, and
+the vertex is more willing to make new change by the structural sense of graph.
+The accuracy of activity will be quite vital to recommendation algorithms of
+advertisement, new friends, or search results. Activity can be also used by
+other metrics, so that the computation of other metrics will no longer need the
+time information directly, but referring to the activity instead.
+
 Centrality, usually defined on vertices, is frequently used to measure the
@@
 networks are large-scaled, which could make the analysis become hard and
-costly, hence limit the scale of meaningful data mining. The
+costly, hence limit the scale of meaningful data mining. Moreover, the time
+effect can also become a factor of the centrality, that is, the same graph with
+different evolving sequence may have totally different metrics. On an
+intuitive level, the node connected with more higher activity nodes should be
+more important at that time, even if other node have much more silent
+neighbors. If we do not excavate the information on the time dimension, we will
+lose tremendous information and also the possibility of accumulative
+computation which could be helpful in enhancement the speed of answering
+consistent quering.
 
@@
 sense with real world data.
+
 \subsection{Algorithms}
@@
 static networks, we have sophisticated methodology on finding the shortest
-paths, stratch a minimal spanning tree, finding the maximal $S$-$T$ flow, and
-we also have a well-established theoretical system to study problems that do
-not seems to have perfect solutions. However, dynamic on-line queries can be
-very hard for general graphs.
+paths, stratch a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
+And we also have a well-established theoretical system to study problems that
+do not seems to have perfect solutions. However, dynamic online queries can be
+very hard for general graphs. Best known solutions for many dynamic basic graph
+problems still remain unsatisfiable for general demands. So to design metrics
+for an general evolving network is a very challenging and open problem. We
+concentrate on the popular studied social networks and try to create meaningful
+and available approaches of operation on such networks.
 
@@
 establish a framework of data structure and algorithms to solve series of
-possible queries about a evolving social network.
+possible queries including computing the metrics about a evolving social
+network.
+
 \section{Evolving Social Network}
-% TODO
+In some related research on evolving graphs, the time dimension is represented
+by constructing a sequence of graphs $EG=\{G_t(V_t,E_t)\}$ on different time
+spots $t$. This model is highly expressive and universal in mathematical
+statement, thus we adopt in. However, we constrain the relation of
+time-adjacent graphs in order to simplify the analysis and remain the highest
+possible loyalty to the reality. We build the \textbf{pure growing model},
+which care about the new connection forming among vertices, neglecting the
+anti-growing operations such as edge deletions. We assume the existence of
+every connection will contribute to the metrics, even if the connection is
+later erased, so we do not delete edges or nodes in our model, instead we
+could add an decay mechanism to reduce the affect of old formed links, which
+will be discussed in the next section. Note that in pure growing model, we
+will assign every edge a timestamp, namely when the edge is created. And thus
+there could be more than one edges between a pair of nodes, with different
+timestamp.
+
 \subsection{Definition}
-% TODO
+\definition A \textbf{pure growing model} for an evolving graph $EG$ is defined
+in pair \begin{equation}
+EG=(V,E),
+\end{equation}
+where $V$ is the set of all nodes in the network, and $E$
+is the set of edges, formally an edge $e\in E$ for $e=(u,v,t)$,
+where $u,v\in V$ are the two end points of the edge, $u<v$ (to ensure
+bidirectional), $t\in \mathbb{N}$. The $t$ component stored the forming time of
+the graph. As for weighted evolving graph model, we modifies $e\in E$ for
+$e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands for the multiplicity of the
+edge, which might be useful in some circumstances, and the others stay the same
+meaning. In the unweighted case, we can simply set $w=1$ for all edges.
+
+\definition The historical edge set $E_t$
+\begin{equation}
+E_t=\{e\;|\;e(u,v,t',w)\in E\text{ and }t'\leq t\}.
+\end{equation}
+An immediate statement one can ensure is
+\begin{equation}
+\forall t, E_t\subseteq E\text{ and }p\leq q\implies E_p\subseteq E_q.
+\end{equation}
+
+Define $G_t$ to be the graph formed by $V$ and $E_t$. So $G_t$ is the snapshot
+of the whole network at time $t$.
+
+Now we define the update of an evolving graph in our model. First we assume all
+possible active vertices has been already defined, so $V$ does not change.
+\definition 
+$EG^*=(V,E^*)$ where $E\subseteq E^*$. We assume the edges are added to the
+model by correct time order, so
+\begin{equation}
+\forall e\in E^*\setminus E, \forall e'\in E, e=(u,v,t,w)\text{ and }
+e'=(u',v',t',w'), t\geq t'.
+\end{equation}
+
+And we define the notation of some frequently used basic functions:
+
+\definition The adjacency matrix.
+\begin{equation}
+A(G_t)=\begin{pmatrix}a_{ij}\end{pmatrix}_{n\times n},\text{ where }n=|V|,
+a_{ij}\in \mathbb{R}^+,
+\end{equation}
+is the adjacency matrix of the graph at time $t$. More detailed
+\begin{equation}
+a_{ij}=\begin{cases}
+0&(i=j)\\
+\sum_{e\in E_t\text{ and }e=(i,j,t,w)}w &(i<j)\\
+a_{ji}&(i>j)
+\end{cases}
+\end{equation}
+
+\begin{definition}
+The degree function $k(G_t,v)$.
+\begin{equation}
+k(G_t,v)=\sum_{\mathclap{e\in E_t, e=(x,y,t,w)}}w(1-\delta(x,v)\delta(y,v)),
+\end{equation}
+where \begin{equation}
+\delta(x,y)=\begin{cases}1&(x\neq y)\\0&(x=y)\end{cases}.
+\end{equation}
+\end{definition}
+
 \subsection{Properties}
 % TODO
-\section{Centrality and Activity}
+\section{Activity and Centrality}
 % TODO

### 2013-06-21 network-science/algo.cpp
del

@@ -1,152 +1,0 @@
-// For Network Science 2013
-// Algorithm Demo
-//
-// Feng Qiwei
-// 2013.06.21
-//
-#include <iostream>
-#include <cstring>
-#include <cstdio>
-#include <vector>
-using namespace std;
-
-const int MAXN=1000010;
-const int MAXQ=1000010;
-
-bool b_deg, b_con, b_vio;
-int n, query_cnt;
-int cur_time;
-
-int edge_x[MAXQ], edge_y[MAXQ], edge_t[MAXQ], edge_n;
-vector<int> ex[MAXN];
-int ufs_fa[MAXN], ufs_sz[MAXN], ufs_t[MAXN];
-
-void add_edge(int x, int y) {
-	++edge_n;
-	edge_x[edge_n]=x;
-	edge_y[edge_n]=y;
-	edge_t[edge_n]=cur_time;
-	// about degree
-	if(b_deg) {
-		ex[x].push_back(cur_time);
-		ex[y].push_back(cur_time);
-	}
-	// about connecting
-	if(b_con) {
-		while(ufs_fa[x]>0) x=ufs_fa[x];
-		while(ufs_fa[y]>0) y=ufs_fa[y];
-		if(ufs_sz[x]<ufs_sz[y]) swap(x, y);
-		ufs_fa[y]=x;
-		ufs_sz[x]+=ufs_sz[y];
-		ufs_t[y]=cur_time;
-	}
-}
-
-int deg_query(int t, int x) {
-	if(!b_deg) return 0;
-	if(ex[x].size()==0) return 0;
-	return (int)(lower_bound(ex[x].begin(), ex[x].end(), t+1) - ex[x].begin());
-}
-
-int vio_deg_query(int t, int x) {
-	int ans=0;
-	for(int i=1; i<=edge_n && edge_t[i]<=t; ++i)
-		if(edge_x[i]==x || edge_y[i]==x)
-			++ans;
-	return ans;
-}
-
-bool con_query(int t, int x, int y) {
-	if(!b_con) return false;
-	while(ufs_fa[x]>0 && ufs_t[x]<=t) x=ufs_fa[x];
-	while(ufs_fa[y]>0 && ufs_t[y]<=t) y=ufs_fa[y];
-	return x==y;
-}
-
-int uf[MAXN]; int get_uf(int x) {
-	return uf[x]==0 ? x : (uf[x]=get_uf(uf[x]));
-}
[…]

### 2013-06-22 trunk/network-science/paper.tex
w

@@
 \renewcommand\cftsecafterpnum{\par}
-\setlength{\cftbeforesecskip}{0.3em}
+\setlength{\cftbeforesecskip}{0.2em}
 
@@
 \smallskip
-\noindent \textbf{Keywords:} social network, dynamic graph, centrality,
-activity, algorithm.
+\noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
+vertex centrality, online algorithm.
 \end{abstract}
@@
 establish a framework of data structure and algorithms to solve series of
-possible queries about a evolving social network.
+possible queries including computing the metrics about a evolving social
+network.
+
 \section{Evolving Social Network}
-% TODO
+In some related research on evolving graphs, the time dimension is represented
+by constructing a sequence of graphs $EG=\{G_t(V_t,E_t)\}$ on different time
+spots $t$. This model is highly expressive and universal in mathematical
+statement, thus we adopt in. However, we constrain the relation of
+time-adjacent graphs in order to simplify the analysis and remain the highest
+possible loyalty to the reality. We build the \textbf{pure growing model},
+which care about the new connection forming among vertices, neglecting the
+anti-growing operations such as edge deletions. We assume the existence of
+every connection will contribute to the metrics, even if the connection is
+later erased, so we do not delete edges or nodes in our model, instead we
+could add an decay mechanism to reduce the affect of old formed links, which
+will be discussed in the next section. Note that in pure growing model, we
+will assign every edge a timestamp, namely when the edge is created. And thus
+there could be more than one edges between a pair of nodes, with different
+timestamp.
+
 \subsection{Definition}
-% TODO
+\definition A \textbf{pure growing model} for an evolving graph $EG$ is defined
+in pair \begin{equation}
+EG=(V,E),
+\end{equation}
+where $V$ is the set of all nodes in the network, and $E$
+is the set of edges, formally an edge $e\in E$ for $e=(u,v,t)$,
+where $u,v\in V$ are the two end points of the edge, $u<v$ (to ensure
+bidirectional), $t\in \mathbb{N}$. The $t$ component stored the forming time of
+the graph. As for weighted evolving graph model, we modifies $e\in E$ for
+$e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands for the multiplicity of the
+edge, which might be useful in some circumstances, and the others stay the same
+meaning. In the unweighted case, we can simply set $w=1$ for all edges.
+
+\definition The historical edge set $E_t$
+\begin{equation}
+E_t=\{e\;|\;e(u,v,t',w)\in E\text{ and }t'\leq t\}.
+\end{equation}
+An immediate statement one can ensure is
+\begin{equation}
+\forall t, E_t\subseteq E\text{ and }p\leq q\implies E_p\subseteq E_q.
+\end{equation}
+
+Define $G_t$ to be the graph formed by $V$ and $E_t$. So $G_t$ is the snapshot
+of the whole network at time $t$.
+
+Now we define the update of an evolving graph in our model. First we assume all
+possible active vertices has been already defined, so $V$ does not change.
+\definition 
+$EG^*=(V,E^*)$ where $E\subseteq E^*$. We assume the edges are added to the
+model by correct time order, so
+\begin{equation}
+\forall e\in E^*\setminus E, \forall e'\in E, e=(u,v,t,w)\text{ and }
+e'=(u',v',t',w'), t\geq t'.
+\end{equation}
+
+And we define the notation of some frequently used basic functions:
+
+\definition The adjacency matrix.
+\begin{equation}
+A(G_t)=\begin{pmatrix}a_{ij}\end{pmatrix}_{n\times n},\text{ where }n=|V|,
+a_{ij}\in \mathbb{R}^+,
+\end{equation}
+is the adjacency matrix of the graph at time $t$. More detailed
+\begin{equation}
+a_{ij}=\begin{cases}
+0&(i=j)\\
+\sum_{e\in E_t\text{ and }e=(i,j,t,w)}w &(i<j)\\
+a_{ji}&(i>j)
+\end{cases}
+\end{equation}
+
+\begin{definition}
+The degree function $k(G_t,v)$.
+\begin{equation}
+k(G_t,v)=\sum_{\mathclap{e\in E_t, e=(x,y,t,w)}}w(1-\delta(x,v)\delta(y,v)),
+\end{equation}
+where \begin{equation}
+\delta(x,y)=\begin{cases}1&(x\neq y)\\0&(x=y)\end{cases}.
+\end{equation}
+\end{definition}
+
 \subsection{Properties}
-% TODO
-\section{Centrality and Activity}
-% TODO
+In most social networks, people have their own friendship circles, and the
+average circle size is quite limited because people do less interaction with
+strangers than their close friends or family members. We call this phenomenon
+the \textbf{sparsity} of social network.
+\definition Reduced edge set (historical) $E_t^\bullet=\{(x_i,y_i)\}$:
+\begin{equation}
+(x,y)\in E_t^\bullet \iff \exists e(x,y,t,w)\in E_t.
+\end{equation}
+\definition Reduced degree $k^\bullet(G_t,v)$:
+\begin{equation}
+k^\bullet(G_t,v)=\#\{u\;|\;(u,v)\in E_t^\bullet\text{ or }(v,u)\in
+E_t^\bullet\}.
+\end{equation}
+
+We then have
+\begin{equation}
+\left<k^\bullet\right>=2\left|E^\bullet\right|/\left|V\right|,
+\end{equation}
+where $\left|E^\bullet\right|/\left|V\right|$ only depends on the structure of
+the network at a time spot. In many available online datasets, such as [?]%TODO
+we can assume $\left<k^\bullet\right>$ is limited by a constant $K$, typically
+$10^2$.
+\definition Sparcity constant $K=\left<k^\bullet\right>$.
+
+\begin{observation} $K=O(1)$.
+\end{observation}
+So if we only use the reduced edge list in our framework as additional memory
+requirements, or similarly speaking, consider the adjacency matrix to be a
+sparse matrix and only store the non-zero entries, the space expense would then
+be just $O(n)$, which is highly available. However this does not means we can
+handle neighbor updating operations in $O(1)$ time, because
+\begin{equation}\max k^\bullet\geq
+\left<k^\bullet\right>=K \end{equation} and the former one may be very large.
+We cannot trivially assert the amortized time complexity to be $O(1)$ neither,
+because the nodes with high degrees may requires more operations over time,
+just like the famous friendship paradox[?].
+
+Another famouse property of social networks is known as the small world
+effect[?], for that the giant component contains nearly all active nodes and it
+has very small diameter.
+
+\section{Activity and Centrality}
+
 \subsection{Desiderata}

### 2013-06-23 trunk/network-science/paper.tex
7

@@
 importance of a specific node in graphs of all kinds. There are many previous
-studies about the static graph centralities[?], and there are many useful
+studies about the static graph centralities[?], such as page rank
+algorithm\cite{page1999pagerank}, and there are many useful
 network analysis algorithms that used some kind of graph centralities. However,
@@
 
+The clustering coefficient[?], namely
+\begin{equation}
+c.c=\frac{\#\text{closed paths of len 2}}{\#\text{paths of len 2}},
+\end{equation}
+for a typical social network is a possitive
+number, which means people are more willing to make interactions with close
+related people than unfamiliars.
+
 \section{Activity and Centrality}
@@
 \subsection{Desiderata}
-% TODO
+Suppose $Act(G_t,v)$ returns the activity of node $v$ in the evolving graph in
+time $t$. Then $Act(G_t,v)$ should be a deterministic function of $v$ and
+$E_t$.
+\begin{itemize}
+\item \textbf{normalization}:
+
+We want the metrics to derive other functions, so it will be nice if we can
+limit the range of the function.
+\begin{equation}
+0\leq Act(G_t,v) \leq 1.
+\end{equation}
+
+\item \textbf{initialization}:
+
+A node with no neighbors is totally inactive.
+\begin{equation}
+k(G_t,v)=0\implies Act(G_t,v)=0.
+\end{equation}
+
+\item \textbf{monotonicity}:
+
+If a vertex $v$ performs an interaction $(v,u)$ at time $t$, and suppose the
+interaction is the only change to the graph at time $t$, then the activity of
+$v$ should enhance.
+
+\begin{equation}
+E_{t+1}=E_t\cup\{e(u,v,t,w)\}\implies Act(G_{t+1},v)>Act(G_{t},v).
+\end{equation}
+
+\item \textbf{attenuation}:
+
+If the network keeps silent, the activity metric of any node $v$ should be decreasing
+over time by intuition. Because there is a lower bound for activity and we want
+the attenuation process to be infinity long since a node changed the network
+once in past time is potential to make another. So we make the decay rate
+of activity for silent nodes to be also decreasing. However in our pure growing
+model, the change of network structure must happen at integral time. So we
+expand the definition
+\begin{equation}
+G_t=G_{\lfloor t \rfloor}\text{ and } E_t=E_{\lfloor t \rfloor},
+\end{equation}
+to make $Act(G,v)$ a well defined $\mathbb{R}\to [0,1]$ function.
+
+\begin{equation}
+
+\end{equation}
+
+\end{itemize}
 \subsection{Design and Analysis}

### 2013-06-23 trunk/network-science/paper.tex
8

@@
 \subsection{Desiderata}
-Suppose $Act(G_t,v)$ returns the activity of node $v$ in the evolving graph in
+\definition $Act(G_t,v)$ returns the activity of node $v$ in the evolving graph in
 time $t$. Then $Act(G_t,v)$ should be a deterministic function of $v$ and
@@
 
-If the network keeps silent, the activity metric of any node $v$ should be decreasing
-over time by intuition. Because there is a lower bound for activity and we want
+If the network keeps silent, the activity metric of any node $v$ should be
+decreasing over time by intuition. Because there is a lower bound for activity
+and we want
 the attenuation process to be infinity long since a node changed the network
@@
 \begin{equation}
-
+todo
 \end{equation}
@@
 \section{Experiment}
-% TODO
+
+We have implemented two of the algorithms using C++ language.
+The program maintains a dynamic graph which contains $n$ vertices and does not have
+any edge at the beginning.
+It support the following operations:
+\begin{itemize}
+	\item \textsc{Add $u,v$:} increase the time counter by one, and then add an edge
+		between vertex $u$ and vertex $v$.
+	\item \textsc{QueryDeg $t,u$:} ask for the degree of $u$ at time $t$.
+	\item \textsc{QueryCon $t,u,v$:} ask that whether vertices $u,v$ is connected or not
+		$u$ at time $t$.
+\end{itemize}
+Note that the time counter is initially zero.
+Each operation cost $O(\log n)$ time in our implemented algorithm.
+
+\subsection{Checking for Correctness}
+We implemented a simple algorithm together which cost $O(\max\{n,m\})$ time for each operation,
+	where $m$ is the number of edges before the operation.
+We have generated several small test cases and compare the results between the simple program
+	and our $O(\log n)$ program.
+There is no difference found between outputs of the two programs.
+
+\subsection{Checking for Time Complexity}
+We have generated several huge test cases to test the running time of the program.
+The following tabular shows the informations about the cases and the running results.
+\begin{center} \begin{tabular}{|c|c|c|c|c|}
+	\hline
+	Case & Number of & Number of & Density of & Running \\
+	ID & vertices & operations & query & time \\
+	\hline
+	1 & 100000 & 200000 & 0.5 & 0.504 \\
+	\hline
+	2 & 100000 & 200000 & 0.5 & 0.524 \\
+	\hline
+	3 & 100000 & 200000 & 0.5 & 0.516 \\
+	\hline
+	4 & 200000 & 400000 & 0.5 & 1.072 \\
+	\hline
+	5 & 200000 & 400000 & 0.5 & 1.092 \\
+	\hline
+	6 & 200000 & 400000 & 0.5 & 1.072 \\
+	\hline
+	7 & 500000 & 500000 & 0.5 & 1.464 \\
+	\hline
+	8 & 500000 & 500000 & 0.5 & 1.492 \\
+	\hline
+	9 & 500000 & 1000000 & 0.5 & 2.772 \\
+	\hline
+	10 & 500000 & 1000000 & 0.5 & 2.732 \\
+	\hline
+	11 & 500000 & 2000000 & 0.5 & 5.232 \\
+	\hline
+	12 & 500000 & 2000000 & 0.5 & 5.256 \\
+	\hline
+	13 & 1000000 & 2000000 & 0.5 & 5.652 \\
+	\hline
+	14 & 1000000 & 2000000 & 0.5 & 5.808 \\
+	\hline
+	15 & 1000000 & 3000000 & 0.5 & 8.417 \\
+	\hline
+\end{tabular} \end{center}
+We can see that the running time grows as linear as number of operations,
+	but grows much slower when number of vertices grows (as $\log$).
+
 \section{Conclusion and Perspective}

### 2013-06-23 trunk/network-science/data/algo.cpp

@@ -11,7 +11,7 @@
 using namespace std;
 
 const int MAXN=1000010;
-const int MAXQ=1000010;
+const int MAXQ=3000010;
 
 bool b_deg, b_con, b_vio, b_info;
 int n;

### 2013-06-23 network-science/data/test-time.sh

@@ -1,2 +1,2 @@
-./data-gen 500000 1000000 0.5 > data.in
+./data-gen 1000000 3000000 0.5 > data.in
 time ./algo -i data.in -con -deg

### 2013-06-23 trunk/network-science/data/test-correctness.sh

@@ -1,2 +1,3 @@
+#!/bin/bash
 ./data-gen 5000 100000 0.5 > data.in
 ./algo -i data.in -con -deg -vio -info

### 2013-06-23 trunk/network-science/data/test-time.sh

@@ -1,2 +1,3 @@
+#!/bin/bash
 ./data-gen 1000000 3000000 0.5 > data.in
 time ./algo -i data.in -con -deg

### 2013-06-23 trunk/network-science/paper.tex

@@
 \end{abstract}
-\tableofcontents
-\newpage
+% \tableofcontents
+% \newpage
 
@@
 computation which could be helpful in enhancement the speed of answering
-consistent quering.
+consistent querying.
 
@@
 time-adjacent graphs in order to simplify the analysis and remain the highest
-possible loyalty to the reality. We build the \textbf{pure growing model},
-which care about the new connection forming among vertices, neglecting the
-anti-growing operations such as edge deletions. We assume the existence of
+possible loyalty to the real data generation. We build the \textbf{pure growing
+model}, which care about the new connection forming among vertices, neglecting
+the anti-growing operations such as edge deletions. We assume the existence of
 every connection will contribute to the metrics, even if the connection is
-later erased, so we do not delete edges or nodes in our model, instead we
-could add an decay mechanism to reduce the affect of old formed links, which
-will be discussed in the next section. Note that in pure growing model, we
-will assign every edge a timestamp, namely when the edge is created. And thus
-there could be more than one edges between a pair of nodes, with different
-timestamp.
+later erased, so we do not delete edges or nodes in our model, instead we could
+add an decay mechanism to reduce the affect of old formed links, which will be
+discussed in the next section. Note that in pure growing model, we will assign
+every edge a timestamp, namely when the edge is created. And thus there could
+be more than one edges between a pair of nodes, with different timestamp.
 
@@
 \section{Experiment}
+\subsection{Data Generation} 
+Our data generation is base on real social network provided by \cite{database1,
+database2}.  Because the real dynamic graph is hard to obtain, we only use
+these graph as a final state of the dynamic graph, which means the evolving
+graph generated will satisfy all the property that we discussed in section 2.
+Then we artificially add a timeline into that graph to make it become an
+evolving graph.
 
+Another way to generate data is to use the method given by
+\cite{kumar2010structure}.  The author in that paper propose a method to
+simulate the real timeline of a social network, which has same component
+properties and very good similarity with the actual network.  Unfortunately,
+because of the time limitation, we have not implemented this brilliant
+technique.
+
+\subsection{Program}
 We have implemented two of the algorithms using C++ language.
@@
 \begin{itemize}
-	\item \textsc{Add $u,v$:} increase the time counter by one, and then add an edge
+	\item \textsc{Add Edge$(u,v)$:} increase the time counter by one, and then add an edge
 		between vertex $u$ and vertex $v$.
-	\item \textsc{QueryDeg $t,u$:} ask for the degree of $u$ at time $t$.
-	\item \textsc{QueryCon $t,u,v$:} ask that whether vertices $u,v$ is connected or not
+	\item \textsc{Query Degree$(t,u)$:} ask for the degree of $u$ at time $t$.
+	\item \textsc{Query Connectivity$(t,u,v)$:} ask that whether vertices $u,v$ is connected or not
 		$u$ at time $t$.
@@
 	\hline
-	15 & 1000000 & 3000000 & 0.5 & 8.417 \\
+	15 & 1000000 & 3000000 & 0.5 & 8.416 \\
 	\hline

### 2013-06-23 network-science/paper.tex

@@
 \smallskip
-\noindent \textbf{Keywords:} social network, dynamic graph, activity,
-centrality, algorithm.
+\noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
+vertex centrality, online algorithm.
 \end{abstract}
-\tableofcontents
-\newpage
+% \tableofcontents
+% \newpage
 
@@
 \subsection{Properties}
-% TODO
+In most social networks, people have their own friendship circles, and the
+average circle size is quite limited because people do less interaction with
+strangers than their close friends or family members. We call this phenomenon
+the \textbf{sparsity} of social network.
+\definition Reduced edge set (historical) $E_t^\bullet=\{(x_i,y_i)\}$:
+\begin{equation}
+(x,y)\in E_t^\bullet \iff \exists e(x,y,t,w)\in E_t.
+\end{equation}
+\definition Reduced degree $k^\bullet(G_t,v)$:
+\begin{equation}
+k^\bullet(G_t,v)=\#\{u\;|\;(u,v)\in E_t^\bullet\text{ or }(v,u)\in
+E_t^\bullet\}.
+\end{equation}
+
+We then have
+\begin{equation}
+\left<k^\bullet\right>=2\left|E^\bullet\right|/\left|V\right|,
+\end{equation}
+where $\left|E^\bullet\right|/\left|V\right|$ only depends on the structure of
+the network at a time spot. In many available online datasets, such as [?]%TODO
+we can assume $\left<k^\bullet\right>$ is limited by a constant $K$, typically
+$10^2$.
+\definition Sparcity constant $K=\left<k^\bullet\right>$.
+
+\begin{observation} $K=O(1)$.
+\end{observation}
+So if we only use the reduced edge list in our framework as additional memory
+requirements, or similarly speaking, consider the adjacency matrix to be a
+sparse matrix and only store the non-zero entries, the space expense would then
+be just $O(n)$, which is highly available. However this does not means we can
+handle neighbor updating operations in $O(1)$ time, because
+\begin{equation}\max k^\bullet\geq
+\left<k^\bullet\right>=K \end{equation} and the former one may be very large.
+We cannot trivially assert the amortized time complexity to be $O(1)$ neither,
+because the nodes with high degrees may requires more operations over time,
+just like the famous friendship paradox[?].
+
+Another famouse property of social networks is known as the small world
+effect[?], for that the giant component contains nearly all active nodes and it
+has very small diameter.
+
+The clustering coefficient[?], namely
+\begin{equation}
+c.c=\frac{\#\text{closed paths of len 2}}{\#\text{paths of len 2}},
+\end{equation}
+for a typical social network is a possitive
+number, which means people are more willing to make interactions with close
+related people than unfamiliars.
+
 \section{Activity and Centrality}
-% TODO
+
 \subsection{Desiderata}
-% TODO
+\definition $Act(G_t,v)$ returns the activity of node $v$ in the evolving graph in
+time $t$. Then $Act(G_t,v)$ should be a deterministic function of $v$ and
+$E_t$.
+\begin{itemize}
+\item \textbf{normalization}:
+
+We want the metrics to derive other functions, so it will be nice if we can
+limit the range of the function.
+\begin{equation}
+0\leq Act(G_t,v) \leq 1.
+\end{equation}
+
+\item \textbf{initialization}:
+
+A node with no neighbors is totally inactive.
+\begin{equation}
+k(G_t,v)=0\implies Act(G_t,v)=0.
+\end{equation}
+
+\item \textbf{monotonicity}:
+
+If a vertex $v$ performs an interaction $(v,u)$ at time $t$, and suppose the
+interaction is the only change to the graph at time $t$, then the activity of
+$v$ should enhance.
+
+\begin{equation}
+E_{t+1}=E_t\cup\{e(u,v,t,w)\}\implies Act(G_{t+1},v)>Act(G_{t},v).
+\end{equation}
+
+\item \textbf{attenuation}:
+
+If the network keeps silent, the activity metric of any node $v$ should be
+decreasing over time by intuition. Because there is a lower bound for activity
+and we want
+the attenuation process to be infinity long since a node changed the network
+once in past time is potential to make another. So we make the decay rate
+of activity for silent nodes to be also decreasing. However in our pure growing
+model, the change of network structure must happen at integral time. So we
+expand the definition
+\begin{equation}
+G_t=G_{\lfloor t \rfloor}\text{ and } E_t=E_{\lfloor t \rfloor},
+\end{equation}
+to make $Act(G,v)$ a well defined $\mathbb{R}\to [0,1]$ function.
+
+\begin{equation}
+todo
+\end{equation}
+
+\end{itemize}
 \subsection{Design and Analysis}
@@
 \section{Experiment}
-% TODO
+\subsection{Data Generation} 
+Our data generation is base on real social network provided by \cite{database1,
+database2}.  Because the real dynamic graph is hard to obtain, we only use
+these graph as a final state of the dynamic graph, which means the evolving
+graph generated will satisfy all the property that we discussed in section 2.
+Then we artificially add a timeline into that graph to make it become an
+evolving graph.
+
+Another way to generate data is to use the method given by
+\cite{kumar2010structure}.  The author in that paper propose a method to
+simulate the real timeline of a social network, which has same component
+properties and very good similarity with the actual network.  Unfortunately,
+because of the time limitation, we have not implemented this brilliant
+technique.
+
+\subsection{Program}
+We have implemented two of the algorithms using C++ language.
+The program maintains a dynamic graph which contains $n$ vertices and does not have
+any edge at the beginning.
+It support the following operations:
+\begin{itemize}
+	\item \textsc{Add Edge$(u,v)$:} increase the time counter by one, and then add an edge
+		between vertex $u$ and vertex $v$.
+	\item \textsc{Query Degree$(t,u)$:} ask for the degree of $u$ at time $t$.
+	\item \textsc{Query Connectivity$(t,u,v)$:} ask that whether vertices $u,v$ is connected or not
+		$u$ at time $t$.
+\end{itemize}
+Note that the time counter is initially zero.
+Each operation cost $O(\log n)$ time in our implemented algorithm.
+
+\subsection{Checking for Correctness}
+We implemented a simple algorithm together which cost $O(\max\{n,m\})$ time for each operation,
+	where $m$ is the number of edges before the operation.
+We have generated several small test cases and compare the results between the simple program
+	and our $O(\log n)$ program.
+There is no difference found between outputs of the two programs.
+
+\subsection{Checking for Time Complexity}
+We have generated several huge test cases to test the running time of the program.
+The following tabular shows the informations about the cases and the running results.
+\begin{center} \begin{tabular}{|c|c|c|c|c|}
+	\hline
+	Case & Number of & Number of & Density of & Running \\
+	ID & vertices & operations & query & time \\
+	\hline
+	1 & 100000 & 200000 & 0.5 & 0.504 \\
+	\hline
+	2 & 100000 & 200000 & 0.5 & 0.524 \\
+	\hline
+	3 & 100000 & 200000 & 0.5 & 0.516 \\
+	\hline
+	4 & 200000 & 400000 & 0.5 & 1.072 \\
+	\hline
+	5 & 200000 & 400000 & 0.5 & 1.092 \\
+	\hline
+	6 & 200000 & 400000 & 0.5 & 1.072 \\
+	\hline
+	7 & 500000 & 500000 & 0.5 & 1.464 \\
+	\hline
+	8 & 500000 & 500000 & 0.5 & 1.492 \\
+	\hline
+	9 & 500000 & 1000000 & 0.5 & 2.772 \\
+	\hline
+	10 & 500000 & 1000000 & 0.5 & 2.732 \\
+	\hline
+	11 & 500000 & 2000000 & 0.5 & 5.232 \\
+	\hline
+	12 & 500000 & 2000000 & 0.5 & 5.256 \\
+	\hline
+	13 & 1000000 & 2000000 & 0.5 & 5.652 \\
+	\hline
+	14 & 1000000 & 2000000 & 0.5 & 5.808 \\
+	\hline
+	15 & 1000000 & 3000000 & 0.5 & 8.417 \\
+	\hline
+\end{tabular} \end{center}
+We can see that the running time grows as linear as number of operations,
+	but grows much slower when number of vertices grows (as $\log$).
+
 \section{Conclusion and Perspective}

### 2013-06-23 network-science/paper.tex
back!!

@@
 \begin{abstract}
-We address the dynamic properties of typical social networks, in which person
-is considered as vertex while relation is considered as edge. We suppose the
-evolution of a social network overtime only includes bidirectional new
-connections between existing or newly created nodes, and we assume the graph
+We address the dynamic properties of typical social networks, in which people
+are considered as vertices while relations are considered as edges. We suppose
+the evolution of a social network overtime only includes bidirectional new
+connections between existing or newly created nodes, and also assume the graph
 will evolve as a typical social network. We study the activity and centrality
-metrics for nodes in such graphs by regulate a series of reasonable properties
-the metrics should satisfy. We then formally define our metrics and give their
-mathematical analysis. We have developed a practical based framework to
-maintain the evolving large-scale network and the algorithm to compute our
-metrics with preferable time and space consumption, including historical
-queries. Finally, we put the result of experiment with a couple of authentic
-data.
+metrics for nodes in such graphs by regulating a series of reasonable
+properties the metrics should satisfy. We then formally define our metrics and
+give their mathematical analysis. We have developed a practical based framework
+to maintain the evolving large-scale network and the algorithm to compute our
+metrics in preferable time and space consumption, including historical queries.
+Finally, we use a simple model to generate data and apply our results to such
+experiments.
 
@@
 computer science, allowing helpful analysis of large-scaled social behavior
-and tendency. In this paper, we will take more information of social networks,
-the time dimension, and make the similar study to the social behaviors. We
-build metrics for evolving social networks and design the algorithm to
+and tendency. In this paper, we will deal with more information of social
+networks, the time dimension, and make a similar study to the social behaviors.
+We build metrics for evolving social networks and design an algorithm to
 calculate them. We compare how different the outcome by our method would be
@@
 individual vertex. Our work is to promote this methodology to the dynamic
-graphs. We basically design the new dynamic metrics according to existing
+graphs. We basically design new dynamic metrics according to existing
 successful static ones, but we will point out a important metric that can be
@@
 importance of a specific node in graphs of all kinds. There are many previous
-studies about the static graph centralities[?], such as page rank
-algorithm\cite{page1999pagerank}, and there are many useful
+studies about the static graph centralities\cite{newman2010networks}, such as
+page rank algorithm\cite{page1999pagerank}, and there are many useful
 network analysis algorithms that used some kind of graph centralities. However,
@@
 \subsection{Algorithms}
-Graph theory is very successful on storing and solving variant problems on
+Graph theory is very successful on storing and solving various problems on
 static networks, we have sophisticated methodology on finding the shortest
-paths, stratch a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
+paths, get a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
 And we also have a well-established theoretical system to study problems that
@@
 because the nodes with high degrees may requires more operations over time,
-just like the famous friendship paradox[?].
+just like the famous friendship paradox\cite{feld1991your}.
 
-Another famouse property of social networks is known as the small world
-effect[?], for that the giant component contains nearly all active nodes and it
-has very small diameter.
+Another famous property of social networks is known as the small world
+effect\cite{buchanan2003nexus}, for that the giant component contains nearly
+all active nodes and it has very small diameter.
 
@@
 \subsection{Desiderata}
-\definition $Act(G_t,v)$ returns the activity of node $v$ in the evolving graph in
-time $t$. Then $Act(G_t,v)$ should be a deterministic function of $v$ and
+\definition $\mathit{Act}(G_t,v)$ returns the activity of node $v$ in the evolving graph in
+time $t$. Then $\mathit{Act}(G_t,v)$ should be a deterministic function of $v$ and
 $E_t$.
 \begin{itemize}
-\item \textbf{normalization}:
+\item \textbf{(normalization)}:
 
@@
 \begin{equation}
-0\leq Act(G_t,v) \leq 1.
+0\leq \mathit{Act}(G_t,v) \leq 1.
 \end{equation}
 
-\item \textbf{initialization}:
+\item \textbf{(initialization)}:
 
@@
 \begin{equation}
-k(G_t,v)=0\implies Act(G_t,v)=0.
+k(G_t,v)=0\implies \mathit{Act}(G_t,v)=0.
+\end{equation}
+Also we declare
+\begin{equation}
+k(G_{-\infty},v)=0.
 \end{equation}
@@
 
-If a vertex $v$ performs an interaction $(v,u)$ at time $t$, and suppose the
-interaction is the only change to the graph at time $t$, then the activity of
-$v$ should enhance.
+If a vertex $v$ performs an interaction $(v,u)$ at time $t$, i.e., a new edge
+is added to $G_t$, and suppose the interaction is the only change to the graph
+at time $t$, then the activity of $v$ should be greater than if the edge is not
+added.
 
 \begin{equation}
-E_{t+1}=E_t\cup\{e(u,v,t,w)\}\implies Act(G_{t+1},v)>Act(G_{t},v).
+E_t=E'_t\cup\{e(u,v,t,w)\}\implies \mathit{Act}(G_{t},v)>\mathit{Act}(G'_{t},v
+),\label{eq-mono}
 \end{equation}
 
-\item \textbf{attenuation}:
+\item \textbf{symmetry}:
 
-If the network keeps silent, the activity metric of any node $v$ should be
-decreasing over time by intuition. Because there is a lower bound for activity
-and we want
-the attenuation process to be infinity long since a node changed the network
-once in past time is potential to make another. So we make the decay rate
-of activity for silent nodes to be also decreasing. However in our pure growing
-model, the change of network structure must happen at integral time. So we
-expand the definition
-\begin{equation}
-G_t=G_{\lfloor t \rfloor}\text{ and } E_t=E_{\lfloor t \rfloor},
-\end{equation}
-to make $Act(G,v)$ a well defined $\mathbb{R}\to [0,1]$ function.
+For a node $v$ who created new connections at time $t$, we do not care about
+the connection's target nor how is $v$ like before the connection, so
+maintaining the change of $\mathit{Act}$ only depends on its current
+$\mathit{Act}$ value and the $w$ values in the new edges. This property makes
+activity a fair metric for all vertices, and also simplifies the computation.
+
+There exists a function $g$, such that for any possible change
+$E_{t+1}=E_t\cup\{e_i(u_i,v_i,t+1,w_i)\}|_{i=1}^n$,
 
 \begin{equation}
-todo
+\mathit{Act}(G_{t+\varepsilon},v)=g(\mathit{Act}(G_t,v),n,\{w_i\},\varepsilon),
+\qquad (0<\varepsilon<2)\label{eq-sym}
 \end{equation}
 
+\item \textbf{locality}:
+
+We make activity the own property of a single node, so the actions in the
+network in which the node did not participate will not affect the metric.
+
+\begin{equation}
+p<q\text{ and }k(G_p,v)=k(G_q,v)\implies \mathit{Act}(G_q,v)=\mathit{Act}(G'_q,v),\label{eq-loc}
+\end{equation}
+where $G'_q$ has exactly the same structure of $G_p$, excepting for the time
+shift from $p$ to $q$.
+
+\item \textbf{integrity}:
+
+The quantity of actions for a node over time is a discrete function, so we
+cannot define its deriviation $f(t,v)=\frac{\mathrm{d}}{\mathrm{d}t}k(G_t,v)$
+directly. However, we reverse this property, and let $\int_{-\infty}^t
+f(\tau,v)\mathrm{d}\tau\approx k(G_t,v)$, then $f$ will prove soundness
+representing the change rate of degree.
+
+Namely, there exists constants $M>0$, such that for any
+graph $G_T$ with $T$ as the final updating time, if $k(G_T,v)\neq 0$,
+\begin{equation}
+\int_{-\infty}^{\infty} \mathit{Act}(G_t,v)\mathrm{d}t/k(G_T,v)\in\left[\frac{1}{M},M\right].
+\label{eq-int}
+\end{equation}
+
+\definition the \textbf{integral quality} of $\mathit{Act}$ is the minimal such $M$.
+
+The smaller $M$ to be, the more precise is the integration.
+
 \end{itemize}
+
+Then we move on the dynamic centrality, by expanding the often used model
+for static network named Katz centrality[?], which is actually a generalized
+version of eigenvalue centrality[?] which estimate the influence of a node in
+social networks by counting the total number of walks between a pair of
+node[?]. We try to combine the activity and the clasical centrality metric and
+expect to define a new centrality model that is mode sensitive to immediate
+effect.
+
 \subsection{Design and Analysis}
-% TODO
-\section{Algorithms}
-% TODO
+
+\definition $a_{\mu,\eta}(G_t,v)$ is the \textbf{evolving activity} for node $v$, if
+\begin{equation}
+a(G_t,v)=\begin{cases}
+0& (z\geq 0)\\
+\mu^{1/z} & (z<0)
+\end{cases},
+\end{equation}
+where $0<\mu<1$ is the \textbf{decay rate}, and $z$ is a status variable that can
+be determined by the following routine:
+\begin{itemize}
+\item $z=0$ initially, and $z$ can never exceed $0$.
+\item $z$ decrease by $\left(\eta\sum_i w_i\right)$, when new edges with weight
+$w_i$'s are created by $v$, as discussed in \eqref{eq-sym}, Here $\eta>0$ is the
+\textbf{activity delay}.
+\item $z$ increase consistently by time, at the same rate of $t$.
+\end{itemize}
+
+\begin{theorem}
+evolving activity satisfies both normalization and initialization.
+\end{theorem}
+\begin{proof}
+Since the initial value of $z$ is $0$ and $z\leq 0$, by definition we have
+$a(G_t,v)=0$ if $v$ is never changed, because there are no chance for $z$
+to be less than $0$.
+
+Since $0<\mu<1$, and $z\in\mathbb{R}$, we have $0<a(G_t,v)<1$.
+\end{proof}
+
+\begin{theorem}
+evolving activity satisfies monotonicity.
+\end{theorem}
+\begin{proof}
+Refer to \eqref{eq-mono}, we have $z$ for $G$ at time $t$ is decreased, and
+is thus at least $\eta w$ less than $z'$ for $G'$ at time $t$, namely
+\begin{equation}z\leq z'-\eta w<0.\end{equation}
+If $z'=0$, then
+\begin{equation}
+a(G'_t,v)=0<a(G_t,v)=\mu^{1/z}.
+\end{equation}
+Otherwise if $z'<0$,
+\begin{equation}
+z<z'\implies \mu^{1/z}>\mu^{1/z'},
+\end{equation}
+hence
+\begin{equation}
+a(G_t,v)>a(G'_t,v).
+\end{equation}
+\end{proof}
+
+\begin{theorem}
+evolving activity satisfies symmetry.
+\end{theorem}
+\begin{proof}
+Refer to \eqref{eq-sym}, we can write
+\begin{equation}
+g(a(G_t,v),n,\left\{w_i\right\},\varepsilon)=\begin{cases}
+0 &(z^*\geq 0)\\
+\mu^{1/z^*}& (z^*=0)
+\end{cases},
+\end{equation}
+where
+\begin{equation}
+z^*=z+\varepsilon-\eta \sum_i w_i,
+\end{equation}
+and
+\begin{equation}
+z=\begin{cases}
+0&(a(G_t,v)=0)\\
+1/\log_{\mu}a(G_t,v)&(a(G_t,v)>0)
+\end{cases}.
+\end{equation}
+So such $g$ exists.
+\end{proof}
+
+\begin{theorem}
+evolving activity satisfies locality.
+\end{theorem}
+\begin{proof}
+By definition, $z$ will not be affected by non-local change.
+\end{proof}
+
+\begin{theorem}
+evolving activity satisfies integrity.
+\end{theorem}
+\begin{proof}
+	%TODO
+\end{proof}
+
+\definition \textbf{evolving centrality} $\textbf{x}(G_t)$ is a vector in space
+$\mathbb{R}^{|V|}$, where
+\begin{equation}
+\mathbf{x}=\alpha DA \mathbf{x} + \beta\mathbf{1},
+\end{equation}
+$A$ is the adjacency matrix of $G_t$, and $D$ is a diagonal matrix that
+\begin{equation}
+D_{ij}=\begin{cases}
+0&(i\neq j)\\
+\mathit{Act}(G_t,v_i)&(i=j)
+\end{cases}
+\end{equation}
+Then $\textbf{x}_i(G_t)$ is the centrality for node $v_i$ in $G_t$, and is
+scale-relative to the influence of $v_i$ in the network at time $t$.
+
+The equivalent form of $x(G_t,v_i)$ is 
+\begin{equation}
+x_i(G_t,v_i)=\alpha\sum_jA_{ij}\mathit{Act}(G_t,v_j)x_j(G_t,v_j)+\beta.
+\end{equation}
+
+\section{Data structure and Algorithms}
 \subsection{Maintaining the basic graph structure}
-% TODO
-\subsection{Historical Queries}
-% TODO
+We formally define the abstract data type for the pure growing model, and
+create algorithmic functions to the data structure.
+
+A evolving network $G_t(V,E_t)$ is stored in following contents:
+\begin{itemize}
+\item \textsc{CurrentTime}, a non-negative real number.
+\item \textsc{EdgeList}[$1\dots|V|$][$1\dots\textsc{EdgeListLen}$], an array with fixed length, every of
+whose entry points to a sorted array, consisting of the out edges of $v_i$
+in the graph, with elements 
+\begin{itemize}
+\item $u$, the other end point of the edge.
+\item $t$, the time when this edge is added. (the array is sorted by $t$)
+\item $w$, the weight of the edge, can be reduced if the network is unweighted.
+\item $a$, the evolving activity of node $v_i$ at time $t$ after updating this
+edge.
+\end{itemize}
+
+\end{itemize}
 \subsection{Computing Metrics}
-% TODO
-\subsection{Mining Significant Data}
 % TODO

### 2013-06-23 trunk/network-science/paper.tex

@@
 	\Large \textbf{\textsf{
-		Metrics and Algorithms for Evolving Social Networks}} \\[1.2em]
+		Metrics and Algorithms for Evolving Social Networks}} \\[2em]
 	\normalsize 
 		Pufan He\upper{1}, Yichao Zhou\upper{2}, Qiwei Feng\upper{3},
-		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin Xing\upper{6}\\[1em]
+		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin
+		Xing\upper{6}\\[1.5em]
 	\small
@@
 		\upper{6}\href{mailto:823291634@qq.com}{823291634@qq.com}
-	\end{tabular} \\[1em]
+	\end{tabular} \\[1.5em]
 
 	\small Institute for Interdisciplinary Information Sciences,
-	Tsinghua University \\[1.5em]
+	Tsinghua University \\[2em]
+	\normalsize
+	June 24, 2013\\[3em]
 \end{center} \par %>>>
@@
 \begin{abstract}
-We address the dynamic properties of typical social networks, in which person
-is considered as vertex while relation is considered as edge. We suppose the
-evolution of a social network overtime only includes bidirectional new
-connections between existing or newly created nodes, and we assume the graph
+We address the dynamic properties of typical social networks, in which people
+are considered as vertices while relations are considered as edges. We suppose
+the evolution of a social network overtime only includes bidirectional new
+connections between existing or newly created nodes, and also assume the graph
 will evolve as a typical social network. We study the activity and centrality
-metrics for nodes in such graphs by regulate a series of reasonable properties
-the metrics should satisfy. We then formally define our metrics and give their
-mathematical analysis. We have developed a practical based framework to
-maintain the evolving large-scale network and the algorithm to compute our
-metrics with preferable time and space consumption, including historical
-queries. Finally, we put the result of experiment with a couple of authentic
-data.
+metrics for nodes in such graphs by regulating a series of reasonable
+properties the metrics should satisfy. We then formally define our metrics and
+give their mathematical analysis. We have developed a practical based framework
+to maintain the evolving large-scale network and the algorithm to compute our
+metrics in preferable time and space consumption, including historical queries.
+Finally, we use a simple model to generate data and apply our results to such
+experiments.\\[1.5em]
 
-\smallskip
 \noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
@@
 % \tableofcontents
-% \newpage
+\newpage
 
@@
 importance of a specific node in graphs of all kinds. There are many previous
-studies about the static graph centralities[?], such as page rank
-algorithm\cite{page1999pagerank}, and there are many useful
+studies about the static graph centralities\cite{newman2010networks}, such as
+PageRank algorithm\cite{page1999pagerank}, and there are many useful
 network analysis algorithms that used some kind of graph centralities. However,
@@
 
-If a vertex $v$ performs an interaction $(v,u)$ at time $t$, and suppose the
-interaction is the only change to the graph at time $t$, then the activity of
-$v$ should enhance.
+If a vertex $v$ performs an interaction $(v,u)$ at time $t$, i.e., a new edge
+is added to $G_t$, and suppose the interaction is the only change to the graph
+at time $t$, then the activity of $v$ should be greater than if the edge is not
+added.
 
 \begin{equation}
-E_{t+1}=E_t\cup\{e(u,v,t,w)\}\implies Act(G_{t+1},v)>Act(G_{t},v).
+E_t=E'_t\cup\{e(u,v,t,w)\}\implies \mathit{Act}(G_{t},v)>\mathit{Act}(G'_{t},v
+),\label{eq-mono}
 \end{equation}
 
-\item \textbf{attenuation}:
+\item \textbf{symmetry}:
 
-If the network keeps silent, the activity metric of any node $v$ should be
-decreasing over time by intuition. Because there is a lower bound for activity
-and we want
-the attenuation process to be infinity long since a node changed the network
-once in past time is potential to make another. So we make the decay rate
-of activity for silent nodes to be also decreasing. However in our pure growing
-model, the change of network structure must happen at integral time. So we
-expand the definition
-\begin{equation}
-G_t=G_{\lfloor t \rfloor}\text{ and } E_t=E_{\lfloor t \rfloor},
-\end{equation}
-to make $Act(G,v)$ a well defined $\mathbb{R}\to [0,1]$ function.
+For a node $v$ who created new connections at time $t$, we do not care about
+the connection's target nor how is $v$ like before the connection, so
+maintaining the change of $\mathit{Act}$ only depends on its current
+$\mathit{Act}$ value and the $w$ values in the new edges. This property makes
+activity a fair metric for all vertices, and also simplifies the computation.
+
+There exists a function $g$, such that for any possible change
+$E_{t+1}=E_t\cup\{e_i(u_i,v_i,t+1,w_i)\}|_{i=1}^n$,
 
 \begin{equation}
-todo
+\mathit{Act}(G_{t+\varepsilon},v)=g(\mathit{Act}(G_t,v),n,\{w_i\},\varepsilon),
+\qquad (0<\varepsilon<2)\label{eq-sym}
 \end{equation}
 
+\item \textbf{locality}:
+
+We make activity the own property of a single node, so the actions in the
+network in which the node did not participate will not affect the metric.
+
+\begin{equation}
+p<q\text{ and }k(G_p,v)=k(G_q,v)\implies \mathit{Act}(G_q,v)=\mathit{Act}(G'_q,v),\label{eq-loc}
+\end{equation}
+where $G'_q$ has exactly the same structure of $G_p$, excepting for the time
+shift from $p$ to $q$.
+
+\item \textbf{integrity}:
+
+The quantity of actions for a node over time is a discrete function, so we
+cannot define its deriviation $f(t,v)=\frac{\mathrm{d}}{\mathrm{d}t}k(G_t,v)$
+directly. However, we reverse this property, and let $\int_{-\infty}^t
+f(\tau,v)\mathrm{d}\tau\approx k(G_t,v)$, then $f$ will prove soundness
+representing the change rate of degree.
+
+Namely, there exists constants $M>0$, such that for any
+graph $G_T$ with $T$ as the final updating time, if $k(G_T,v)\neq 0$,
+\begin{equation}
+\int_{-\infty}^{\infty} \mathit{Act}(G_t,v)\mathrm{d}t/k(G_T,v)\in\left[\frac{1}{M},M\right].
+\label{eq-int}
+\end{equation}
+
+\definition the \textbf{integral quality} of $\mathit{Act}$ is the minimal such $M$.
+
+The smaller $M$ to be, the more precise is the integration.
+
 \end{itemize}
+
+Then we move on the dynamic centrality, by expanding the often used model
+for static network named Katz centrality[?], which is actually a generalized
+version of eigenvalue centrality[?] which estimate the influence of a node in
+social networks by counting the total number of walks between a pair of
+node[?]. We try to combine the activity and the clasical centrality metric and
+expect to define a new centrality model that is mode sensitive to immediate
+effect.
+
 \subsection{Design and Analysis}
-% TODO
-\section{Algorithms}
-% TODO
+
+\definition $a_{\mu,\eta}(G_t,v)$ is the \textbf{evolving activity} for node $v$, if
+\begin{equation}
+a(G_t,v)=\begin{cases}
+0& (z\geq 0)\\
+\mu^{1/z} & (z<0)
+\end{cases},
+\end{equation}
+where $0<\mu<1$ is the \textbf{decay rate}, and $z$ is a status variable that can
+be determined by the following routine:
+\begin{itemize}
+\item $z=0$ initially, and $z$ can never exceed $0$.
+\item $z$ decrease by $\left(\eta\sum_i w_i\right)$, when new edges with weight
+$w_i$'s are created by $v$, as discussed in \eqref{eq-sym}, Here $\eta>0$ is the
+\textbf{activity delay}.
+\item $z$ increase consistently by time, at the same rate of $t$.
+\end{itemize}
+
+\begin{theorem}
+evolving activity satisfies both normalization and initialization.
+\end{theorem}
+\begin{proof}
+Since the initial value of $z$ is $0$ and $z\leq 0$, by definition we have
+$a(G_t,v)=0$ if $v$ is never changed, because there are no chance for $z$
+to be less than $0$.
+
+Since $0<\mu<1$, and $z\in\mathbb{R}$, we have $0<a(G_t,v)<1$.
+\end{proof}
+
+\begin{theorem}
+evolving activity satisfies monotonicity.
+\end{theorem}
+\begin{proof}
+Refer to \eqref{eq-mono}, we have $z$ for $G$ at time $t$ is decreased, and
+is thus at least $\eta w$ less than $z'$ for $G'$ at time $t$, namely
+\begin{equation}z\leq z'-\eta w<0.\end{equation}
+If $z'=0$, then
+\begin{equation}
+a(G'_t,v)=0<a(G_t,v)=\mu^{1/z}.
+\end{equation}
+Otherwise if $z'<0$,
+\begin{equation}
+z<z'\implies \mu^{1/z}>\mu^{1/z'},
+\end{equation}
+hence
+\begin{equation}
+a(G_t,v)>a(G'_t,v).
+\end{equation}
+\end{proof}
+
+\begin{theorem}
+evolving activity satisfies symmetry.
+\end{theorem}
+\begin{proof}
+Refer to \eqref{eq-sym}, we can write
+\begin{equation}
+g(a(G_t,v),n,\left\{w_i\right\},\varepsilon)=\begin{cases}
+0 &(z^*\geq 0)\\
+\mu^{1/z^*}& (z^*=0)
+\end{cases},
+\end{equation}
+where
+\begin{equation}
+z^*=z+\varepsilon-\eta \sum_i w_i,
+\end{equation}
+and
+\begin{equation}
+z=\begin{cases}
+0&(a(G_t,v)=0)\\
+1/\log_{\mu}a(G_t,v)&(a(G_t,v)>0)
+\end{cases}.
+\end{equation}
+So such $g$ exists.
+\end{proof}
+
+\begin{theorem}
+evolving activity satisfies locality.
+\end{theorem}
+\begin{proof}
+By definition, $z$ will not be affected by non-local change.
+\end{proof}
+
+\begin{theorem}
+evolving activity satisfies integrity.
+\end{theorem}
+\begin{proof}
+	%TODO
+\end{proof}
+
+\definition \textbf{evolving centrality} $\textbf{x}(G_t)$ is a vector in space
+$\mathbb{R}^{|V|}$, where
+\begin{equation}
+\mathbf{x}=\alpha DA^\bullet \mathbf{x} + \beta\mathbf{1},
+\end{equation}
+$A^\bullet$ is the 0/1 adjacency matrix of $E^\bullet_t$ as defined in Section 2,
+because centrality accentuate more on the structure of the network but not the
+intensity of edges. And
+$D$ is a diagonal matrix that
+\begin{equation}
+D_{ij}=\begin{cases}
+0&(i\neq j)\\
+\mathit{Act}(G_t,v_i)&(i=j)
+\end{cases}
+\end{equation}
+Then $\textbf{x}_i(G_t)$ is the centrality for node $v_i$ in $G_t$, and is
+scale-relative to the influence of $v_i$ in the network at time $t$.
+
+The equivalent form of evolving centrality $x(G_t,v_i)$ is 
+\begin{equation}
+x_i(G_t,v_i)=\alpha\sum_jA^\bullet_{ij}
+\mathit{Act}(G_t,v_j)x_j(G_t,v_j)+\beta.
+\end{equation}
+
+We can also change the model into a directional graph, and study the network as
+a citation network:
+
+\definition \textbf{evolving PageRank} $\textbf{x}(G_t)$ is a vector in space
+$\mathbb{R}^{|V|}$, where
+\begin{equation}
+\mathbf{x}=\alpha DKA \mathbf{x} + \beta\mathbf{1},
+\end{equation}
+where $A_{ij}$ stands for the total weight of edges from $j$ to $i$,
+\begin{equation}
+D_{ij}=\begin{cases}
+0&(i\neq j)\\
+\mathit{Act}(G_t,v_i)&(i=j)
+\end{cases};\qquad
+K_{ij}=\begin{cases}
+0&(i\neq j)\\
+k_{\mathrm{out}}(G_t,v_i)&(i=j)
+\end{cases}.
+\end{equation}
+
+The equivalent form of evolving PageRank $x(G_t,v_i)$ is 
+\begin{equation}
+x_i(G_t,v_i)=\alpha\sum_j
+\frac{A_{ij}\mathit{Act}(G_t,v_j)x_j(G_t,v_j)}{k_{\mathrm{out}}(G_t,v_j)}
++\beta.
+\end{equation}
+
+\section{Data structure and Algorithms}
 \subsection{Maintaining the basic graph structure}
-% TODO
-\subsection{Historical Queries}
-% TODO
+We formally define the abstract data type for the pure growing model, and
+create algorithmic functions to the data structure.
+
+A evolving network $G_t(V,E_t)$ is stored in following contents:
+\begin{itemize}
+\item \textit{currentTime}, a non-negative real number.
+\item \textit{edgeList}[$1\dots|V|$], an array that every of
+whose entry points to a sorted array again, consisting the description of the
+in edges of $v_i$ in the graph, each with elements:
+\begin{itemize}
+\item $u$, the other end point of the edge.
+\item $t$, the time when this edge is added. (the array is sorted by $t$)
+\item $w$, the weight of the edge, can be reduced if the network is unweighted.
+\item $a$, the evolving activity of node $v_i$ at time $t$ after updating this
+edge.
+\end{itemize}
+
+\item \textit{edgeListReduced}[$1\dots|V|$], an array that every of
+whose entry points to a sorted array again, consisting the description of the
+neighbors of $v_i$ in the graph, each with a element $u$ (sorted by $u$).
+
+\item \textit{father}[$1\dots|V|$], an array exploited by the historicall
+union-find algorithm, which will be discussed later. Each of the elements
+contains:
+\begin{itemize}
+\item $u$, the identity of $v_i$'s father node if $u\neq 0$, otherwise $v_i$
+is a root node.
+\item $t$, the time when $u$ becomes non-zero.
+\end{itemize}
+
+\end{itemize}
+\textbf{Space complexity:} $O(|V|+|E|)$.
+
+\begin{algorithm}
+\caption{Add a new edge $e(v_i,v_j,t,w)$ to $G_t$}
+\begin{algorithmic}[1]
+\Require $1\leq i,j\leq |V|$, $t\geq currentTime$, $w>0$.
+\Ensure $G_t$ is up-to-date.
+\State 
+\end{algorithmic}
+\end{algorithm}
 \subsection{Computing Metrics}
-% TODO
-\subsection{Mining Significant Data}
 % TODO
@@
 	\hline
-	15 & 1000000 & 3000000 & 0.5 & 8.416 \\
+	15 & 1000000 & 3000000 & 0.5 & 8.417 \\
 	\hline
@@
 % TODO
-\nocite{*}
-\bibliography{paper.bib}
+
+\bibliography{paper}
 \end{document}

### 2013-06-24 network-science/paper.tex

@@
 Finally, we use a simple model to generate data and apply our results to such
-experiments.
+experiments.\\[1.5em]
 
-\smallskip
 \noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
@@
 studies about the static graph centralities\cite{newman2010networks}, such as
-page rank algorithm\cite{page1999pagerank}, and there are many useful
+PageRank algorithm\cite{page1999pagerank}, and there are many useful
 network analysis algorithms that used some kind of graph centralities. However,
@@
 \begin{equation}
-\mathbf{x}=\alpha DA \mathbf{x} + \beta\mathbf{1},
+\mathbf{x}=\alpha DA^\bullet \mathbf{x} + \beta\mathbf{1},
 \end{equation}
-$A$ is the adjacency matrix of $G_t$, and $D$ is a diagonal matrix that
+$A^\bullet$ is the 0/1 adjacency matrix of $E^\bullet_t$ as defined in Section 2,
+because centrality accentuate more on the structure of the network but not the
+intensity of edges. And
+$D$ is a diagonal matrix that
 \begin{equation}
@@
 
-The equivalent form of $x(G_t,v_i)$ is 
+The equivalent form of evolving centrality $x(G_t,v_i)$ is 
 \begin{equation}
-x_i(G_t,v_i)=\alpha\sum_jA_{ij}\mathit{Act}(G_t,v_j)x_j(G_t,v_j)+\beta.
+x_i(G_t,v_i)=\alpha\sum_jA^\bullet_{ij}
+\mathit{Act}(G_t,v_j)x_j(G_t,v_j)+\beta.
+\end{equation}
+
+We can also change the model into a directional graph, and study the network as
+a citation network:
+
+\definition \textbf{evolving PageRank} $\textbf{x}(G_t)$ is a vector in space
+$\mathbb{R}^{|V|}$, where
+\begin{equation}
+\mathbf{x}=\alpha DKA \mathbf{x} + \beta\mathbf{1},
+\end{equation}
+where $A_{ij}$ stands for the total weight of edges from $j$ to $i$,
+\begin{equation}
+D_{ij}=\begin{cases}
+0&(i\neq j)\\
+\mathit{Act}(G_t,v_i)&(i=j)
+\end{cases};\qquad
+K_{ij}=\begin{cases}
+0&(i\neq j)\\
+k_{\mathrm{out}}(G_t,v_i)&(i=j)
+\end{cases}.
+\end{equation}
+
+The equivalent form of evolving PageRank $x(G_t,v_i)$ is 
+\begin{equation}
+x_i(G_t,v_i)=\alpha\sum_j
+\frac{A_{ij}\mathit{Act}(G_t,v_j)x_j(G_t,v_j)}{k_{\mathrm{out}}(G_t,v_j)}
++\beta.
 \end{equation}
@@
 \begin{itemize}
-\item \textsc{CurrentTime}, a non-negative real number.
-\item \textsc{EdgeList}[$1\dots|V|$][$1\dots\textsc{EdgeListLen}$], an array with fixed length, every of
-whose entry points to a sorted array, consisting of the out edges of $v_i$
-in the graph, with elements 
+\item \textit{currentTime}, a non-negative real number.
+\item \textit{edgeList}[$1\dots|V|$], an array that every of
+whose entry points to a sorted array again, consisting the description of the
+in edges of $v_i$ in the graph, each with elements:
 \begin{itemize}
@@
 
+\item \textit{edgeListReduced}[$1\dots|V|$], an array that every of
+whose entry points to a sorted array again, consisting the description of the
+neighbors of $v_i$ in the graph, each with a element $u$ (sorted by $u$).
+
+\item \textit{father}[$1\dots|V|$], an array exploited by the historicall
+union-find algorithm\cite{tarjan1975efficiency} (a weakened model), which
+will be discussed later. Each of the elements contains:
+\begin{itemize}
+\item $u$, the identity of $v_i$'s father node if $u>0$, otherwise $v_i$
+is a root node, and $-u$ is the size of the tree.
+\item $t$, the time when $u$ becomes non-zero.
 \end{itemize}
+
+\end{itemize}
+\textbf{Space complexity:} $O(|V|+|E|)$.
+
+\begin{algorithm}
+\caption{\textsc{AddEdge}($v_i,v_j,t,w$)}
+\textbf{Time Complexity:} $O(\log |V|)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\Require $1\leq i,j\leq |V|$ and $t\geq currentTime$ and $w>0$.
+\Ensure $G_t$ is up-to-date.
+\State $\mathit{currentTime}\gets t$;
+\State append ($j$,$t$,$w$) to \textit{edgeList}[$i$];
+\State append ($i$,$t$,$w$) to \textit{edgeList}[$j$];
+\If{ binary search on \textit{edgeListReduced}[$i$] did not find $j$}
+\State insert $j$ to \textit{edgeListReduced}[$i$] in appropriate position;
+\State binary search $i$ on \textit{edgeListReduced}[$j$];
+\State insert $i$ to \textit{edgeListReduced}[$j$] in appropriate position;
+\EndIf
+\State $p\gets \Call{FindRoot}{i}$;
+\State $q\gets \Call{FindRoot}{j}$;
+\If{$p\neq q$}
+\State \Call{Merge}{$p$,$q$}
+\EndIf
+\end{algorithmic}
+\end{algorithm}
+
+The facility functions of union-find set is defined in follow.
+\begin{algorithm}
+\caption{\textsc{FindRoot}($i$)}
+\textbf{Time Complexity:} $O(\log |V|)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\Require $1\leq i\leq |V|$
+\Ensure return the root of the union tree containing $v_i$.
+\State $\mathit{currentTime}\gets t$;
+\If {$\mathit{father}[i].u>0$}
+	\State \Return{\Call{FindRoot}{$\mathit{father}[i].u$}};
+\Else
+	\State \Return{$i$};
+\EndIf
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{\textsc{Merge}($p$,$q$)}
+\textbf{Time Complexity:} $O(1)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\Require $\mathit{father}[p].u<0$ and $\mathit{father}[q].u<0$
+and $p\neq q$.
+\Ensure Union trees $p$ and $q$.
+\State $x \gets -\mathit{father}[p].u$;
+\State $y \gets -\mathit{father}[q].u$;
+\If {$x>y$}
+	\State \Return{\Call{FindRoot}{$\mathit{father}[i]$}};
+\Else
+	\State \Return{$i$};
+\EndIf
+\end{algorithmic}
+\end{algorithm}
+
 \subsection{Computing Metrics}

### 2013-06-24 trunk/network-science/data/algo.cpp

@@ -2,34 +2,49 @@
 // Algorithm Demo
 //
 // Feng Qiwei
-// 2013.06.21
+// 2013.06.24
 //
 #include <iostream>
 #include <cstring>
 #include <cstdio>
 #include <vector>
+#include <cmath>
 using namespace std;
 
-const int MAXN=1000010;
+const int MAXN=3000010;
 const int MAXQ=3000010;
 
-bool b_deg, b_con, b_vio, b_info;
+const double c_eta=10.;
+const double c_mu=10;
+
+bool b_deg, b_con, b_act;
+bool b_vio, b_info;
 int n;
 int cur_time;
 
-int edge_x[MAXQ], edge_y[MAXQ], edge_t[MAXQ], edge_n;
-vector<int> ex[MAXN];
+int edge_x[MAXQ], edge_y[MAXQ], edge_t[MAXQ], edge_n; double edge_w[MAXQ];
+vector<int> et[MAXN];
+vector<double> ez[MAXN], ed[MAXN];
 int ufs_fa[MAXN], ufs_sz[MAXN], ufs_t[MAXN];
 
-void add_edge(int x, int y) {
+void add_edge(int x, int y, double w) {
 	++edge_n;
 	edge_x[edge_n]=x;
 	edge_y[edge_n]=y;
+	edge_w[edge_n]=w;
 	edge_t[edge_n]=cur_time;
+
+	et[x].push_back(cur_time);
+	et[y].push_back(cur_time);
 	// about degree
 	if(b_deg) {
-		ex[x].push_back(cur_time);
-		ex[y].push_back(cur_time);
+		ed[x].push_back(ed[x].back()+w);
+		ed[y].push_back(ed[y].back()+w);
+	}
+	// about activity
+	if(b_act) {
+		ez[x].push_back(min(0., ez[x].back()-c_eta*w+cur_time-et[x][ez[x].size()-1]));
+		ez[y].push_back(min(0., ez[y].back()-c_eta*w+cur_time-et[y][ez[y].size()-1]));
 	}
 	// about connecting
 	if(b_con) {
@@ -44,19 +59,40 @@ void add_edge(int x, int y) {
 	}
 }
 
-int deg_query(int t, int x) {
-	if(!b_deg) return 0;
-	if(ex[x].size()==0) return 0;
-	return (int)(lower_bound(ex[x].begin(), ex[x].end(), t+1) - ex[x].begin());
[…]

### 2013-06-24 trunk/network-science/data/data-gen.c

@@ -6,8 +6,16 @@
 #include <time.h>
 #include <limits.h>
 
+#include "array.h"
+
 static int state = 1;
 char buffer[1000];
+
+typedef struct {
+    int v;
+    int idx;
+} edge_t;
+array(edge_t) *edge;
 
 int my_rand(void)
 {
@@ -41,16 +49,21 @@ int main(int argc, char *argv[])
     if (strcmp(argv[1], "-e") == 0) {
         freopen(argv[2], "r", stdin);
         int n, m;
+        edge = calloc(n, sizeof(edge[0]));
+
         double p = atof(argv[3]);
         gets(buffer);
         gets(buffer);
         scanf("# Nodes: %d Edges: %d ", &n, &m);
         printf("%d %d\n", n, m);
+
         gets(buffer);
         for (int i = 0; i < m; ++i) {
             int src, dst;
             scanf("%d %d", &src, &dst);
-            printf("a %d %d\n", src, dst);
+            /* arr_push(edge[src], (edge_t){dst, i}); */
+            /* arr_push(edge[dst], (edge_t){src, i}); */
+
             while ((double)my_rand()/INT_MAX < p) {
                 if (my_rand() & 1)
                     printf("q -c %d %d %d\n", my_rand()%(i+2), 1+my_rand()%n, 1+my_rand()%n);
@@ -67,12 +80,14 @@ int main(int argc, char *argv[])
 
         printf("%d\n", n);
         for (int i = 0; i < m; ++i) {
-            printf("a %d %d\n", 1+my_rand()%n, 1+my_rand()%n);
+            printf("a %d %d %.2f\n", 1+my_rand()%n, 1+my_rand()%n, 1+(double)my_rand()/INT_MAX);
             while ((double)my_rand()/INT_MAX < p) {
-                if (my_rand() & 1)
+                if (my_rand() % 3 == 0)
                     printf("q -c %d %d %d\n", my_rand()%(i+2), 1+my_rand()%n, 1+my_rand()%n);
-                else
+                else if (my_rand() % 3 == 1)
                     printf("q -d %d %d\n", my_rand()%(i+2), 1+my_rand()%n);
+                else
+                    printf("q -a %d %d\n", my_rand()%(i+2), 1+my_rand()%n);
             }
         }
     }

### 2013-06-24 network-science/data/array.h

@@ -1,0 +1,68 @@
+/* The MIT License (MIT)
+ *
+ * Copyright (c) 2012, Yichao Zhou
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to
+ * deal in the Software without restriction, including without limitation the
+ * rights to use, copy, modify, merge, publish, distribute, sublicense, and/or
+ * sell copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
+ * AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+ * FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS
+ * IN THE SOFTWARE.
+ */
+
+/* This is a macro library to implement a dynamic-sizegth array.  Notice that
+ * arr_pop will *NOT* shrink the actual memory it uses. */
+
+#pragma once
+
+#include "utility.h"
+
+#define array(type) struct { \
+    type *v; \
+    int size; \
+    int mem_size; \
+}
+
+#define arr_init(x) ({ \
+    (x).v = NULL; \
+    (x).size = 0; \
+    (x).mem_size = 0; \
+})
+
+#define arr_push(x, y) \
+({ \
+    if ((x).size == (x).mem_size) { \
+        (x).mem_size = (x).mem_size * 2 + 2; \
+        (x).v = realloc((x).v, sizeof((x).v[0]) * (x).mem_size); \
+    } \
+    (x).v[(x).size++] = (y); \
+})
+
+#define arr_empty(x) (x.size == 0)
+
[…]

### 2013-06-24 trunk/network-science/data/utility.h

@@ -1,0 +1,62 @@
+/* The MIT License (MIT)
+ *
+ * Copyright (c) 2012, Yichao Zhou
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to
+ * deal in the Software without restriction, including without limitation the
+ * rights to use, copy, modify, merge, publish, distribute, sublicense, and/or
+ * sell copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
+ * AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+ * FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS
+ * IN THE SOFTWARE.
+ */
+
+#pragma once
+
+#define UNUSED(x) (void)(x)
+#define STATIC_ASSERT(e) typedef char _STATIC_ASSERT[(e)?1:-1]
+
+#define swap(x, y) ({ \
+    (void) (&x == &y); \
+    typeof(x) z; \
+    z = x; \
+    x = y; \
+    y = z; \
+})
+
+#define min(x, y) ({ \
+        typeof(x) _min1 = (x); \
+        typeof(y) _min2 = (y); \
+        (void) (&_min1 == &_min2); \
+        _min1 < _min2 ? _min1 : _min2; })
+
+#define max(x, y) ({ \
+        typeof(x) _max1 = (x); \
+        typeof(y) _max2 = (y); \
+        (void) (&_max1 == &_max2); \
+        _max1 > _max2 ? _max1 : _max2; })
+
+#define pair(x, y) struct { x a; y b; }
+
+#define __plus(x, y) ((x)+(y))
[…]

### 2013-06-24 network-science/data/test-correctness.sh

@@ -1,3 +1,3 @@
 #!/bin/bash
-./data-gen 5000 100000 0.5 > data.in
-./algo -i data.in -con -deg -vio -info
+./data-gen 500 500 0.5 > data.in
+./algo -i data.in -con -deg -act -vio -info

### 2013-06-24 trunk/network-science/data/algo.cpp

@@ -14,8 +14,8 @@ using namespace std;
 const int MAXN=3000010;
 const int MAXQ=3000010;
 
-const double c_eta=10.;
-const double c_mu=10;
+const double c_eta=1000.;
+const double c_mu=0.2;
 
 bool b_deg, b_con, b_act;
 bool b_vio, b_info;
@@ -43,8 +43,8 @@ void add_edge(int x, int y, double w) {
 	}
 	// about activity
 	if(b_act) {
-		ez[x].push_back(min(0., ez[x].back()-c_eta*w+cur_time-et[x][ez[x].size()-1]));
-		ez[y].push_back(min(0., ez[y].back()-c_eta*w+cur_time-et[y][ez[y].size()-1]));
+		ez[x].push_back(min(0., ez[x].back()+cur_time-et[x][ez[x].size()-1])-c_eta*w);
+		ez[y].push_back(min(0., ez[y].back()+cur_time-et[y][ez[y].size()-1])-c_eta*w);
 	}
 	// about connecting
 	if(b_con) {
@@ -86,10 +86,10 @@ double vio_act_query(int t, int x) {
 	if(!b_act) return 0.;
 	double z=0; int e=0;
 	for(int i=1; i<=edge_n && edge_t[i]<=t; ++i) {
-		if(edge_x[i]==x) z-=c_eta*edge_w[i];
-		if(edge_y[i]==x) z-=c_eta*edge_w[i];
 		z=min(0., z+edge_t[i]-e);
 		e=edge_t[i];
+		if(edge_x[i]==x) z-=c_eta*edge_w[i];
+		if(edge_y[i]==x) z-=c_eta*edge_w[i];
 	}
 	z=min(0., z+t-e);
 	return pow(c_mu, 1./z);
@@ -126,7 +126,7 @@ void print_usage(char *s) {
 }
 
 int main(int argc, char *argv[]) {
-	b_con=b_deg=b_vio=b_info=false;
+	b_con=b_deg=b_vio=b_act=b_info=false;
 	char *s_inf=NULL;
 	char *s_ouf=NULL;
 	for(int i=1; i<argc; ++i) {
@@ -149,18 +149,18 @@ int main(int argc, char *argv[]) {
 		print_usage(argv[0]);
 		return 0;
 	}
+	FILE *inf=fopen(s_inf, "r");
[…]

### 2013-06-24 network-science/paper.tex

@@
 \item \textit{currentTime}, a non-negative real number.
+\item $\mu$, a real number in range $(0,1)$.
+\item $\eta$, a non-negative real number.
 \item \textit{edgeList}[$1\dots|V|$], an array that every of
@@
 \item $t$, the time when this edge is added. (the array is sorted by $t$)
-\item $w$, the weight of the edge, can be reduced if the network is unweighted.
-\item $a$, the evolving activity of node $v_i$ at time $t$ after updating this
-edge.
+\item $w$, the weight of the edge, can be reduced if the network is
+unweighted.
+\item $s$, the sum of all previous $w$, including this one.
+\item $z$, the status variable for calculating the evolving activity of node
+$v_i$ at time $t$ after updating this edge.
 \end{itemize}
@@
 
-\begin{algorithm}
+The data type contains following functions:
+\begin{itemize}
+\item \textsc{Add Edge}($v_i,v_j,t,w$)
+
+adds $e(v_i,v_j,t,w)$ to the graph and update the graph,
+defined in Algorithm \ref{alg-add}.
+\item \textsc{Query Degree}($t,v$)
+
+returns $k(G_t,v)$, defined in Algorithm \ref{alg-deg}.
+\item \textsc{Query Connectivity}($t,u,v$)
+
+returns whether $u$ and $v$ is connected in the network at time $t$.
+\item \textsc{Query Connectivity}($t,u,v$)
+
+returns whether $u$ and $v$ is connected in the network at time $t$.
+\item \textsc{Query Activity}($t,v$)
+
+returns the evolving activity $a_{\mu,\eta}(G_t,v)$.
+\item \textsc{Query Centrality}($t$, $\alpha$, $\beta$, $\mathbf{x}_0$, $m$)
+
+returns the active centrality vector $\mathbf{x}(G_t)$. Algorithm
+\ref{alg-cen} use the iteration method start with $\mathbf{x}_0$ and for
+$m$ times.
+\end{itemize}
+
+\begin{algorithm}[htbp]
 \caption{\textsc{AddEdge}($v_i,v_j,t,w$)}
+\label{alg-add}
 \textbf{Time Complexity:} $O(\log |V|)$\\
@@
 \begin{algorithmic}[1]
-\Require $1\leq i,j\leq |V|$ and $t\geq currentTime$ and $w>0$.
+\Require $1\leq i,j\leq |V|$ and $t\geq \mathit{currentTime}$ and $w>0$.
 \Ensure $G_t$ is up-to-date.
 \State $\mathit{currentTime}\gets t$;
-\State append ($j$,$t$,$w$) to \textit{edgeList}[$i$];
-\State append ($i$,$t$,$w$) to \textit{edgeList}[$j$];
+\State $z_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.z$;
+\State $t_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.t$;
+\State $z_1\gets z_1+\mathit{currentTime}-t_1$;
+\If {$z_1>0$} \State $z_1\gets 0$;\EndIf
+\State $z_1\gets z_1-\eta\cdot w$;
+\State $z_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.z$;
+\State $t_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.t$;
+\State $z_2\gets z_2+\mathit{currentTime}-t_2$;
+\If {$z_2>0$} \State $z_2\gets 0$;\EndIf
+\State $z_2\gets z_2-\eta\cdot w$;
+\State append ($j$,$t$,$w$,$z_2$) to \textit{edgeList}[$i$];
+\State append ($i$,$t$,$w$,$z_1$) to \textit{edgeList}[$j$];
 \If{ binary search on \textit{edgeListReduced}[$i$] did not find $j$}
@@
 
-The facility functions of union-find set is defined in follow.
-\begin{algorithm}
-\caption{\textsc{FindRoot}($i$)}
+\begin{algorithm}[htbp]
+\caption{\textsc{FindRoot}($i$)}\label{alg1}
 \textbf{Time Complexity:} $O(\log |V|)$\\
@@
 
-\begin{algorithm}
+\begin{algorithm}[htbp]
 \caption{\textsc{Merge}($p$,$q$)}
@@
 \If {$x>y$}
-	\State \Return{\Call{FindRoot}{$\mathit{father}[i]$}};
+	\State $\mathit{father}[q].u\gets p$;
+	\State $\mathit{father}[q].t\gets \mathit{currentTime}$;
+	\State $\mathit{father}[p].u \gets \mathit{father}[p].u-y$;
 \Else
-	\State \Return{$i$};
+	\State $\mathit{father}[p].u\gets q$;
+	\State $\mathit{father}[p].t\gets \mathit{currentTime}$;
+	\State $\mathit{father}[q].u \gets \mathit{father}[q].u-x$;
 \EndIf

### 2013-06-24 network-science/data/algo.cpp

@@ -221,7 +221,8 @@ int main(int argc, char *argv[]) {
 			}
 		}
 	}
-	fprintf(ouf, "Finish.\n");
+	if(b_info)
+		fprintf(ouf, "Finish.\n");
 	if(b_vio)
 		fprintf(ouf, " correct %d/%d (%.5lf)\n", n_yes, n_tot, (double)n_yes/(double)n_tot);
 	

### 2013-06-24 trunk/network-science/data/test-time.sh

@@ -1,3 +1,7 @@
 #!/bin/bash
-./data-gen 1000000 3000000 0.5 > data.in
-time ./algo -i data.in -con -deg
+for (( i=200000; i<=3000000; i=i+200000 ))
+do
+	echo "n=100000 q=$i"
+	./data-gen 100000 $i 0.5 > data.in
+	time ./algo -i data.in -con -deg -act
+done

### 2013-06-24 network-science/data/array.h

@@ -34,35 +34,38 @@
     int mem_size; \
 }
 
-#define arr_init(x) ({ \
-    (x).v = NULL; \
-    (x).size = 0; \
-    (x).mem_size = 0; \
+#define arr_init(arr) ({ \
+    (arr).v = NULL; \
+    (arr).size = 0; \
+    (arr).mem_size = 0; \
 })
 
-#define arr_push(x, y) \
+#define arr_push(arr, element) \
 ({ \
-    if ((x).size == (x).mem_size) { \
-        (x).mem_size = (x).mem_size * 2 + 2; \
-        (x).v = realloc((x).v, sizeof((x).v[0]) * (x).mem_size); \
+    if ((arr).size == (arr).mem_size) { \
+        (arr).mem_size = (arr).mem_size * 2 + 2; \
+        (arr).v = realloc((arr).v, sizeof((arr).v[0]) * (arr).mem_size); \
     } \
-    (x).v[(x).size++] = (y); \
+    (arr).v[(arr).size++] = (element); \
 })
 
-#define arr_empty(x) (x.size == 0)
-
-#define arr_resize(x, new_size) \
+#define arr_erase(arr, index) \
 ({ \
-    if ((x).mem_size < new_size) { \
-        (x).mem_size = min((x).mem_size*2, new_size); \
-        (x).v = realloc((x).v, sizeof((x).v[0]) * (x).mem_size); \
+})
+
+#define arr_empty(arr) ((arr).size == 0)
+
+#define arr_resize(arr, new_size) \
+({ \
+    if ((arr).mem_size < new_size) { \
+        (arr).mem_size = min((arr).mem_size*2, new_size); \
+        (arr).v = realloc((arr).v, sizeof((arr).v[0]) * (arr).mem_size); \
     } \
 })
 
-#define arr_pop(x)   ({(x).size--; (x).v[(x).size];})
-#define arr_free(x)  (free((x).v))
-#define arr_back(x)  ((x).v[(x).size-1])
-#define arr_front(x) ((x).v[0])
+#define arr_pop(arr)   ({(arr).size--; (arr).v[(arr).size];})
+#define arr_free(arr)  (free((arr).v))
+#define arr_back(arr)  ((arr).v[(arr).size-1])
+#define arr_front(arr) ((arr).v[0])
 
-#define arr_for(i, x) for (typeof((x).v) i = (x).v; i < (x).v + (x).size; ++i)
-
[…]

### 2013-06-24 network-science/data/data-gen.c

@@ -15,7 +15,18 @@ typedef struct {
     int v;
     int idx;
 } edge_t;
+
 array(edge_t) *edge;
+array(int) e_q;
+array(int) v_q;
+
+int timer;
+int time_delta;
+
+int num_nodes = 1;
+
+int *src, *dst;
+bool *v_inq, *e_inq, *visited;
 
 int my_rand(void)
 {
@@ -49,26 +60,82 @@ int main(int argc, char *argv[])
     if (strcmp(argv[1], "-e") == 0) {
         freopen(argv[2], "r", stdin);
         int n, m;
-        edge = calloc(n, sizeof(edge[0]));
 
         double p = atof(argv[3]);
         gets(buffer);
         gets(buffer);
         scanf("# Nodes: %d Edges: %d ", &n, &m);
         printf("%d %d\n", n, m);
-
         gets(buffer);
-        for (int i = 0; i < m; ++i) {
-            int src, dst;
-            scanf("%d %d", &src, &dst);
-            /* arr_push(edge[src], (edge_t){dst, i}); */
-            /* arr_push(edge[dst], (edge_t){src, i}); */
 
-            while ((double)my_rand()/INT_MAX < p) {
-                if (my_rand() & 1)
-                    printf("q -c %d %d %d\n", my_rand()%(i+2), 1+my_rand()%n, 1+my_rand()%n);
-                else
-                    printf("q -d %d %d\n", my_rand()%(i+2), 1+my_rand()%n);
+        edge    = calloc(n, sizeof(edge[0]));
+        v_inq   = calloc(n, sizeof(bool));
+        e_inq   = calloc(m, sizeof(bool));
+        visited = calloc(n, sizeof(bool));
+        src     = malloc(m * sizeof(int));
+        dst     = malloc(m * sizeof(int));
+
+        for (int i = 0; i < m; ++i) {
+            scanf("%d %d", src+i, dst+i);
+            arr_push(edge[src[i]], ((edge_t){dst[i], i}));
+            arr_push(edge[dst[i]], ((edge_t){src[i], i}));
+        }
+
+        arr_init(e_q);
+        arr_init(v_q);
+
+        v_inq[src[0]] = true;
+
+        arr_for(p, edge[src[0]])
+            arr_push(e_q, p->idx);
+
+        timer = 0;
+        while (!arr_empty(e_q)) {
+            int idx = my_rand() % e_q.size;
[…]

### 2013-06-24 trunk/network-science/paper.tex

@@
 \usetikzlibrary{automata}
+\usetikzlibrary{plotmarks}
 \usepackage{tikz-3dplot}
@@
 \item \textit{father}[$1\dots|V|$], an array exploited by the historicall
-union-find algorithm, which will be discussed later. Each of the elements
-contains:
+union-find algorithm\cite{tarjan1975efficiency} (a weakened model), which
+will be discussed later. Each of the elements contains:
 \begin{itemize}
-\item $u$, the identity of $v_i$'s father node if $u\neq 0$, otherwise $v_i$
-is a root node.
+\item $u$, the identity of $v_i$'s father node if $u>0$, otherwise $v_i$
+is a root node, and $-u$ is the size of the tree.
 \item $t$, the time when $u$ becomes non-zero.
@@
 
-\begin{algorithm}
-\caption{Add a new edge $e(v_i,v_j,t,w)$ to $G_t$}
+The data type contains following functions:
+\begin{itemize}
+\item \textsc{Add Edge}($v_i,v_j,t,w$)
+
+adds $e(v_i,v_j,t,w)$ to the graph and update the graph,
+defined in Algorithm \ref{alg-add}.
+\item \textsc{Query Degree}($t,v$)
+
+returns $k(G_t,v)$, defined in Algorithm \ref{alg-deg}.
+\item \textsc{Query Connectivity}($t,u,v$)
+
+returns whether $u$ and $v$ is connected in the network at time $t$.
+\item \textsc{Query Connectivity}($t,u,v$)
+
+returns whether $u$ and $v$ is connected in the network at time $t$.
+\item \textsc{Query Activity}($t,v$)
+
+returns the evolving activity $a_{\mu,\eta}(G_t,v)$.
+\item \textsc{Query Centrality}($t$, $\alpha$, $\beta$, $\mathbf{x}_0$, $m$)
+
+returns the active centrality vector $\mathbf{x}(G_t)$. Algorithm
+\ref{alg-cen} use the iteration method start with $\mathbf{x}_0$ and for
+$m$ times.
+\end{itemize}
+
+\begin{algorithm}[htbp]
+\caption{\textsc{Add Edge}($v_i,v_j,t,w$)}
+\label{alg-add}
+\textbf{Time Complexity:} $O(\log |V|)$\\
+\textbf{Additional Space:} $O(1)$
 \begin{algorithmic}[1]
-\Require $1\leq i,j\leq |V|$, $t\geq currentTime$, $w>0$.
+\Require $1\leq i,j\leq |V|$ and $t\geq \mathit{currentTime}$ and $w>0$.
 \Ensure $G_t$ is up-to-date.
-\State 
+\State $\mathit{currentTime}\gets t$;
+\State $z_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.z$;
+\State $t_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.t$;
+\State $s_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.s$;
+\State $z_1\gets z_1+\mathit{currentTime}-t_1$;
+\If {$z_1>0$} \State $z_1\gets 0$;\EndIf
+\State $z_1\gets z_1-\eta\cdot w$;
+\State $z_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.z$;
+\State $t_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.t$;
+\State $z_2\gets z_2+\mathit{currentTime}-t_2$;
+\State $s_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.s$;
+\If {$z_2>0$} \State $z_2\gets 0$;\EndIf
+\State $z_2\gets z_2-\eta\cdot w$;
+\State append ($j$, $t$, $w$, $s_2+w$, $z_2$) to \textit{edgeList}[$i$];
+\State append ($i$, $t$, $w$, $s_1+w$, $z_1$) to \textit{edgeList}[$j$];
+\If{ binary search on \textit{edgeListReduced}[$i$] did not find $j$}
+\State insert $j$ to \textit{edgeListReduced}[$i$] in appropriate position;
+\State binary search $i$ on \textit{edgeListReduced}[$j$];
+\State insert $i$ to \textit{edgeListReduced}[$j$] in appropriate position;
+\EndIf
+\State $p\gets \Call{FindRoot}{i}$;
+\State $q\gets \Call{FindRoot}{j}$;
+\If{$p\neq q$}
+\State \Call{Merge}{$p$,$q$}
+\EndIf
 \end{algorithmic}
 \end{algorithm}
+
+\begin{algorithm}[htbp]
+\caption{\textsc{Find Root}($i$)}\label{alg-find}
+\textbf{Time Complexity:} $O(\log |V|)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\Require $1\leq i\leq |V|$
+\Ensure return the root of the union tree containing $v_i$.
+\State $\mathit{currentTime}\gets t$;
+\If {$\mathit{father}[i].u>0$}
+	\State \Return{\Call{FindRoot}{$\mathit{father}[i].u$}};
+\Else
+	\State \Return{$i$};
+\EndIf
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[htbp]
+\caption{\textsc{Merge}($p$,$q$)}
+\label{alg-merge}
+\textbf{Time Complexity:} $O(1)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\Require $\mathit{father}[p].u<0$ and $\mathit{father}[q].u<0$
+and $p\neq q$.
+\Ensure Union trees $p$ and $q$.
+\State $x \gets -\mathit{father}[p].u$;
+\State $y \gets -\mathit{father}[q].u$;
+\If {$x>y$}
+	\State $\mathit{father}[q].u\gets p$;
+	\State $\mathit{father}[q].t\gets \mathit{currentTime}$;
+	\State $\mathit{father}[p].u \gets \mathit{father}[p].u-y$;
+\Else
+	\State $\mathit{father}[p].u\gets q$;
+	\State $\mathit{father}[p].t\gets \mathit{currentTime}$;
+	\State $\mathit{father}[q].u\gets \mathit{father}[q].u-x$;
+\EndIf
+\end{algorithmic}
+\end{algorithm}
+
 \subsection{Computing Metrics}
@@
 \begin{itemize}
-	\item \textsc{Add Edge$(u,v)$:} increase the time counter by one, and then add an edge
-		between vertex $u$ and vertex $v$.
+	\item \textsc{Add Edge$(u,v,w)$:} increase the time counter by one, and then add an edge
+		of weight $w$ between vertex $u$ and vertex $v$.
 	\item \textsc{Query Degree$(t,u)$:} ask for the degree of $u$ at time $t$.
+	\item \textsc{Query Activity$(t,u)$:} ask for the activity (as we defined) of $u$ at time $t$.
 	\item \textsc{Query Connectivity$(t,u,v)$:} ask that whether vertices $u,v$ is connected or not
@@
 
-\subsection{Checking for Correctness}
+\subsubsection{Checking for Correctness}
 We implemented a simple algorithm together which cost $O(\max\{n,m\})$ time for each operation,
@@
 
-\subsection{Checking for Time Complexity}
+\subsubsection{Checking for Time Complexity}
 We have generated several huge test cases to test the running time of the program.
-The following tabular shows the informations about the cases and the running results.
-\begin{center} \begin{tabular}{|c|c|c|c|c|}
-	\hline
-	Case & Number of & Number of & Density of & Running \\
-	ID & vertices & operations & query & time \\
-	\hline
-	1 & 100000 & 200000 & 0.5 & 0.504 \\
-	\hline
-	2 & 100000 & 200000 & 0.5 & 0.524 \\
-	\hline
-	3 & 100000 & 200000 & 0.5 & 0.516 \\
-	\hline
-	4 & 200000 & 400000 & 0.5 & 1.072 \\
-	\hline
-	5 & 200000 & 400000 & 0.5 & 1.092 \\
-	\hline
-	6 & 200000 & 400000 & 0.5 & 1.072 \\
-	\hline
-	7 & 500000 & 500000 & 0.5 & 1.464 \\
-	\hline
-	8 & 500000 & 500000 & 0.5 & 1.492 \\
-	\hline
-	9 & 500000 & 1000000 & 0.5 & 2.772 \\
-	\hline
-	10 & 500000 & 1000000 & 0.5 & 2.732 \\
-	\hline
-	11 & 500000 & 2000000 & 0.5 & 5.232 \\
-	\hline
-	12 & 500000 & 2000000 & 0.5 & 5.256 \\
-	\hline
-	13 & 1000000 & 2000000 & 0.5 & 5.652 \\
-	\hline
-	14 & 1000000 & 2000000 & 0.5 & 5.808 \\
-	\hline
-	15 & 1000000 & 3000000 & 0.5 & 8.417 \\
-	\hline
-\end{tabular} \end{center}
+The following plots shows the informations about the cases and the running results.
+
+\begin{center} \begin{tikzpicture}[y=.3cm, x=.2cm, font=\sffamily]
+ 	%axis
+	\draw (0,0) -- coordinate (x axis mid) (31, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 16);
+	%ticks
+	\foreach \x in {0,5,...,30}
+		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+	\foreach \y in {0,3,...,15}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	%labels      
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Querys ($\times10^4$)};
+	\node[rotate=90, left=0.8cm] at (0, 15) {\scriptsize Running Time (sec.)};
+	%plots
+	\draw plot[mark=*, mark options={fill=white}] file {exp-n10w};
+\end{tikzpicture} \end{center}
+
 We can see that the running time grows as linear as number of operations,

### 2013-06-24 trunk/network-science/data/algo.cpp

@@ -14,7 +14,7 @@ using namespace std;
 const int MAXN=3000010;
 const int MAXQ=3000010;
 
-const double c_eta=1000.;
+const double c_eta=100.;
 const double c_mu=0.2;
 
 bool b_deg, b_con, b_act;

### 2013-06-24 network-science/data/test-time.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 for (( i=200000; i<=3000000; i=i+200000 ))
 do
-	echo "n=100000 q=$i"
-	./data-gen 100000 $i 0.5 > data.in
+	echo "n=500000 q=$i"
+	./data-gen 500000 $i 0.5 > data.in
 	time ./algo -i data.in -con -deg -act
 done

### 2013-06-24 network-science/paper.tex

@@
 \begin{algorithm}[htbp]
-\caption{\textsc{AddEdge}($v_i,v_j,t,w$)}
+\caption{\textsc{Add Edge}($v_i,v_j,t,w$)}
 \label{alg-add}
@@
 \State $t_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.t$;
+\State $s_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.s$;
 \State $z_1\gets z_1+\mathit{currentTime}-t_1$;
@@
 \State $z_2\gets z_2+\mathit{currentTime}-t_2$;
+\State $s_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.s$;
 \If {$z_2>0$} \State $z_2\gets 0$;\EndIf
 \State $z_2\gets z_2-\eta\cdot w$;
-\State append ($j$,$t$,$w$,$z_2$) to \textit{edgeList}[$i$];
-\State append ($i$,$t$,$w$,$z_1$) to \textit{edgeList}[$j$];
+\State append ($j$, $t$, $w$, $s_2+w$, $z_2$) to \textit{edgeList}[$i$];
+\State append ($i$, $t$, $w$, $s_1+w$, $z_1$) to \textit{edgeList}[$j$];
 \If{ binary search on \textit{edgeListReduced}[$i$] did not find $j$}
@@
 \begin{algorithm}[htbp]
-\caption{\textsc{FindRoot}($i$)}\label{alg1}
+\caption{\textsc{Find Root}($i$)}\label{alg-find}
 \textbf{Time Complexity:} $O(\log |V|)$\\
@@
 \caption{\textsc{Merge}($p$,$q$)}
+\label{alg-merge}
 \textbf{Time Complexity:} $O(1)$\\
@@
 	\State $\mathit{father}[p].t\gets \mathit{currentTime}$;
-	\State $\mathit{father}[q].u \gets \mathit{father}[q].u-x$;
+	\State $\mathit{father}[q].u\gets \mathit{father}[q].u-x$;
 \EndIf
@@
 
-\subsection{Checking for Time Complexity}
+\subsubsection{Checking for Time Complexity}
 We have generated several huge test cases to test the running time of the program.
-The following tabular shows the informations about the cases and the running results.
-\begin{center} \begin{tabular}{|c|c|c|c|c|}
-	\hline
-	Case & Number of & Number of & Density of & Running \\
-	ID & vertices & operations & query & time \\
-	\hline
-	1 & 100000 & 200000 & 0.5 & 0.504 \\
-	\hline
-	2 & 100000 & 200000 & 0.5 & 0.524 \\
-	\hline
-	3 & 100000 & 200000 & 0.5 & 0.516 \\
-	\hline
-	4 & 200000 & 400000 & 0.5 & 1.072 \\
-	\hline
-	5 & 200000 & 400000 & 0.5 & 1.092 \\
-	\hline
-	6 & 200000 & 400000 & 0.5 & 1.072 \\
-	\hline
-	7 & 500000 & 500000 & 0.5 & 1.464 \\
-	\hline
-	8 & 500000 & 500000 & 0.5 & 1.492 \\
-	\hline
-	9 & 500000 & 1000000 & 0.5 & 2.772 \\
-	\hline
-	10 & 500000 & 1000000 & 0.5 & 2.732 \\
-	\hline
-	11 & 500000 & 2000000 & 0.5 & 5.232 \\
-	\hline
-	12 & 500000 & 2000000 & 0.5 & 5.256 \\
-	\hline
-	13 & 1000000 & 2000000 & 0.5 & 5.652 \\
-	\hline
-	14 & 1000000 & 2000000 & 0.5 & 5.808 \\
-	\hline
-	15 & 1000000 & 3000000 & 0.5 & 8.417 \\
-	\hline
-\end{tabular} \end{center}
+The following plots shows the informations about the cases and the running results.
+
+\begin{center} \begin{tikzpicture}[y=.3cm, x=.4cm, font=\sffamily]
+ 	%axis
+	\draw (0,0) -- coordinate (x axis mid) (31, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 19);
+	%ticks
+	\foreach \x in {2,4,...,30}
+		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x0};
+	\foreach \y in {3,6,...,18}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	%labels      
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Querys ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 15) {\scriptsize Running Time (sec.)};
+	%plots
+	\draw plot[mark=*, mark options={fill=white}] file {exp-n10w};
+	\draw plot[mark=triangle*, mark options={fill=white}] file {exp-n50w};
+	\draw plot[mark=square*, mark options={fill=white}] file {exp-n2w};
+\end{tikzpicture} \end{center}
+
 We can see that the running time grows as linear as number of operations,

### 2013-06-24 network-science/data/test-time.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 for (( i=200000; i<=3000000; i=i+200000 ))
 do
-	echo "n=500000 q=$i"
-	./data-gen 500000 $i 0.5 > data.in
+	echo "n=20000 q=$i"
+	./data-gen 20000 $i 0.5 > data.in
 	time ./algo -i data.in -con -deg -act
 done

### 2013-06-24 network-science/paper.tex

@@
 
-\begin{center} \begin{tikzpicture}[y=.3cm, x=.4cm, font=\sffamily]
+\begin{center} \begin{tikzpicture}[y=.3cm, x=.3cm, font=\sffamily]
  	%axis
@@
 		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x0};
-	\foreach \y in {3,6,...,18}
+	\foreach \y in {2,4,...,18}
 		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
@@
 	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Querys ($\times10^3$)};
-	\node[rotate=90, left=0.8cm] at (0, 15) {\scriptsize Running Time (sec.)};
+	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
 	%plots
-	\draw plot[mark=*, mark options={fill=white}] file {exp-n10w};
-	\draw plot[mark=triangle*, mark options={fill=white}] file {exp-n50w};
-	\draw plot[mark=square*, mark options={fill=white}] file {exp-n2w};
+	\draw[color=red!70!black] plot[mark=*, mark options={fill=white}] file {exp-n2w};
+	\draw[color=green!50!black] plot[mark=square*, mark options={fill=white}] file {exp-n10w};
+	\draw[color=blue!80!black] plot[mark=triangle*, mark options={fill=white}] file {exp-n50w};
+	%legend
+	\begin{scope}[shift={(2,13)}]
+	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
+		node[right]{\scriptsize number of nodes=20,000};
+	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
+		node[right]{\scriptsize number of nodes=100,000};
+	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
+		node[right]{\scriptsize number of nodes=500,000};
+	\end{scope}
 \end{tikzpicture} \end{center}

### 2013-06-24 network-science/paper.tex

@@
 \end{equation}
-where $0<\mu<1$ is the \textbf{decay rate}, and $z$ is a status variable that can
+where $\mu>1$ is the \textbf{decay rate}, and $z$ is a status variable that can
 be determined by the following routine:
@@
 
-Since $0<\mu<1$, and $z\in\mathbb{R}$, we have $0<a(G_t,v)<1$.
+Since $\mu>1$, and $z\in\mathbb{R}$, we have $0<a(G_t,v)<1$.
 \end{proof}
@@
 \section{Data structure and Algorithms}
-\subsection{Maintaining the basic graph structure}
+\subsection{Maintaining the graph}
 We formally define the abstract data type for the pure growing model, and
@@
 \item \textit{currentTime}, a non-negative real number.
-\item $\mu$, a real number in range $(0,1)$.
+\item $\mu$, a real number in range $(1,+\infty)$.
 \item $\eta$, a non-negative real number.
@@
 
-returns whether $u$ and $v$ is connected in the network at time $t$.
-\item \textsc{Query Connectivity}($t,u,v$)
-
-returns whether $u$ and $v$ is connected in the network at time $t$.
+returns whether $u$ and $v$ is connected in the network at time $t$,
+defined in
+Algorithm \ref{alg-con}.
 \item \textsc{Query Activity}($t,v$)
 
-returns the evolving activity $a_{\mu,\eta}(G_t,v)$.
+returns the evolving activity $a_{\mu,\eta}(G_t,v)$, defined in
+Algorithm \ref{alg-act}.
 \item \textsc{Query Centrality}($t$, $\alpha$, $\beta$, $\mathbf{x}_0$, $m$)
@@
 $m$ times.
+\item \textsc{Modify Mu}($\mu'$)
+
+change the value of $\mu$ which defines the evolving activity, in case the
+current $\mu$ is inappropriate, defined in algorithm \ref{alg-mu}.
+\item \textsc{Modify Eta}($\eta'$)
+
+change the value of $\eta$ which defines the evolving activity, in case the
+current $\eta$ is inappropriate, defined in algorithm \ref{alg-eta}.
 \end{itemize}
@@
 \EndIf
-\State $p\gets \Call{FindRoot}{i}$;
-\State $q\gets \Call{FindRoot}{j}$;
+\State $p\gets \Call{FindRoot}{i,\mathit{currentTime}}$;
+\State $q\gets \Call{FindRoot}{j,\mathit{currentTime}}$;
 \If{$p\neq q$}
@@
 \begin{algorithm}[htbp]
-\caption{\textsc{Find Root}($i$)}\label{alg-find}
+\caption{\textsc{Find Root}($i$, $t$)}\label{alg-find}
 \textbf{Time Complexity:} $O(\log |V|)$\\
@@
 \Require $1\leq i\leq |V|$
-\Ensure return the root of the union tree containing $v_i$.
+\Ensure return the root of the union tree containing $v_i$ at time $t$.
 \State $\mathit{currentTime}\gets t$;
-\If {$\mathit{father}[i].u>0$}
+\If {$\mathit{father}[i].u>0$ and $\mathit{father}[i].t\leq t$}
 	\State \Return{\Call{FindRoot}{$\mathit{father}[i].u$}};
@@
 
-\subsection{Computing Metrics}
-% TODO
+\begin{algorithm}[htbp]
+\caption{\textsc{Query Connectivity}($t$,$p$,$q$)}
+\label{alg-con}
+\textbf{Time Complexity:} $O(\log |V|)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\Require $1\leq p,q \leq |V|$.
+\Ensure return whether $p$ and $q$ are connected at time $t$.
+\State \Return{$\Call{Find Root}{p,t}=\Call{Find Root}{q,t}$};
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[htbp]
+\caption{\textsc{Query Degree}($t$,$v_i$)}
+\label{alg-deg}
+\textbf{Time Complexity:} $O(\log |V|)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\Require $1\leq i\leq |V|$.
+\Ensure return the degree of $v_i$ at time $t$.
+\State $p\gets\text{binary search }\mathit{edgeList}[i]\text{ for
+the latest edge before }t$;
+\If{ $p$ not found}
+\State\Return{$0$}
+\Else
+\State \Return{$p.s$};
+\EndIf
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[htbp]
+\caption{\textsc{Query Activity}($t$,$v_i$)}
+\label{alg-act}
+\textbf{Time Complexity:} $O(\log |V|)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\Require $1\leq i\leq |V|$.
+\Ensure return the evolving activity $a_{\mu,\eta}(G_t,v_i)$.
+\State $p\gets\text{binary search }\mathit{edgeList}[i]\text{ for
+the latest edge before }t$;
+\If{ $p$ not found}
+\State\Return{$0$}
+\Else
+\State $z=\min(p.z+t-p.t,0)$;
+\If{$z=0$}
+\State \Return{$0$};
+\Else
+\State \Return{$\mu^{1/z}$};
+\EndIf
+\EndIf
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[htbp]
+\caption{\textsc{Modify Mu}($\mu'$)}
+\label{alg-mu}
+\textbf{Time Complexity:} $O(1)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\State $\mu\gets\mu'$;
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[htbp]
+\caption{\textsc{Modify Eta}($\eta'$)}
+\label{alg-eta}
+\textbf{Time Complexity:} $O(1)$\\
+\textbf{Additional Space:} $O(1)$
+\begin{algorithmic}[1]
+\State $\eta\gets\eta'$;\State\Comment{Imcompatible with historical queries.
+The alternative is to rebuild the whole graph.}
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[htbp]
+\caption{\textsc{Query Centrality}($t$,$\alpha$,$\beta$,
+$\mathbf{x}_0$,$m$)}
+\label{alg-cen}
+\textbf{Time Complexity:} $O(mK|V|)$, $K$ is the sparsity constant.\\
+\textbf{Additional Space:} $O(|V|)$
+\begin{algorithmic}[1]
+\Require $0<\alpha<\lambda_1(A^\bullet(G_t))^{-1}$ and $\beta>0$ and $m>0$. Here
+$\lambda_1(A)$ is the maximal possitive eigenvalue of matrix $A$.
+\Ensure return the active centrality $\mathbf{x}(G_t)$.
+\For{$i\gets 1\dots|V|$}
+\State $a[i]\gets \Call{Query Activity}{t,v_i}$;
+\State $\mathbf{x}[i]\gets \mathbf{x}_0[i]$;
+\EndFor
+\For{$\mathit{count}\gets 1\dots m$}
+\For{$i\gets 1\dots|V|$}
+\State $\mathbf{x'}[i]\gets \beta$;
+\EndFor
+\For{$i\gets 1\dots|V|$}
+\ForAll{$j\in\mathit{edgeListReduced}[i]$}
+\State $\mathbf{x'}[i]\gets \mathbf{x'}[i]+\alpha\cdot a[j]\cdot\mathbf{x}[j]$
+\EndFor\EndFor
+\For{$i\gets 1\dots|V|$}
+\State $\mathbf{x}[i]\gets \mathbf{x'}[i]$;
+\EndFor
+\EndFor
+\State\Return{$\mathbf{x}$};
+\end{algorithmic}
+\end{algorithm}
+
 \subsection{Optimization and Parallelizability}
-% TODO
+
+In most cases, we only need to query the latest properties of the graph, i.e.,
+$t=\mathit{currentTime}$. And we observe that in Algorithm \ref{alg-con},
+\ref{alg-deg} and \ref{alg-act}, the binary search can be replace by simply find
+the last entry of the argument sequence. So those three algorithms can be done
+in $O(1)$ time if we do not perform historical queries.
+
+Algorithm \ref{alg-cen} actually repeat the computation of the multiplication
+of a sparse matrix to a vector, which is highly parallelizable[?]. So in a large
+scale distributed system, we can perform very efficient analysis to an evolving
+graph, by our model.
 \section{Experiment}
 \subsection{Data Generation} 
-Our data generation is base on real social network provided by \cite{database1,
-database2}.  Because the real dynamic graph is hard to obtain, we only use
-these graph as a final state of the dynamic graph, which means the evolving
-graph generated will satisfy all the property that we discussed in section 2.
-Then we artificially add a timeline into that graph to make it become an
-evolving graph.
-
-Another way to generate data is to use the method given by
-\cite{kumar2010structure}.  The author in that paper propose a method to
-simulate the real timeline of a social network, which has same component
-properties and very good similarity with the actual network.  Unfortunately,
-because of the time limitation, we have not implemented this brilliant
-technique.
+Our data generation is base on real social networks provided by \cite{database1,
+database2}. Unfortunatly, those databases do not contain evolving history
+recorded data, so we simulate the evolving history by use the
+authentic graph as the final state of the tested dynamic graph.
+We give a random permutation to the edges, in a way such that there will always
+be just one component -- known as the giant component. Because the final state
+is from real world data, it is ensured 
+the evolving graph generated by our model will satisfy all the property that we
+discussed in section 2.2. In addition, Kumar introduced another way to generate
+artificial data of evolving social networks\cite{kumar2010structure}.
 
 \subsection{Program}
-We have implemented two of the algorithms using C++ language.
-The program maintains a dynamic graph which contains $n$ vertices and does not have
-any edge at the beginning.
+We have implemented the algorithms using C++ language without compiler
+optimization, and all execution is done under a typical PC with Intel Core i3.
+
+The program maintains a dynamic graph which contains $n$ vertices and does not
+have any edge at the beginning.
 It support the following operations:
@@
 \subsubsection{Checking for Correctness}
-We implemented a simple algorithm together which cost $O(\max\{n,m\})$ time for each operation,
-	where $m$ is the number of edges before the operation.
-We have generated several small test cases and compare the results between the simple program
-	and our $O(\log n)$ program.
-There is no difference found between outputs of the two programs.
+We implemented a simple algorithm together which cost $O(\max\{n,m\})$ time for
+each operation, where $m$ is the number of edges before the operation.  We have
+generated several small test cases and compare the results between the simple
+program and our $O(\log n)$ program.  There is no difference found between
+outputs of the two programs.
 
@@
 	\foreach \x in {2,4,...,30}
-		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x0};
+		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
 	\foreach \y in {2,4,...,18}
@@
 	%labels      
-	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Querys ($\times10^3$)};
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Queries ($\times10^5$)};
 	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
@@
 
-We can see that the running time grows as linear as number of operations,
-	but grows much slower when number of vertices grows (as $\log$).
+We can verify that our algorithm model works efficiently with those four kinds
+of basic operations.
 

### 2013-06-24 trunk/network-science/paper.tex

@@
 
-\begin{center} \begin{tikzpicture}[y=.3cm, x=.2cm, font=\sffamily]
+\begin{center} \begin{tikzpicture}[y=.3cm, x=.3cm, font=\sffamily]
  	%axis
 	\draw (0,0) -- coordinate (x axis mid) (31, 0);
-	\draw (0,0) -- coordinate (y axis mid) (0, 16);
+	\draw (0,0) -- coordinate (y axis mid) (0, 19);
 	%ticks
-	\foreach \x in {0,5,...,30}
+	\foreach \x in {2,4,...,30}
 		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
-	\foreach \y in {0,3,...,15}
+	\foreach \y in {2,4,...,18}
 		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
 	%labels      
-	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Querys ($\times10^4$)};
-	\node[rotate=90, left=0.8cm] at (0, 15) {\scriptsize Running Time (sec.)};
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Operations ($\times10^5$)};
+	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
 	%plots
-	\draw plot[mark=*, mark options={fill=white}] file {exp-n10w};
+	\draw[color=red!70!black] plot[mark=*, mark options={fill=white}] file {exp-n2w};
+	\draw[color=green!50!black] plot[mark=square*, mark options={fill=white}] file {exp-n10w};
+	\draw[color=blue!80!black] plot[mark=triangle*, mark options={fill=white}] file {exp-n50w};
+	%legend
+	\begin{scope}[shift={(2,13)}]
+	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
+		node[right]{\scriptsize number of nodes=20,000};
+	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
+		node[right]{\scriptsize number of nodes=100,000};
+	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
+		node[right]{\scriptsize number of nodes=500,000};
+	\end{scope}
 \end{tikzpicture} \end{center}
 
-We can see that the running time grows as linear as number of operations,
-	but grows much slower when number of vertices grows (as $\log$).
+We can verify that our algorithm model works efficiently with those four kinds
+of basic operations.
+
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+ 	%axis
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 14);
+	%ticks
+	\foreach \x in {1,2,...,20}
+		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+	\foreach \y in {2,4,...,13}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	%labels      
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Nodes ($\times10^5$)};
+	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
+	%plots
+	\draw[color=red!70!black] plot[mark=*, mark options={fill=white}] file {exp-q10w};
+	\draw[color=green!50!black] plot[mark=square*, mark options={fill=white}] file {exp-q50w};
+	\draw[color=blue!80!black] plot[mark=triangle*, mark options={fill=white}] file {exp-q100w};
+	%legend
+	\begin{scope}[shift={(2,11)}]
+	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
+		node[right]{\scriptsize number of Operations=100,000};
+	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
+		node[right]{\scriptsize number of Operations=500,000};
+	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
+		node[right]{\scriptsize number of Operations=1000,000};
+	\end{scope}
+\end{tikzpicture} \end{center}
 

### 2013-06-24 trunk/network-science/data/test-time.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
-for (( i=200000; i<=3000000; i=i+200000 ))
+for (( i=50000; i<=2000000; i=i+10000000 ))
 do
-	echo "n=20000 q=$i"
-	./data-gen 20000 $i 0.5 > data.in
+	echo "n=$i q=1000000"
+	./data-gen $i 1000000 0.5 > data.in
 	time ./algo -i data.in -con -deg -act
 done

### 2013-06-24 network-science/paper.tex

@@
 
-In Section 3 we will concentrate on centrality and activity in evolving social
+In section 3 we will concentrate on centrality and activity in evolving social
 network. We will define what centrality or activity is good, and we will design
-some instance of those metrics by the standard we set. In Section 4, we will
+some instance of those metrics by the standard we set. In section 4, we will
 give the algorithms to compute our designed centrality and activity from the
@@
 show how to quickly locate significant vertices that has high activity or
-centrality at a specific time. In Section 5, we will show the metrics make
+centrality at a specific time. In section 5, we will show the metrics make
 sense with real world data.
@@
 
-In Section 2 we will discuss the known properties of a typical social network,
-which could be helpful for our algorithm designs. In Section 4, we will
+In section 2 we will discuss the known properties of a typical social network,
+which could be helpful for our algorithm designs. In section 4, we will
 establish a framework of data structure and algorithms to solve series of
@@
 \subsection{Definition}
-\definition A \textbf{pure growing model} for an evolving graph $EG$ is defined
-in pair \begin{equation}
+\begin{definition}
+A \textbf{pure growing model} for an evolving graph $EG$ is defined in pair:
+\begin{equation}
 EG=(V,E),
 \end{equation}
-where $V$ is the set of all nodes in the network, and $E$
-is the set of edges, formally an edge $e\in E$ for $e=(u,v,t)$,
-where $u,v\in V$ are the two end points of the edge, $u<v$ (to ensure
-bidirectional), $t\in \mathbb{N}$. The $t$ component stored the forming time of
-the graph. As for weighted evolving graph model, we modifies $e\in E$ for
-$e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands for the multiplicity of the
-edge, which might be useful in some circumstances, and the others stay the same
-meaning. In the unweighted case, we can simply set $w=1$ for all edges.
+where $V$ is the set of all nodes in the network, and $E$ is the set of edges,
+formally an edge $e\in E$ for $e=(u,v,t)$, where $u,v\in V$ are the two end
+points of the edge, $u<v$ (to ensure bidirectional), $t\in \mathbb{N}$. The $t$
+component stored the forming time of the graph. As for weighted evolving graph
+model, we modifies $e\in E$ for $e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands
+for the multiplicity of the edge, which might be useful in some circumstances,
+and the others stay the same meaning. In the unweighted case, we can simply set
+$w=1$ for all edges.
+\end{definition}
 
-\definition The historical edge set $E_t$
+\begin{definition}
+The historical edge set $E_t$
 \begin{equation}
@@
 \begin{equation}
-\forall t, E_t\subseteq E\text{ and }p\leq q\implies E_p\subseteq E_q.
+\forall t: E_t\subseteq E\text{ and }p\leq q\implies E_p\subseteq E_q.
 \end{equation}
@@
 of the whole network at time $t$.
+\end{definition}
 
@@
 possible active vertices has been already defined, so $V$ does not change.
-\definition 
+
+\begin{definition}
 $EG^*=(V,E^*)$ where $E\subseteq E^*$. We assume the edges are added to the
@@
 \begin{equation}
-\forall e\in E^*\setminus E, \forall e'\in E, e=(u,v,t,w)\text{ and }
-e'=(u',v',t',w'), t\geq t'.
+\forall (u,v,t,w) \in E^*\setminus E,\, \forall (u',v',t',w')\in E: t \geq t'.
 \end{equation}
+\end{definition}
 
 And we define the notation of some frequently used basic functions:
-
-\definition The adjacency matrix.
+\begin{definition}
+The adjacency matrix
 \begin{equation}
@@
 \end{equation}
+\end{definition}
 
@@
 the \textbf{sparsity} of social network.
-\definition Reduced edge set (historical) $E_t^\bullet=\{(x_i,y_i)\}$:
+
+\begin{definition}
+Reduced edge set (historical) $E_t^\bullet=\{(x_i,y_i)\}$:
 \begin{equation}
-(x,y)\in E_t^\bullet \iff \exists e(x,y,t,w)\in E_t.
+(x,y)\in E_t^\bullet \iff \exists e: e=(x,y,t,w)\in E_t.
 \end{equation}
-\definition Reduced degree $k^\bullet(G_t,v)$:
+\end{definition}
+
+\begin{definition}
+Reduced degree $k^\bullet(G_t,v)$:
 \begin{equation}
-k^\bullet(G_t,v)=\#\{u\;|\;(u,v)\in E_t^\bullet\text{ or }(v,u)\in
-E_t^\bullet\}.
+k^\bullet(G_t,v)=\Big|\{u\;|\;(u,v)\in E_t^\bullet\text{ or }(v,u)\in
+E_t^\bullet\}\Big|.
 \end{equation}
+\end{definition}
 
@@
 We want the metrics to derive other functions, so it will be nice if we can
-limit the range of the function.
+limit the range of the function:
 \begin{equation}
@@
 
-A node with no neighbors is totally inactive.
+A node with no neighbors is totally inactive:
 \begin{equation}
@@
 \end{equation}
-Also we declare
+Also we declare that
 \begin{equation}
@@
 added.
-
 \begin{equation}
 E_t=E'_t\cup\{e(u,v,t,w)\}\implies \mathit{Act}(G_{t},v)>\mathit{Act}(G'_{t},v
-),\label{eq-mono}
+).\label{eq-mono}
 \end{equation}
@@
 There exists a function $g$, such that for any possible change
-$E_{t+1}=E_t\cup\{e_i(u_i,v_i,t+1,w_i)\}|_{i=1}^n$,
+$E_{t+1}=E_t\cup\{e_i(u_i$, $v_i$, $t+1$, $w_i)\}|_{i=1}^n$,
 
@@
 \mathit{Act}(G_{t+\varepsilon},v)=g(\mathit{Act}(G_t,v),n,\{w_i\},\varepsilon),
-\qquad (0<\varepsilon<2)\label{eq-sym}
+\label{eq-sym}
 \end{equation}
+where $0<\varepsilon<2$.
 
@@
 \begin{equation}
-\int_{-\infty}^{\infty} \mathit{Act}(G_t,v)\mathrm{d}t/k(G_T,v)\in\left[\frac{1}{M},M\right].
+\int_{-\infty}^{\infty} \frac{\mathit{Act}(G_t,v)}{k(G_T,v)}\mathrm{d}t\in\left[\frac{1}{M},M\right].
 \label{eq-int}
 \end{equation}
-
-\definition the \textbf{integral quality} of $\mathit{Act}$ is the minimal such $M$.
 
@@
 \end{itemize}
+
+\begin{definition}
+The \textbf{integral quality} of $\mathit{Act}$ is the minimal such $M$.
+\end{definition}
 
@@
 
-\definition $a_{\mu,\eta}(G_t,v)$ is the \textbf{evolving activity} for node $v$, if
+\begin{definition}[Evolving Activity]
+$a_{\mu,\eta}(G_t,v)$ is the \textbf{evolving activity} for node $v$, if
 \begin{equation}
@@
 \end{itemize}
+\end{definition}
 
 \begin{theorem}
-evolving activity satisfies both normalization and initialization.
+Evolving activity satisfies both normalization and initialization.
 \end{theorem}
@@
 \begin{theorem}
-evolving activity satisfies monotonicity.
+Evolving activity satisfies monotonicity.
 \end{theorem}
@@
 \begin{theorem}
-evolving activity satisfies symmetry.
+Evolving activity satisfies symmetry.
 \end{theorem}
@@
 \begin{theorem}
-evolving activity satisfies locality.
+Evolving activity satisfies locality.
 \end{theorem}
@@
 \begin{theorem}
-evolving activity satisfies integrity.
+Evolving activity satisfies integrity.
 \end{theorem}
@@
 
-\definition \textbf{evolving centrality} $\textbf{x}(G_t)$ is a vector in space
+\begin{definition}[Evolving Centrality]
+\textbf{Evolving centrality} $\textbf{x}(G_t)$ is a vector in space
 $\mathbb{R}^{|V|}$, where
@@
 \end{equation}
-$A^\bullet$ is the 0/1 adjacency matrix of $E^\bullet_t$ as defined in Section 2,
+$A^\bullet$ is the 0/1 adjacency matrix of $E^\bullet_t$ as defined in section 2,
 because centrality accentuate more on the structure of the network but not the
@@
 scale-relative to the influence of $v_i$ in the network at time $t$.
+\end{definition}
 
@@
 
-\definition \textbf{evolving PageRank} $\textbf{x}(G_t)$ is a vector in space
+\begin{definition}[Evolving PageRank]
+\textbf{Evolving PageRank} $\textbf{x}(G_t)$ is a vector in space
 $\mathbb{R}^{|V|}$, where
@@
 
-adds $e(v_i,v_j,t,w)$ to the graph and update the graph,
-defined in Algorithm \ref{alg-add}.
+Add $e(v_i,v_j,t,w)$ to the graph and update the graph,
+defined in algorithm \ref{alg-add}.
 \item \textsc{Query Degree}($t,v$)
 
-returns $k(G_t,v)$, defined in Algorithm \ref{alg-deg}.
+Return $k(G_t,v)$, defined in algorithm \ref{alg-deg}.
 \item \textsc{Query Connectivity}($t,u,v$)
 
-returns whether $u$ and $v$ is connected in the network at time $t$,
-defined in
-Algorithm \ref{alg-con}.
+Return whether $u$ and $v$ is connected in the network at time $t$, defined in
+algorithm \ref{alg-con}.
+
 \item \textsc{Query Activity}($t,v$)
 
-returns the evolving activity $a_{\mu,\eta}(G_t,v)$, defined in
-Algorithm \ref{alg-act}.
+Returns the evolving activity $a_{\mu,\eta}(G_t,v)$, defined in algorithm
+\ref{alg-act}.
+
 \item \textsc{Query Centrality}($t$, $\alpha$, $\beta$, $\mathbf{x}_0$, $m$)
 
-returns the active centrality vector $\mathbf{x}(G_t)$. Algorithm
-\ref{alg-cen} use the iteration method start with $\mathbf{x}_0$ and for
-$m$ times.
+Return the active centrality vector $\mathbf{x}(G_t)$. Algorithm \ref{alg-cen}
+use the iteration method start with $\mathbf{x}_0$ and for $m$ times.
+
 \item \textsc{Modify Mu}($\mu'$)
 
-change the value of $\mu$ which defines the evolving activity, in case the
+Change the value of $\mu$ which defines the evolving activity, in case the
 current $\mu$ is inappropriate, defined in algorithm \ref{alg-mu}.
+
 \item \textsc{Modify Eta}($\eta'$)
 
-change the value of $\eta$ which defines the evolving activity, in case the
+Change the value of $\eta$ which defines the evolving activity, in case the
 current $\eta$ is inappropriate, defined in algorithm \ref{alg-eta}.
@@
 	%labels      
-	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Queries ($\times10^5$)};
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Operations ($\times10^5$)};
 	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
@@
 
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+ 	%axis
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 14);
+	%ticks
+	\foreach \x in {1,2,...,20}
+		\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+	\foreach \y in {2,4,...,13}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	%labels      
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Number of Nodes ($\times10^5$)};
+	\node[rotate=90, left=0.8cm] at (0, 12) {\scriptsize Running Time (sec.)};
+	%plots
+	\draw[color=red!70!black] plot[mark=*, mark options={fill=white}] file {exp-q10w};
+	\draw[color=green!50!black] plot[mark=square*, mark options={fill=white}] file {exp-q50w};
+	\draw[color=blue!80!black] plot[mark=triangle*, mark options={fill=white}] file {exp-q100w};
+	%legend
+	\begin{scope}[shift={(2,11)}]
+	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
+		node[right]{\scriptsize number of Operations=100,000};
+	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
+		node[right]{\scriptsize number of Operations=500,000};
+	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
+		node[right]{\scriptsize number of Operations=1000,000};
+	\end{scope}
+\end{tikzpicture} \end{center}
+
 \section{Conclusion and Perspective}

### 2013-06-24 network-science/data/data-gen.c

@@ -119,7 +119,9 @@ int main(int argc, char *argv[])
                 e_inq[idx] = true;
 
                 ++num_nodes;
-                time_delta = max(1, INT_MAX / 100 / num_nodes);
+                double flt = INT_MAX / 1000000. / num_nodes;
+                if (flt > 1)
+                    time_delta = max(1, 
                 timer += time_delta;
                 printf("d %d\n", time_delta);
 

### 2013-06-24 trunk/network-science/paper.tex

@@
 \end{itemize}
+\end{definition}
+
+\begin{center} \begin{tikzpicture}[y=.3cm, x=.3cm, font=\sffamily]
+  \begin{axis}[ 
+    xlabel={$z$},
+    ylabel={$a$}
+  ] 
+    \addplot[domain=-10:-0.001] {exp(ln(10)*(1/x))}; 
+  \end{axis}
+\end{tikzpicture} \end{center}
 
 \begin{theorem}
-evolving activity satisfies both normalization and initialization.
+Evolving activity satisfies both normalization and initialization.
 \end{theorem}

### 2013-06-24 trunk/network-science/paper.tex

@@
 quantification to concentrate on specific features of the whole graph, or an
-individual vertex. Our work is to promote this methodology to the dynamic
-graphs. We basically design new dynamic metrics according to existing
-successful static ones, but we will point out a important metric that can be
-only observed in time evolving networks, the activity. Intuitively speaking,
-a vertex with high activity indicates more frequent recent social actions, and
-the vertex is more willing to make new change by the structural sense of graph.
-The accuracy of activity will be quite vital to recommendation algorithms of
-advertisement, new friends, or search results. Activity can be also used by
-other metrics, so that the computation of other metrics will no longer need the
-time information directly, but referring to the activity instead.
+individual vertex. Our work is to promote this method to the dynamic graphs. We
+basically design new dynamic metrics according to existing successful static
+ones, but we will point out a important metric that can be only observed in
+time evolving networks, the activity. Intuitively speaking, a vertex with high
+activity indicates more frequent recent social actions, and the vertex is more
+willing to make new change by the structural sense of graph.  The accuracy of
+activity will be quite vital to recommendation algorithms of advertisement, new
+friends, or search results. Activity can be also used by other metrics, so that
+the computation of other metrics will no longer need the time information
+directly, but referring to the activity instead.
 
@@
 studies about the static graph centralities\cite{newman2010networks}, such as
-PageRank algorithm\cite{page1999pagerank}, and there are many useful
-network analysis algorithms that used some kind of graph centralities. However,
-most social networks change over time, and even more unfortunately, some of the
+PageRank algorithm\cite{page1999pagerank}, and there are many useful network
+analysis algorithms that used some kind of graph centralities. However, most
+social networks change over time, and even more unfortunately, some of the
 networks are large-scaled, which could make the analysis become hard and
@@
 effect can also become a factor of the centrality, that is, the same graph with
-different evolving sequence may have totally different metrics. On an
-intuitive level, the node connected with more higher activity nodes should be
-more important at that time, even if other node have much more silent
-neighbors. If we do not excavate the information on the time dimension, we will
-lose tremendous information and also the possibility of accumulative
-computation which could be helpful in enhancement the speed of answering
-consistent querying.
+different evolving sequence may have totally different metrics. On an intuitive
+level, the node connected with more higher activity nodes should be more
+important at that time, even if other node have much more silent neighbors. If
+we do not excavate the information on the time dimension, we will lose
+tremendous information and also the possibility of accumulative computation
+which could be helpful in enhancement the speed of answering consistent
+querying.
 
@@
 So if we only use the reduced edge list in our framework as additional memory
-requirements, or similarly speaking, consider the adjacency matrix to be a
-sparse matrix and only store the non-zero entries, the space expense would then
-be just $O(n)$, which is highly available. However this does not means we can
-handle neighbor updating operations in $O(1)$ time, because
-\begin{equation}\max k^\bullet\geq
-\left<k^\bullet\right>=K \end{equation} and the former one may be very large.
-We cannot trivially assert the amortized time complexity to be $O(1)$ neither,
-because the nodes with high degrees may requires more operations over time,
-just like the famous friendship paradox\cite{feld1991your}.
+requirements, namely considering the adjacency matrix to be a sparse matrix and
+only store the non-zero entries, the space expense would then be just $O(n)$,
+which is highly available. However this does not means we can handle neighbor
+updating operations in $O(1)$ time, because
+\begin{equation}
+\max k^\bullet\geq \left<k^\bullet\right>=K
+\end{equation}
+and the former one may be very large.  We cannot trivially assert the amortized
+time complexity to be $O(1)$ neither, because the nodes with high degrees may
+requires more operations over time, just like the famous friendship
+paradox\cite{feld1991your}.
 
@@
 
-\begin{center} \begin{tikzpicture}[y=.3cm, x=.3cm, font=\sffamily]
+\begin{center} \begin{tikzpicture}
   \begin{axis}[ 
     xlabel={$z$},
-    ylabel={$a$}
+    ylabel={evolving activity}
   ] 
-    \addplot[domain=-10:-0.001] {exp(ln(10)*(1/x))}; 
+  \addplot[color=blue!50!black,samples=300,domain=-20:-0.001] {exp(ln(10)*(1/x))}; 
+  \addplot[color=green!50!black,samples=300,domain=-20:-0.001] {exp(ln(100)*(1/x))}; 
+  \addplot[color=red!50!black,samples=300,domain=-20:-0.001] {exp(ln(1000)*(1/x))}; 
   \end{axis}
-\end{tikzpicture} \end{center}
+\end{tikzpicture}
+
+\begin{color}{blue!50!black}blue
+\end{color}: $\mu=10$,
+\begin{color}{green!50!black}green
+\end{color}: $\mu=100$,
+\begin{color}{red!50!black}red
+\end{color}: $\mu=1000$\end{center}
 
@@
 We have implemented the algorithms using C++ language without compiler
-optimization, and all execution is done under a typical PC with Intel Core i3.
+optimization, and all execution is done under a typical PC with Intel Core i3
+M380.
 

### 2013-06-24 trunk/network-science/data/data-gen.c

@@ -51,17 +51,15 @@ int main(int argc, char *argv[])
 {
     if (argc == 1) {
         puts("data-gen [number of vertices] [number of edges] [question density] ");
-        puts("data-gen -e filename [question density]");
+        puts("data-gen -e filename");
         return 0;
     }
 
-    assert(argc == 4);
-
     if (strcmp(argv[1], "-e") == 0) {
+        assert(argc == 3);
+
         freopen(argv[2], "r", stdin);
         int n, m;
-
-        double p = atof(argv[3]);
         gets(buffer);
         gets(buffer);
         scanf("# Nodes: %d Edges: %d ", &n, &m);
@@ -121,12 +119,15 @@ int main(int argc, char *argv[])
                 ++num_nodes;
                 double flt = INT_MAX / 1000000. / num_nodes;
                 if (flt > 1)
-                    time_delta = max(1, 
+                    time_delta = (int)flt;
+                else
+                    time_delta = ((double)my_rand() / INT_MAX < flt);
                 timer += time_delta;
                 printf("d %d\n", time_delta);
 
                 printf("a %d %d %.2f\n", 1+src[idx], 1+dst[idx], 1.);
 
+                /*
                 while ((double)my_rand()/INT_MAX < p) {
                     int r_time = my_rand() % (timer+1);
                     int node1 = v_q.v[my_rand()%v_q.size]+1;
@@ -138,9 +139,11 @@ int main(int argc, char *argv[])
                     else
                         printf("q -a %d %d\n", r_time, node2);
                 }
+                */
             }
         }
     } else {
+        assert(argc == 4);
         int n = atoi(argv[1]);
         int m = atoi(argv[2]);
         double p = atof(argv[3]);

### 2013-06-24 network-science/paper.tex

@@
 \end{definition}
+
+\begin{center} \begin{tikzpicture}
+  \begin{axis}[ 
+    xlabel={$z$},
+    ylabel={evolving activity}
+  ] 
+  \addplot[color=blue!50!black,samples=300,domain=-20:-0.001] {exp(ln(10)*(1/x))}; 
+  \addplot[color=green!50!black,samples=300,domain=-20:-0.001] {exp(ln(100)*(1/x))}; 
+  \addplot[color=red!50!black,samples=300,domain=-20:-0.001] {exp(ln(1000)*(1/x))}; 
+  \end{axis}
+\end{tikzpicture}
+
+\begin{color}{blue!50!black}blue
+\end{color}: $\mu=10$,
+\begin{color}{green!50!black}green
+\end{color}: $\mu=100$,
+\begin{color}{red!50!black}red
+\end{color}: $\mu=1000$\end{center}
 
@@
 We have implemented the algorithms using C++ language without compiler
-optimization, and all execution is done under a typical PC with Intel Core i3.
+optimization, and all execution is done under a typical PC with 
+Intel (R) Core (TM) i3 CPU M380  @ 2.53GHz, 2GB RAM.
 
@@
 	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
-		node[right]{\scriptsize number of nodes=20,000};
+		node[right]{\scriptsize number of nodes=20\,000};
 	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
-		node[right]{\scriptsize number of nodes=100,000};
+		node[right]{\scriptsize number of nodes=100\,000};
 	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
-		node[right]{\scriptsize number of nodes=500,000};
+		node[right]{\scriptsize number of nodes=500\,000};
 	\end{scope}
@@
 	\draw[color=red!70!black] (0,0) -- plot[mark=*, mark options={fill=white}] (1,0) -- (2,0)
-		node[right]{\scriptsize number of Operations=100,000};
+		node[right]{\scriptsize number of operations=100\,000};
 	\draw[color=green!50!black] (0,1) -- plot[mark=square*, mark options={fill=white}] (1,1) -- (2,1)
-		node[right]{\scriptsize number of Operations=500,000};
+		node[right]{\scriptsize number of operations=500\,000};
 	\draw[color=blue!90!black] (0,2) -- plot[mark=triangle*, mark options={fill=white}] (1,2) -- (2,2)
-		node[right]{\scriptsize number of Operations=1000,000};
+		node[right]{\scriptsize number of operations=1\,000\,000};
 	\end{scope}
@@
 
+\subsection{Com}
+
 \section{Conclusion and Perspective}

### 2013-06-24 trunk/network-science/paper.tex

@@
 
-\begin{center} \begin{tikzpicture}
-  \begin{axis}[ 
+\begin{center} \begin{tikzpicture} \begin{axis}[ 
+	thick,
+	xmax=5, ymax=1,
+	axis line style=very thick,
+	axis x line=bottom,
+	axis y line=left,
 	xlabel={$z$},
-    ylabel={evolving activity}
+	ylabel={evolving activity},
+        legend pos=outer north east
 ] 
@@
 	\addplot[color=red!50!black,samples=300,domain=-20:-0.001] {exp(ln(1000)*(1/x))}; 
-  \end{axis}
-\end{tikzpicture}
-
-\begin{color}{blue!50!black}blue
-\end{color}: $\mu=10$,
-\begin{color}{green!50!black}green
-\end{color}: $\mu=100$,
-\begin{color}{red!50!black}red
-\end{color}: $\mu=1000$\end{center}
+	\legend{$\mu=10$,$\mu=100$,$\mu=1000$};
+	\end{axis} \end{tikzpicture} 
+\end{center}
 
@@
 
-\subsection{Optimization and Parallelizability}
-
+\subsection{Optimization and Parallelization}
 In most cases, we only need to query the latest properties of the graph, i.e.,
-$t=\mathit{currentTime}$. And we observe that in Algorithm \ref{alg-con},
+$t=\mathit{currentTime}$. And we observe that in algorithm \ref{alg-con},
 \ref{alg-deg} and \ref{alg-act}, the binary search can be replace by simply find
@@
 
-Algorithm \ref{alg-cen} actually repeat the computation of the multiplication
-of a sparse matrix to a vector, which is highly parallelizable[?]. So in a large
-scale distributed system, we can perform very efficient analysis to an evolving
-graph, by our model.
+What algorithm \ref{alg-cen} do is only the multiplication of a sparse matrix
+to a vector, which is a classical problem called sparse matrix-vector
+multiplication (SpMV). This problem can be easily solve in both
+throughput-oriented and latency-oriented processors in
+parallel\cite{williams2009optimization, bell2008efficient,
+bell2009implementing, catalyurek1999hypergraph, zhuo2005sparse}.  This is a
+good news to us because nowadays parallel machine is much more common in
+company, research facilities and even with desktop computer, thanks to the
+emergence of GPGPU platforms such as CUDA and OpenCL.
+
 \section{Experiment}
@@
 Our data generation is base on real social networks provided by \cite{database1,
-database2}. Unfortunatly, those databases do not contain evolving history
+database2}. Unfortunately, those databases do not contain evolving history
 recorded data, so we simulate the evolving history by use the
@@
 We have implemented the algorithms using C++ language without compiler
-optimization, and all execution is done under a typical PC with Intel Core i3
-M380.
+optimization, and all execution is done under a typical PC with 
+Intel (R) Core (TM) i3 CPU M380  @ 2.53GHz, 2GB RAM.
 

### 2013-06-24 trunk/network-science/data/algo_c.cpp

@@ -1,0 +1,165 @@
+// For Network Science 2013
+// Algorithm Demo
+//
+// Feng Qiwei
+// 2013.06.24
+//
+#include <iostream>
+#include <cstring>
+#include <cstdlib>
+#include <cstdio>
+#include <vector>
+#include <cmath>
+using namespace std;
+
+const int MAXN=6010;
+const int MAXM=30010;
+
+const double c_eta=500.;
+const double c_mu=2;
+const double c_mup=8;
+const double c_alpha=0.8;
+const double c_beta=1.;
+
+int n;
+int cur_time;
+
+vector<int> edge[MAXN];
+double tmp_z[MAXN];
+double tmp_d[MAXN];
+
+int tmp_t[MAXN];
+
+inline void update_z(int x) {
+	tmp_z[x]=min(0., tmp_z[x]+cur_time-tmp_t[x]);
+	tmp_t[x]=cur_time;
+}
+
+void add_edge(int x, int y, double w) {
+	update_z(x);
+	update_z(y);
+	tmp_z[x]-=c_eta*w; tmp_d[x]+=w;
+	tmp_z[y]-=c_eta*w; tmp_d[y]+=w;
+	edge[x].push_back(y);
+	edge[y].push_back(x);
+}
+
+double x[MAXN], oldx[MAXN], a[MAXN];
+void cal_centrality() {
+	//printf("\ncal_centrality n=%d\n", n);
+	for(int i=1; i<=n; ++i) {
+		update_z(i);
+		if(fabs(tmp_z[i])<1E-5) a[i]=0;
+			else a[i]=pow(c_mu, c_mup/tmp_z[i]);
+	}
+	for(int cnt=1; ; ++cnt) {
+		memmove(oldx, x, sizeof(x));
+		for(int i=1; i<=n; ++i) {
+			x[i]=c_beta;
+			for(vector<int>::iterator it=edge[i].begin(); it!=edge[i].end(); ++it)
+				x[i]+=c_alpha*a[*it]*oldx[*it]/tmp_d[*it];
+		}
+		double delta=0;
+		for(int i=1; i<=n; ++i) delta=max(delta, fabs(x[i]-oldx[i]));
+		//if(cnt%1000==0) printf("  iterating.. cnt=%d delta=%.5lf\n", cnt, delta);
+		if(delta<1E-4) {
+			//printf("  finish at cnt=%d\n", cnt);
[…]

### 2013-06-24 network-science/paper.tex

@@
 are considered as vertices while relations are considered as edges. We suppose
-the evolution of a social network overtime only includes bidirectional new
+the evolution of a social network overtime includes new
 connections between existing or newly created nodes, and also assume the graph
@@
 to maintain the evolving large-scale network and the algorithm to compute our
-metrics in preferable time and space consumption, including historical queries.
-Finally, we use a simple model to generate data and apply our results to such
-experiments.\\[1.5em]
+metrics including historical queries in preferable time and space consumption.
+Finally, we use a simple model to generate evolving data from existing social
+network data and compare our metrics to static metrics. The results could imply
+that dynamic centrality is more capable in spotting hot social events.\\[1.5em]
 
@@
 \begin{equation}
-\mathbf{x}=\alpha DA^\bullet \mathbf{x} + \beta\mathbf{1},
+\mathbf{x}=\alpha DLA^\bullet \mathbf{x} + \beta\mathbf{1},
 \end{equation}
@@
 intensity of edges. And
-$D$ is a diagonal matrix that
+$D,L$ are diagonal matrices such that
 \begin{equation}
@@
 \mathit{Act}(G_t,v_i)&(i=j)
-\end{cases}
+\end{cases}\qquad
+L_{ij}=\begin{cases}
+0&(i\neq j)\\
+1/k^\bullet(G_t,v_i)&(i=j)
+\end{cases}.
 \end{equation}
@@
 \begin{equation}
-x_i(G_t,v_i)=\alpha\sum_jA^\bullet_{ij}
-\mathit{Act}(G_t,v_j)x_j(G_t,v_j)+\beta.
+x_i(G_t,v_i)=\alpha\sum_j\frac{A^\bullet_{ij}
+\mathit{Act}(G_t,v_j)x_j(G_t,v_j)}{k^\bullet(G_t,v_j)}+\beta.
 \end{equation}
@@
 \begin{equation}
-\mathbf{x}=\alpha DKA \mathbf{x} + \beta\mathbf{1},
+\mathbf{x}=\alpha DLA \mathbf{x} + \beta\mathbf{1},
 \end{equation}
@@
 \end{cases};\qquad
-K_{ij}=\begin{cases}
+L_{ij}=\begin{cases}
 0&(i\neq j)\\
-k_{\mathrm{out}}(G_t,v_i)&(i=j)
+1/k_{\mathrm{out}}(G_t,v_i)&(i=j)
 \end{cases}.
@@
 \State $a[i]\gets \Call{Query Activity}{t,v_i}$;
+\State $d[i]\gets \mathrm{size}(\mathit{edgeListReduced}[i])$;
 \State $\mathbf{x}[i]\gets \mathbf{x}_0[i]$;
@@
 \ForAll{$j\in\mathit{edgeListReduced}[i]$}
-\State $\mathbf{x'}[i]\gets \mathbf{x'}[i]+\alpha\cdot a[j]\cdot\mathbf{x}[j]$
+\State $\mathbf{x'}[i]\gets \mathbf{x'}[i]+\alpha\cdot
+a[j]\cdot\mathbf{x}[j]/d[j]$
 \EndFor\EndFor
@@
 
-Algorithm \ref{alg-cen} actually repeat the computation of the multiplication
-of a sparse matrix to a vector, which is highly parallelizable[?]. So in a large
-scale distributed system, we can perform very efficient analysis to an evolving
-graph, by our model.
+What the core part of algorithm \ref{alg-cen} does is only the multiplication
+of a sparse matrix to a vector, which is a classical problem called sparse
+matrix-vector multiplication (SpMV). This problem can be easily solve in both
+throughput-oriented and latency-oriented processors in
+parallel\cite{williams2009optimization, bell2008efficient,
+bell2009implementing, catalyurek1999hypergraph, zhuo2005sparse}.  This is a
+good news to us because nowadays parallel machine is much more common in
+companies, research facilities and even with desktop computers, thanks to the
+emergence of GPGPU platforms such as CUDA and OpenCL.
+
 \section{Experiment}
@@
 
-\subsection{Com}
+The time efficiency in terms of $|V|$ proves to have logarithm growth as
+expected.
+
+\subsection{Centrality Analysis}
+Here are some traces of both the evolving centrality and the classical PageRank
+centrality of specific nodes.
+
+We generates evolving network data in the same model discussed above, with
+$|V|\leq 6\,000$ and $|E|\leq 30\,000$. All iterations run for enough time,
+until the maximum magnitude of change in individual centralities (known as the
+$\infty$-norm of $\Delta\mathbf{x}$) is smaller than $10^{-4}$ by absolute value.
+We also calculate the static PageRank centrality in parallel, which do not have
+the activity metric as coefficients. All of our calculation assumes
+$\alpha=0.8$, and $\beta=1$.
+
+The centrality trace graph for an representative node, when $s$:
 
 \section{Conclusion and Perspective}
-% TODO
+So far, we have established and verified the framework for analysing an
+evolving social network. We defined two metrics for the networks, namely
+\textbf{evolving activity} and \textbf{evolving centrality}. The
+experiment showed that our model can successful compute both of the metrics in
+practical cases.
+
+By the final experiment, we can observe that the increase on magnitude of
+evolving centrality is similar to that of the static one. However, when the
+influence of a node stops increase so fast, our evolving centrality quickly
+pulls back, while the static centrality usually keeps a high value for long
+time. In many fields, the social concern are supposed to be sensitive to time
+, innovation and activeness, instead of imposing more attention to historical
+issues that are once very popular. Those fields such as web-page search
+engine[?], ranking of movie actors[?], seeking hot scholar topics, etc.
+By using evolving centrality, the increment of actions of a node and its
+closely related region will be more notable in increment of its ranking of
+influence, whereas the static centrality is more likely to trigger cascade on
+social preference[?] because people will have less chance to see and rate new
+information. The cascade may prevent high quality information from being
+popular, and even worse, hasten the monopolization in the commercial aspect.
+
+The evolving centrality is more sensitive to activities of the surroundings, so
+it usually changes more dramatically than static centrality which is more
+stable. Dynamic metrics provides new methods for network analysis.
 

### 2013-06-24 network-science/data/algo_c.cpp

@@ -14,10 +14,12 @@ using namespace std;
 
 const int MAXN=6010;
 const int MAXM=30010;
+const int INTERVAL=20;
+const int num=20;
 
-const double c_eta=500.;
+const double c_eta=1000.;
 const double c_mu=2;
-const double c_mup=8;
+const double c_mup=12;
 const double c_alpha=0.8;
 const double c_beta=1.;
 
@@ -89,11 +91,10 @@ void cal_pagerank() {
 	}
 }
 
-const int num=20;
 int id[num];
 
 int main(int argc, char *argv[]) {
-	FILE *inf=(argc<2 ? stdin : fopen(argv[1], "r"));
+	FILE *inf=fopen("CA-GrQc-output.txt", "r");
 	FILE *ouf1[num], *ouf2[num];
 	printf("$1\n");
 	for(int i=0; i<num; ++i) {
@@ -132,7 +133,7 @@ int main(int argc, char *argv[]) {
 			printf("t=%d\t%.5lf\t%.5lf\n",cur_time,x[k],px[k]);
 			//for(int i=1; i<=10; ++i) printf("%.4lf ", x[i]); printf("\n");
 			//for(int i=1; i<=10; ++i) printf("%.4lf ", px[i]); printf("\n");
-			next_time+=100;
+			next_time+=INTERVAL;
 		}
 	}
 	fclose(inf);
@@ -141,7 +142,7 @@ int main(int argc, char *argv[]) {
 		fclose(ouf2[i]);
 	}
 
-	system("cp exp.tex.head exp.tex");
+	system("copy exp.tex.head exp.tex");
 	FILE *f=fopen("exp.tex", "a");
 	for(int i=0; i<num; ++i) {
 fprintf(f, "\\begin{center} \\begin{tikzpicture}[y=.4cm, x=.5cm, font=\\sffamily]\n");
@@ -160,6 +161,8 @@ fprintf(f, "\\end{document}\n");
 	fclose(f);
 
 	system("pdflatex exp");
+        
+	system("del exp-g*.tex");
 	
 	return 0;
 }

### 2013-06-24 network-science/paper.tex

@@
 \begin{proof}
-	%TODO
+First we consider the base case, where we add edges to the vertex $v$ at time $t_i$ and $z=0$ initially.
+
+Denote the sum of weights of these new edges by $w(t_i)$, so $z$ decreases to $-\eta w(t_i)$ from 0.
+By the definition of $z$, we write $z$ as the function of $t$, which is $z(t)=t-t_i-\eta w(t_i)$.
+For simplify we choose $\mu=e$ here, it's similar to prove for other values of $\mu$.
+Now the integrity is as follows:
+
+\begin{equation}
+\begin{split}
+\int_{t_i}^{t_i+\eta w(t_i)} a(G_t,v) dt &= \int_{t_i}^{t_i+\eta w(t_i)} e^{\frac{1}{t-t_i-\eta w(t_i)}} dt \\
+&= \int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt.
+\end{split}
+\end{equation}
+
+Notice that $e^{1/t}<1(t<0)$, so it's easy for this direction
+\begin{equation}
+\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt< \eta w(t_i).
+\end{equation}
+
+Define $f(x)=\int_{-x}^{0} e^{1/t} dt - \frac{x}{10}$, from $f'(x)=e^{-1/x}-\frac{1}{10}$, at least we can see $f(x)$ increases when $x\ge 1$. So $f(x)\ge f(1)\approx 0.05>0$.
+
+Now we have the other direction: 
+\begin{equation}
+\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt>\frac{\eta w(t_i)}{10},
+\end{equation}
+as long as $\eta w(t_i)\ge 1$.
+
+Next we return to a general case.
+
+We show the theorem holds for each "phase", where we call the period of time when $z<0$ a "phase" and a "phase" starts and ends both with $z=0$.
+Consider a "phase" starting from $t_i$ and ending at $t_j$, some edges whose sum of weights is $w(t_k)$ are added to $v$ at time $t_k(i\le k\le j)$, so $z$ decreases from $z(t_k)$ to $z(t_k)-\eta w(t_k)$ sharply.
+
+One can verify that
+\begin{equation}
+\int_{t_i}^{t_j} a(G_t,v) dt< \eta \sum_{k=i}^j w(t_k),
+\end{equation}
+easily since we still have $\mu^{1/z(t)}<1$.
+
+As for the other direction, notice that at time $t_{k+1}$, there are two cases.
+One is that $z(t_{k+1})$ has increased equal or above $z(t_k)$, namely we can find some $t_k^*\in (t_k, t_{k+1})$, where $t_k^*$ is defined to satisfy that $z(t_k)=z(t_k^*)$ for all $k$.
+So we have
+\begin{equation}
+\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t)}} dt \ge \int_{t_k}^{t_k^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt.
+\end{equation}
+The other case is that $z(t_{k+1})$ is still less than $z(t_{k})$, in other words, we will find $t_k^*>t_{k+1}$.
+
+Now from
+\begin{equation}
+z(t)=
+\begin{cases}
+z(t_k)+t-t_k&  t\in (t_k, t_{k+1})\\
+z(t_{k+1})+t-t_{k+1}& t\in (t_{k+1}, t_{k+2})
+\end{cases}
+\end{equation}
+
+we have:
+\begin{equation}
+\begin{split}
+\int_{t_k}^{t_{k+2}} \mu^{\frac{1}{z(t)}} dt &\ge \int_{t_k}^{t_{k+1}^*} \mu^{\frac{1}{z(t)}} dt \\
+&= \int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}  dt + \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} -  \mu^{\frac{1}{z(t_{k+1})}} dt + (t_{k+1}^*-t_{k+1})\mu^{\frac{1}{z(t_{k+1})}}\\
+&\ge \int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt + \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} - \mu^{\frac{1}{z(t_{k+1})}}dt,
+\end{split}
+\end{equation}
+by an easy induction, one can split a "phase" into integrals in the form 
+\begin{equation}
+\int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt
+\end{equation}
+ Since $ \mu^{1/z}$ decreases as $z$ becomes larger, we can reduce it to the base case now.
+
+Above all, the theorem holds.
 \end{proof}

### 2013-06-24 trunk/network-science/paper.tex

@@
 to maintain the evolving large-scale network and the algorithm to compute our
-metrics in preferable time and space consumption, including historical queries.
-Finally, we use a simple model to generate data and apply our results to such
-experiments.\\[1.5em]
+metrics including historical queries in preferable time and space consumption.
+Finally, we use a simple model to generate evolving data from existing social
+network data and compare our metrics to static metrics. The results could imply
+that dynamic centrality is more capable in spotting hot social events.\\[1.5em]
 
 \noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
-vertex centrality, online algorithm.
+centrality, online algorithm.
 \end{abstract}
@@
 \begin{proof}
-	%TODO
+First we consider the base case, where we add edges to the vertex $v$ at time $t_i$ and $z=0$ initially.
+
+Denote the sum of weights of these new edges by $w(t_i)$, so $z$ decreases to $-\eta w(t_i)$ from 0.
+By the definition of $z$, we write $z$ as the function of $t$, which is $z(t)=t-t_i-\eta w(t_i)$.
+For simplify we choose $\mu=e$ here, it's similar to prove for other values of $\mu$.
+Now the integrity is as follows:
+
+\begin{equation}
+\begin{split}
+\int_{t_i}^{t_i+\eta w(t_i)} a(G_t,v) \mathrm{d}t &= \int_{t_i}^{t_i+\eta
+w(t_i)} e^{\frac{1}{t-t_i-\eta w(t_i)}} \mathrm{d}t \\
+&= \int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} \mathrm{d}t.
+\end{split}
+\end{equation}
+
+Notice that $e^{1/t}<1(t<0)$, so it's easy for this direction
+\begin{equation}
+\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} \mathrm{d}t< \eta w(t_i).
+\end{equation}
+
+Define $f(x)=\int_{-x}^{0} e^{1/t} \mathrm{d}t - \frac{x}{10}$, from $f'(x)=e^{-1/x}-\frac{1}{10}$, at least we can see $f(x)$ increases when $x\ge 1$. So $f(x)\ge f(1)\approx 0.05>0$.
+
+Now we have the other direction: 
+\begin{equation}
+\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} \mathrm{d}t>\frac{\eta w(t_i)}{10},
+\end{equation}
+as long as $\eta w(t_i)\ge 1$.
+
+Next we return to a general case.
+
+We show the theorem holds for each "phase", where we call the period of time when $z<0$ a "phase" and a "phase" starts and ends both with $z=0$.
+Consider a "phase" starting from $t_i$ and ending at $t_j$, some edges whose sum of weights is $w(t_k)$ are added to $v$ at time $t_k(i\le k\le j)$, so $z$ decreases from $z(t_k)$ to $z(t_k)-\eta w(t_k)$ sharply.
+
+One can verify that
+\begin{equation}
+\int_{t_i}^{t_j} a(G_t,v) \mathrm{d}t< \eta \sum_{k=i}^j w(t_k),
+\end{equation}
+easily since we still have $\mu^{1/z(t)}<1$.
+
+As for the other direction, notice that at time $t_{k+1}$, there are two cases.
+One is that $z(t_{k+1})$ has increased equal or above $z(t_k)$, namely we can find some $t_k^*\in (t_k, t_{k+1})$, where $t_k^*$ is defined to satisfy that $z(t_k)=z(t_k^*)$ for all $k$.
+So we have
+\begin{equation}
+\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t)}} \mathrm{d}t \ge \int_{t_k}^{t_k^*}
+\mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}\mathrm{d}t.
+\end{equation}
+The other case is that $z(t_{k+1})$ is still less than $z(t_{k})$, in other words, we will find $t_k^*>t_{k+1}$.
+
+Now from
+\begin{equation}
+z(t)=
+\begin{cases}
+z(t_k)+t-t_k&  t\in (t_k, t_{k+1})\\
+z(t_{k+1})+t-t_{k+1}& t\in (t_{k+1}, t_{k+2})
+\end{cases}
+\end{equation}
+
+we have:
+\begin{equation}
+\begin{split}
+&\int_{t_k}^{t_{k+2}} \mu^{\frac{1}{z(t)}} \mathrm{d}t\\
+\ge{}& \int_{t_k}^{t_{k+1}^*} \mu^{\frac{1}{z(t)}} \mathrm{d}t \\
+={}&\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}
+\mathrm{d}t+ \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}}\\& -
+\mu^{\frac{1}{z(t_{k+1})}} \mathrm{d}t + (t_{k+1}^*-t_{k+1})\mu^{\frac{1}{z(t_{k+1})}}\\
+\ge{}& \int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} -
+\mu^{\frac{1}{z(t_{k})}}\mathrm{d}t + \int_{t_{k+1}}^{t_{k+1}^*}
+\mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} - \mu^{\frac{1}{z(t_{k+1})}}\mathrm{d}t,
+\end{split}
+\end{equation}
+by an easy induction, one can split a "phase" into integrals in the form 
+\begin{equation}
+\int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}\mathrm{d}t
+\end{equation}
+ Since $ \mu^{1/z}$ decreases as $z$ becomes larger, we can reduce it to the base case now.
+
+Above all, the theorem holds.
 \end{proof}
@@
 
-What algorithm \ref{alg-cen} do is only the multiplication of a sparse matrix
-to a vector, which is a classical problem called sparse matrix-vector
-multiplication (SpMV). This problem can be easily solve in both
+What the core part of algorithm \ref{alg-cen} does is only the multiplication
+of a sparse matrix to a vector, which is a classical problem called sparse
+matrix-vector multiplication (SpMV). This problem can be easily solve in both
 throughput-oriented and latency-oriented processors in
@@
 good news to us because nowadays parallel machine is much more common in
-company, research facilities and even with desktop computer, thanks to the
+companies, research facilities and even with desktop computers, thanks to the
 emergence of GPGPU platforms such as CUDA and OpenCL.
@@
 authentic graph as the final state of the tested dynamic graph.
-We give a random permutation to the edges, in a way such that there will always
-be just one component -- known as the giant component. Because the final state
+We give a random permutation to the edges, in a way such that:
+\begin{itemize}
+\item There will always
+be just one component -- known as the giant component. We never add an edge out
+of the giant component, so the evolving of the network seems to have increasing
+vertices joining to the network.
+\item The time delay of two adjacent new edges is inversely proportional to the
+size of the giant component. So the average activity of any indivitual node do
+not change tremendously.
+\end{itemize}
+Because the final state
 is from real world data, it is ensured 
 the evolving graph generated by our model will satisfy all the property that we
-discussed in section 2.2. In addition, Kumar introduced another way to generate
-artificial data of evolving social networks\cite{kumar2010structure}.
+discussed in section 2.2. In addition, Kumar introduced how to generate
+an artificial evolving social networks\cite{kumar2010structure}.
 
@@
 
-\subsection{Com}
+The time efficiency in terms of $|V|$ proves to have logarithm growth as
+expected.
+
+\subsection{Centrality Analysis}
+Here are some traces of both the evolving centrality and the classical PageRank
+centrality of specific nodes.
+
+We generates evolving network data in the same model discussed above, with
+$|V|\leq 6\,000$ and $|E|\leq 30\,000$. All iterations run for enough time,
+until the maximum magnitude of change in individual centralities (known as the
+$\infty$-norm of $\Delta\mathbf{x}$) is smaller than $10^{-4}$ by absolute value.
+We also calculate the static PageRank centrality in parallel, which do not have
+the activity metric as coefficients. All of our calculation assumes
+$\alpha=0.8$, and $\beta=1$.
+
+The centrality trace graph for some representative node, when $\mu=4096$ and
+$\eta=1000$:
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 11);
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
+	Centrality};
+	\foreach \x in {1,2,...,20}
+	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+		\foreach \y in {1,2,...,11}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	\draw[color=red!70!black,line width=1pt] plot file {exp-g3-1};
+	\draw[color=blue!70!black] plot file {exp-g3-2};
+	\begin{scope}[shift={(2,8)}]
+	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
+		node[right]{\scriptsize evolving centrality};
+	\draw[color=blue!50!black] (0,1) -- (2,1)
+		node[right]{\scriptsize static centrality};
+	\end{scope}
+\end{tikzpicture} \end{center}
+
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 11);
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
+	Centrality};
+	\foreach \x in {1,2,...,20}
+	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+		\foreach \y in {1,2,...,11}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	\draw[color=red!70!black,line width=1pt] plot file {exp-g9-1};
+	\draw[color=blue!70!black] plot file {exp-g9-2};
+	\begin{scope}[shift={(2,8)}]
+	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
+		node[right]{\scriptsize evolving centrality};
+	\draw[color=blue!50!black] (0,1) -- (2,1)
+		node[right]{\scriptsize static centrality};
+	\end{scope}
+\end{tikzpicture} \end{center}
+
+The centrality trace graph for some representative node, when $\mu=2^{20}$ and
+$\eta=2000$:
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 11);
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
+	Centrality};
+	\foreach \x in {1,2,...,20}
+	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+		\foreach \y in {1,2,...,11}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	\draw[color=red!70!black,line width=1pt] plot file {exp-g8-1};
+	\draw[color=blue!70!black] plot file {exp-g8-2};
+	\begin{scope}[shift={(2,8)}]
+	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
+		node[right]{\scriptsize evolving centrality};
+	\draw[color=blue!50!black] (0,1) -- (2,1)
+		node[right]{\scriptsize static centrality};
+	\end{scope}
+\end{tikzpicture} \end{center}
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 11);
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
+	Centrality};
+	\foreach \x in {1,2,...,20}
+	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+		\foreach \y in {1,2,...,11}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	\draw[color=red!70!black,line width=1pt] plot file {exp-g11-1};
+	\draw[color=blue!70!black] plot file {exp-g11-2};
+	\begin{scope}[shift={(2,8)}]
+	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
+		node[right]{\scriptsize evolving centrality};
+	\draw[color=blue!50!black] (0,1) -- (2,1)
+		node[right]{\scriptsize static centrality};
+	\end{scope}
+\end{tikzpicture} \end{center}
 
 \section{Conclusion and Perspective}
-% TODO
+So far, we have established and verified the framework for analysing an
+evolving social network. We defined two metrics for the networks, namely
+\textbf{evolving activity} and \textbf{evolving centrality}. The
+experiment showed that our model can successful compute both of the metrics in
+practical cases.
+
+By the final experiment, we can observe that the increase on magnitude of
+evolving centrality is similar to that of the static one. However, when the
+influence of a node stops increase so fast, our evolving centrality quickly
+pulls back, while the static centrality usually keeps a high value for long
+time. In many fields, the social concern are supposed to be sensitive to time
+, innovation and activeness, instead of imposing more attention to historical
+issues that are once very popular. Those fields such as web-page search
+engine[?], ranking of movie actors[?], seeking hot scholar topics, etc.
+By using evolving centrality, the increment of actions of a node and its
+closely related region will be more notable in increment of its ranking of
+influence, whereas the static centrality is more likely to trigger cascade on
+social preference[?] because people will have less chance to see and rate new
+information. The cascade may prevent high quality information from being
+popular, and even worse, hasten the monopolization in the commercial aspect.
+
+The evolving centrality is more sensitive to activities of the surroundings, so
+it usually changes more dramatically than static centrality which is more
+stable. Dynamic metrics provides new methods for network analysis.
 

### 2013-06-24 trunk/network-science/data/algo_c.cpp

@@ -17,9 +17,9 @@ const int MAXM=30010;
 const int INTERVAL=20;
 const int num=20;
 
-const double c_eta=1000.;
+const double c_eta=2000.;
 const double c_mu=2;
-const double c_mup=12;
+const double c_mup=20;
 const double c_alpha=0.8;
 const double c_beta=1.;
 
@@ -162,7 +162,5 @@ fprintf(f, "\\end{document}\n");
 
 	system("pdflatex exp");
         
-	system("del exp-g*.tex");
-	
 	return 0;
 }

### 2013-06-24 network-science/paper.tex

@@
 \noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
-vertex centrality, online algorithm.
+centrality, online algorithm.
 \end{abstract}
@@
 \begin{itemize}
-\item \textbf{(normalization)}:
+\item \textbf{normalization}:
 
@@
 
-\item \textbf{(initialization)}:
+\item \textbf{initialization}:
 
@@
 \begin{split}
-\int_{t_i}^{t_i+\eta w(t_i)} a(G_t,v) dt &= \int_{t_i}^{t_i+\eta w(t_i)} e^{\frac{1}{t-t_i-\eta w(t_i)}} dt \\
-&= \int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt.
+\int_{t_i}^{t_i+\eta w(t_i)} a(G_t,v) \mathrm{d}t &= \int_{t_i}^{t_i+\eta
+w(t_i)} e^{\frac{1}{t-t_i-\eta w(t_i)}} \mathrm{d}t \\
+&= \int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} \mathrm{d}t.
 \end{split}
@@
 \begin{equation}
-\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt< \eta w(t_i).
-\end{equation}
-
-Define $f(x)=\int_{-x}^{0} e^{1/t} dt - \frac{x}{10}$, from $f'(x)=e^{-1/x}-\frac{1}{10}$, at least we can see $f(x)$ increases when $x\ge 1$. So $f(x)\ge f(1)\approx 0.05>0$.
+\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} \mathrm{d}t< \eta w(t_i).
+\end{equation}
+
+Define $f(x)=\int_{-x}^{0} e^{1/t} \mathrm{d}t - \frac{x}{10}$, from $f'(x)=e^{-1/x}-\frac{1}{10}$, at least we can see $f(x)$ increases when $x\ge 1$. So $f(x)\ge f(1)\approx 0.05>0$.
 
@@
 \begin{equation}
-\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} dt>\frac{\eta w(t_i)}{10},
+\int_{-\eta w(t_i)}^{0} e^{\frac{1}{t}} \mathrm{d}t>\frac{\eta w(t_i)}{10},
 \end{equation}
@@
 \begin{equation}
-\int_{t_i}^{t_j} a(G_t,v) dt< \eta \sum_{k=i}^j w(t_k),
+\int_{t_i}^{t_j} a(G_t,v) \mathrm{d}t< \eta \sum_{k=i}^j w(t_k),
 \end{equation}
@@
 \begin{equation}
-\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t)}} dt \ge \int_{t_k}^{t_k^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt.
+\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t)}} \mathrm{d}t \ge \int_{t_k}^{t_k^*}
+\mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}\mathrm{d}t.
 \end{equation}
@@
 \begin{split}
-\int_{t_k}^{t_{k+2}} \mu^{\frac{1}{z(t)}} dt &\ge \int_{t_k}^{t_{k+1}^*} \mu^{\frac{1}{z(t)}} dt \\
-&= \int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}  dt + \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} -  \mu^{\frac{1}{z(t_{k+1})}} dt + (t_{k+1}^*-t_{k+1})\mu^{\frac{1}{z(t_{k+1})}}\\
-&\ge \int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt + \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} - \mu^{\frac{1}{z(t_{k+1})}}dt,
+&\int_{t_k}^{t_{k+2}} \mu^{\frac{1}{z(t)}} \mathrm{d}t\\
+\ge{}& \int_{t_k}^{t_{k+1}^*} \mu^{\frac{1}{z(t)}} \mathrm{d}t \\
+={}&\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}
+\mathrm{d}t+ \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}}\\& -
+\mu^{\frac{1}{z(t_{k+1})}} \mathrm{d}t + (t_{k+1}^*-t_{k+1})\mu^{\frac{1}{z(t_{k+1})}}\\
+\ge{}& \int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} -
+\mu^{\frac{1}{z(t_{k})}}\mathrm{d}t + \int_{t_{k+1}}^{t_{k+1}^*}
+\mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} - \mu^{\frac{1}{z(t_{k+1})}}\mathrm{d}t,
 \end{split}
@@
 \begin{equation}
-\int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}dt
+\int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}\mathrm{d}t
 \end{equation}
@@
 \EndIf
-\State $p\gets \Call{FindRoot}{i,\mathit{currentTime}}$;
-\State $q\gets \Call{FindRoot}{j,\mathit{currentTime}}$;
+\State $p\gets \Call{Find Root}{i,\mathit{currentTime}}$;
+\State $q\gets \Call{Find Root}{j,\mathit{currentTime}}$;
 \If{$p\neq q$}
@@
 
-The centrality trace graph for an representative node, when $s$:
+The centrality trace graph for some representative node, when $\mu=4096$ and
+$\eta=1000$:
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 11);
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
+	Centrality};
+	\foreach \x in {1,2,...,20}
+	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+		\foreach \y in {1,2,...,11}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	\draw[color=red!70!black,line width=1pt] plot file {exp-g3-1};
+	\draw[color=blue!70!black] plot file {exp-g3-2};
+	\begin{scope}[shift={(2,8)}]
+	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
+		node[right]{\scriptsize evolving centrality};
+	\draw[color=blue!50!black] (0,1) -- (2,1)
+		node[right]{\scriptsize static centrality};
+	\end{scope}
+\end{tikzpicture} \end{center}
+
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 11);
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
+	Centrality};
+	\foreach \x in {1,2,...,20}
+	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+		\foreach \y in {1,2,...,11}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	\draw[color=red!70!black,line width=1pt] plot file {exp-g9-1};
+	\draw[color=blue!70!black] plot file {exp-g9-2};
+	\begin{scope}[shift={(2,8)}]
+	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
+		node[right]{\scriptsize evolving centrality};
+	\draw[color=blue!50!black] (0,1) -- (2,1)
+		node[right]{\scriptsize static centrality};
+	\end{scope}
+\end{tikzpicture} \end{center}
+
+The centrality trace graph for some representative node, when $\mu=2^{20}$ and
+$\eta=2000$:
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 11);
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
+	Centrality};
+	\foreach \x in {1,2,...,20}
+	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+		\foreach \y in {1,2,...,11}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	\draw[color=red!70!black,line width=1pt] plot file {exp-g8-1};
+	\draw[color=blue!70!black] plot file {exp-g8-2};
+	\begin{scope}[shift={(2,8)}]
+	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
+		node[right]{\scriptsize evolving centrality};
+	\draw[color=blue!50!black] (0,1) -- (2,1)
+		node[right]{\scriptsize static centrality};
+	\end{scope}
+\end{tikzpicture} \end{center}
+\begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
+	\draw (0,0) -- coordinate (x axis mid) (21, 0);
+	\draw (0,0) -- coordinate (y axis mid) (0, 11);
+	\node[below=0.5cm] at (x axis mid) {\scriptsize Time ($\times10^3$)};
+	\node[rotate=90, left=0.8cm] at (0, 10) {\scriptsize Magnitude of
+	Centrality};
+	\foreach \x in {1,2,...,20}
+	\draw (\x,1pt) -- (\x,-3pt) node[anchor=north] {\scriptsize \x};
+		\foreach \y in {1,2,...,11}
+		\draw (1pt,\y) -- (-3pt,\y) node[anchor=east] {\scriptsize \y};
+	\draw[color=red!70!black,line width=1pt] plot file {exp-g11-1};
+	\draw[color=blue!70!black] plot file {exp-g11-2};
+	\begin{scope}[shift={(2,8)}]
+	\draw[color=red!70!black,line width=1pt] (0,0) -- (2,0)
+		node[right]{\scriptsize evolving centrality};
+	\draw[color=blue!50!black] (0,1) -- (2,1)
+		node[right]{\scriptsize static centrality};
+	\end{scope}
+\end{tikzpicture} \end{center}
 

### 2013-06-24 trunk/network-science/paper.tex

@@
 	\normalsize
-	June 24, 2013\\[3em]
 \end{center} \par %>>>
@@
 the computation of other metrics will no longer need the time information
-directly, but referring to the activity instead.
+directly, but refer to the activity instead.
 
@@
 analysis algorithms that used some kind of graph centralities. However, most
-social networks change over time, and even more unfortunately, some of the
+social networks change over time, and even more unfortunately, many of the
 networks are large-scaled, which could make the analysis become hard and

### 2013-06-24 network-science/paper.tex

@@
 	thick,
-	xmax=5, ymax=1,
+	width=0.6\textwidth,
+	x=1cm/4,
+	xmax=10, ymax=1,
 	axis line style=very thick,
@@
 	ylabel={evolving activity},
-        legend pos=outer north east
 ] 
-	\addplot[color=blue!50!black,samples=300,domain=-20:-0.001] {exp(ln(10)*(1/x))}; 
-	\addplot[color=green!50!black,samples=300,domain=-20:-0.001] {exp(ln(100)*(1/x))}; 
-	\addplot[color=red!50!black,samples=300,domain=-20:-0.001] {exp(ln(1000)*(1/x))}; 
+	\addplot[color=blue!50!black,samples=300,domain=-40:-0.001] {exp(ln(10)*(1/x))}; 
+	\addplot[color=green!50!black,samples=300,domain=-40:-0.001] {exp(ln(100)*(1/x))}; 
+	\addplot[color=red!50!black,samples=300,domain=-40:-0.001] {exp(ln(1000)*(1/x))}; 
 	\legend{$\mu=10$,$\mu=100$,$\mu=1000$};

### 2013-06-24 trunk/network-science/paper.tex

@@
 \begin{abstract}
-We address the dynamic properties of typical social networks, in which people
-are considered as vertices while relations are considered as edges. We suppose
-the evolution of a social network overtime includes new
-connections between existing or newly created nodes, and also assume the graph
-will evolve as a typical social network. We study the activity and centrality
+We address the dynamic properties of typical social networks. We suppose
+the evolution over time only includes new connections between existing or newly
+created nodes. We study the activity and centrality
 metrics for nodes in such graphs by regulating a series of reasonable
 properties the metrics should satisfy. We then formally define our metrics and
-give their mathematical analysis. We have developed a practical based framework
+give their mathematical analysis. We have developed a practice based framework
 to maintain the evolving large-scale network and the algorithm to compute our
@@
 network data and compare our metrics to static metrics. The results could imply
-that dynamic centrality is more capable in spotting hot social events.\\[1.5em]
-
+that dynamic centrality is more capable in spotting hot social events.
+
+\smallskip
 \noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,

### 2013-06-24 trunk/network-science/paper.tex

@@
 \begin{abstract}
-We address the dynamic properties of typical social networks. We suppose
-the evolution over time only includes new connections between existing or newly
-created nodes. We study the activity and centrality
-metrics for nodes in such graphs by regulating a series of reasonable
-properties the metrics should satisfy. We then formally define our metrics and
-give their mathematical analysis. We have developed a practice based framework
-to maintain the evolving large-scale network and the algorithm to compute our
-metrics including historical queries in preferable time and space consumption.
-Finally, we use a simple model to generate evolving data from existing social
-network data and compare our metrics to static metrics. The results could imply
+This paper addresses the dynamic properties of typical social networks. We
+suppose the evolution over time only includes creating new edges but no
+deletion. The paper studies the activity and centrality metrics for nodes in
+such graphs by regulating a series of reasonable properties the metrics should
+satisfy. Then formal definition is given for our metrics and
+also their mathematical analysis. We have developed a practice based framework
+to maintain the evolving large-scale network and an algorithm to compute our
+metrics including historical queries in acceptable time and space consumption.
+Finally, we use a simple model to generate evolving graph from existing social
+network data and compare our metric to the static one. The results could imply
 that dynamic centrality is more capable in spotting hot social events.

### 2013-06-24 network-science/paper.tex

@@
 \begin{abstract}
-We address the dynamic properties of typical social networks, in which people
-are considered as vertices while relations are considered as edges. We suppose
-the evolution of a social network overtime includes new
-connections between existing or newly created nodes, and also assume the graph
-will evolve as a typical social network. We study the activity and centrality
-metrics for nodes in such graphs by regulating a series of reasonable
-properties the metrics should satisfy. We then formally define our metrics and
-give their mathematical analysis. We have developed a practical based framework
-to maintain the evolving large-scale network and the algorithm to compute our
-metrics including historical queries in preferable time and space consumption.
-Finally, we use a simple model to generate evolving data from existing social
-network data and compare our metrics to static metrics. The results could imply
-that dynamic centrality is more capable in spotting hot social events.\\[1.5em]
-
+This article addresses the dynamic properties of typical social networks. By
+supposing that the evolution over time only includes creating new edges but no
+deletion, we studies the activity and centrality metrics for nodes in
+such graphs by regulating a series of reasonable properties the metrics should
+satisfy. Then formal definitions are given to our metrics and
+their mathematical analysis are put. We have developed a practice based framework
+to maintain the evolving large-scale network and an algorithm to compute our
+metrics including historical queries in acceptable time and space consumption.
+Finally, we use a simple model to generate evolving graph from existing social
+network data and compare our metric to the static one. The results could imply
+that dynamic centrality is more capable in spotting hot social events.
+
+\smallskip
 \noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,

### 2013-06-24 trunk/network-science/paper.tex

@@
 \begin{abstract}
-This paper addresses the dynamic properties of typical social networks. We
-suppose the evolution over time only includes creating new edges but no
-deletion. The paper studies the activity and centrality metrics for nodes in
+This article addresses the dynamic properties of typical social networks. By
+supposing that the evolution over time only includes creating new edges but no
+deletion, we studies the activity and centrality metrics for nodes in
 such graphs by regulating a series of reasonable properties the metrics should
-satisfy. Then formal definition is given for our metrics and
-also their mathematical analysis. We have developed a practice based framework
+satisfy. Then formal definitions are given to our metrics and
+their mathematical analysis are put. We have developed a practice based framework
 to maintain the evolving large-scale network and an algorithm to compute our
@@
 computer science, allowing helpful analysis of large-scaled social behavior
-and tendency. In this paper, we will deal with more information of social
-networks, the time dimension, and make a similar study to the social behaviors.
-We build metrics for evolving social networks and design an algorithm to
-calculate them. We compare how different the outcome by our method would be
-against the classical analysis with un-timestamped data mining.
+and tendency. In this article, we are able to deal with more information, the
+time dimension, of social networks, and make a similar study to the social
+behaviors.  We build metrics for evolving social networks and design an
+algorithm to calculate them. We compare out results with the classical analysis
+which works under un-timestamped data.
 

### 2013-06-24 network-science/paper.tex

@@
 Finally, we use a simple model to generate evolving graph from existing social
-network data and compare our metric to the static one. The results could imply
+network data and compare our metric to the static one. The results imply
 that dynamic centrality is more capable in spotting hot social events.
@@
 Networks contain too much information to be easily observed by people without
-any abstraction. To study a network, people exploited the basic form of
-quantification to concentrate on specific features of the whole graph, or an
-individual vertex. Our work is to promote this method to the dynamic graphs. We
+any abstraction. To study a network, people exploit the basic form of
+quantification to concentrate on specific features of the whole graph or an
+individual vertex. Our work is to extend this method to the dynamic graphs. We
 basically design new dynamic metrics according to existing successful static
@@
 networks are large-scaled, which could make the analysis become hard and
-costly, hence limit the scale of meaningful data mining. Moreover, the time
+costly, hence limiting the scale of meaningful data mining. Moreover, the time
 effect can also become a factor of the centrality, that is, the same graph with
@@
 tremendous information and also the possibility of accumulative computation
-which could be helpful in enhancement the speed of answering consistent
+which could be helpful in enhancing the speed of answering consistent
 querying.
@@
 In section 3 we will concentrate on centrality and activity in evolving social
-network. We will define what centrality or activity is good, and we will design
-some instance of those metrics by the standard we set. In section 4, we will
+network. We will define what kind of activity is good, and we will design
+an instance of those metrics by the standard we set. In section 4, we will
 give the algorithms to compute our designed centrality and activity from the
@@
 Graph theory is very successful on storing and solving various problems on
-static networks, we have sophisticated methodology on finding the shortest
+static networks. We have sophisticated method on finding the shortest
 paths, get a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.

### 2013-06-24 network-science/paper.tex

@@
 PageRank algorithm\cite{page1999pagerank}, and there are many useful network
-analysis algorithms that used some kind of graph centralities. However, most
+analysis algorithms that used some forms of graph centralities. However, most
 social networks change over time, and even more unfortunately, many of the
@@
 static networks. We have sophisticated method on finding the shortest
-paths, get a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
+paths, getting a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
 And we also have a well-established theoretical system to study problems that
-do not seems to have perfect solutions. However, dynamic online queries can be
+do not seems to have perfect solutions. However, dynamic queries can be
 very hard for general graphs. Best known solutions for many dynamic basic graph
 problems still remain unsatisfiable for general demands. So to design metrics
-for an general evolving network is a very challenging and open problem. We
-concentrate on the popular studied social networks and try to create meaningful
-and available approaches of operation on such networks.
-
-In section 2 we will discuss the known properties of a typical social network,
+for a general evolving network is a challenging and open problem. We
+concentrate on the popularly studied social networks and try to create meaningful
+and available approaches of operations on such networks.
+
+In section 2, we will discuss the known properties of a typical social network,
 which could be helpful for our algorithm designs. In section 4, we will
 establish a framework of data structure and algorithms to solve series of
-possible queries including computing the metrics about a evolving social
+possible queries including computing the metrics about an evolving social
 network.
@@
 \begin{definition}
-A \textbf{pure growing model} for an evolving graph $EG$ is defined in pair:
-\begin{equation}
-EG=(V,E),
+A \textbf{pure growing model} for an evolving graph $G$ is defined in pair:
+\begin{equation}
+G=(V,E),
 \end{equation}
@@
 \begin{definition}
-$EG^*=(V,E^*)$ where $E\subseteq E^*$. We assume the edges are added to the
+$G^*=(V,E^*)$ where $E\subseteq E^*$. We assume the edges are added to the
 model by correct time order, so

### 2013-06-24 network-science/paper.tex

@@
 In some related research on evolving graphs, the time dimension is represented
-by constructing a sequence of graphs $EG=\{G_t(V_t,E_t)\}$ on different time
+by constructing a sequence of graphs $\{G_t(V_t,E_t)\}$ on different time
 spots $t$. This model is highly expressive and universal in mathematical

### 2013-06-24 network-science/paper.tex

@@
 possible loyalty to the real data generation. We build the \textbf{pure growing
-model}, which care about the new connection forming among vertices, neglecting
+model}, which cares about the new connection forming among vertices, neglecting
 the anti-growing operations such as edge deletions. We assume the existence of
 every connection will contribute to the metrics, even if the connection is
-later erased, so we do not delete edges or nodes in our model, instead we could
+later erased. So we do not delete edges or nodes in our model, instead we could
 add an decay mechanism to reduce the affect of old formed links, which will be
-discussed in the next section. Note that in pure growing model, we will assign
-every edge a timestamp, namely when the edge is created. And thus there could
-be more than one edges between a pair of nodes, with different timestamp.
+discussed in the next section. In pure growing model, we will assign every edge
+a timestamp, namely what time the edge is created. Thus there could be more
+than one edges between a pair of nodes with different timestamps.
 

### 2013-06-24 trunk/network-science/paper.tex

@@
 PageRank algorithm\cite{page1999pagerank}, and there are many useful network
-analysis algorithms that used some kind of graph centralities. However, most
+analysis algorithms that used some forms of graph centralities. However, most
 social networks change over time, and even more unfortunately, many of the
 networks are large-scaled, which could make the analysis become hard and
-costly, hence limit the scale of meaningful data mining. Moreover, the time
+costly, hence limiting the scale of meaningful data mining. Moreover, the time
 effect can also become a factor of the centrality, that is, the same graph with
@@
 Graph theory is very successful on storing and solving various problems on
-static networks, we have sophisticated methodology on finding the shortest
-paths, get a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
+static networks. We have sophisticated method on finding the shortest
+paths, getting a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
 And we also have a well-established theoretical system to study problems that
-do not seems to have perfect solutions. However, dynamic online queries can be
+do not seems to have perfect solutions. However, dynamic queries can be
 very hard for general graphs. Best known solutions for many dynamic basic graph
 problems still remain unsatisfiable for general demands. So to design metrics
-for an general evolving network is a very challenging and open problem. We
-concentrate on the popular studied social networks and try to create meaningful
-and available approaches of operation on such networks.
-
-In section 2 we will discuss the known properties of a typical social network,
+for a general evolving network is a challenging and open problem. We
+concentrate on the popularly studied social networks and try to create meaningful
+and available approaches of operations on such networks.
+
+In section 2, we will discuss the known properties of a typical social network,
 which could be helpful for our algorithm designs. In section 4, we will
 establish a framework of data structure and algorithms to solve series of
-possible queries including computing the metrics about a evolving social
+possible queries including computing the metrics about an evolving social
 network.
@@
 \begin{definition}
-A \textbf{pure growing model} for an evolving graph $EG$ is defined in pair:
-\begin{equation}
-EG=(V,E),
-\end{equation}
-where $V$ is the set of all nodes in the network, and $E$ is the set of edges,
-formally an edge $e\in E$ for $e=(u,v,t)$, where $u,v\in V$ are the two end
-points of the edge, $u<v$ (to ensure bidirectional), $t\in \mathbb{N}$. The $t$
+A \textbf{pure growing model} for an evolving graph $G$ is defined in pair:
+\begin{equation}
+G=(V,E),
+\end{equation}
+where $V$ is the set of all nodes in the network, and $E$ is the set of edges.
+For every $(u,v,t)\in E$, where $u,v\in V$ are the two end
+points of the edge, ($u<v$ in case of bidirectional graph),
+$t\in \mathbb{N}$. The $t$
 component stored the forming time of the graph. As for weighted evolving graph

### 2013-06-24 network-science/paper.tex

@@
 \end{equation}
-where $V$ is the set of all nodes in the network, and $E$ is the set of edges,
-formally an edge $e\in E$ for $e=(u,v,t)$, where $u,v\in V$ are the two end
-points of the edge, $u<v$ (to ensure bidirectional), $t\in \mathbb{N}$. The $t$
-component stored the forming time of the graph. As for weighted evolving graph
+where $V$ is the set of all nodes in the network, and $E$ is the set of edges.
+For every $(u,v,t)\in E$, where $u,v\in V$ are the two end
+points of the edge, ($u<v$ in case of bidirectional graph),
+$t\in \mathbb{N}$. The $t$
+component stores the forming time of the edge. As for weighted evolving graph
 model, we modifies $e\in E$ for $e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands
@@
 \begin{definition}
-$G^*=(V,E^*)$ where $E\subseteq E^*$. We assume the edges are added to the
-model by correct time order, so
+$G^*(V,E^*)$ is the updated version of $G$, where $E\subseteq E^*$. We assume
+the edges are added to the
+model by correct time order, namely
 \begin{equation}
@@
 0&(i=j)\\
-\sum_{e\in E_t\text{ and }e=(i,j,t,w)}w &(i<j)\\
+\sum_{(i,j,t',w)\in E_t}w &(i<j)\\
 a_{ji}&(i>j)
@@
 \begin{equation}
-k(G_t,v)=\sum_{\mathclap{e\in E_t, e=(x,y,t,w)}}w(1-\delta(x,v)\delta(y,v)),
+k(G_t,v)=\sum_{\mathclap{(x,y,t',w)\in E_t}}(1-\delta(x,v)\delta(y,v))w,
 \end{equation}

### 2013-06-24 network-science/paper.tex

@@
 a_{ji}&(i>j)
+\end{cases}.
+\end{equation}
+Or, in case of directional graph,
+\begin{equation}
+a_{ij}=\begin{cases}
+0&(i=j)\\
+\sum_{(i,j,t',w)\in E_t}w &(i\neq j)
 \end{cases}
@@
 where $\left|E^\bullet\right|/\left|V\right|$ only depends on the structure of
-the network at a time spot. In many available online datasets, such as [?]%TODO
+the network at a time spot. In many available online datasets,
 we can assume $\left<k^\bullet\right>$ is limited by a constant $K$, typically
@@
 
-The clustering coefficient[?], namely
+The clustering coefficient\cite{newman2010networks}, namely
 \begin{equation}
@@
 If a vertex $v$ performs an interaction $(v,u)$ at time $t$, i.e., a new edge
-is added to $G_t$, and suppose the interaction is the only change to the graph
+is added to $G_t$, and the interaction is the only change to the graph
 at time $t$, then the activity of $v$ should be greater than if the edge is not

### 2013-06-24 trunk/network-science/paper.tex

@@
 $t\in \mathbb{N}$. The $t$
-component stored the forming time of the graph. As for weighted evolving graph
+component stores the forming time of the edge. As for weighted evolving graph
 model, we modifies $e\in E$ for $e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands
@@
 0&(i=j)\\
-\sum_{e\in E_t\text{ and }e=(i,j,t,w)}w &(i<j)\\
+\sum_{(i,j,t',w)\in E_t}w &(i<j)\\
 a_{ji}&(i>j)
+\end{cases}.
+\end{equation}
+Or, in case of directional graph,
+\begin{equation}
+a_{ij}=\begin{cases}
+0&(i=j)\\
+\sum_{(i,j,t',w)\in E_t}w &(i\neq j)
 \end{cases}
@@
 \begin{equation}
-\int_{-\infty}^{\infty} \frac{\mathit{Act}(G_t,v)}{k(G_T,v)}\mathrm{d}t\in\left[\frac{1}{M},M\right].
+\frac{\int_{-\infty}^{\infty} \mathit{Act}(G_t,v)\mathrm{d}t}{k(G_T,v)}\in\left[\frac{1}{M},M\right].
 \label{eq-int}

### 2013-06-24 trunk/network-science/paper.tex

@@
 
-Then we move on the dynamic centrality, by expanding the often used model
-for static network named Katz centrality[?], which is actually a generalized
-version of eigenvalue centrality[?] which estimate the influence of a node in
-social networks by counting the total number of walks between a pair of
-node[?]. We try to combine the activity and the clasical centrality metric and
+Then we move on the dynamic centrality, by extending the often used model
+for static network named Katz centrality\cite{katz1953new}, which is actually
+a generalized version of eigenvalue centrality which estimate the influence
+of a node in social networks by counting the total number of walks between a pair of
+node. We try to combine the activity and the clasical centrality metric and
 expect to define a new centrality model that is mode sensitive to immediate
@@
 	\addplot[color=blue!50!black,samples=300,domain=-40:-0.001] {exp(ln(10)*(1/x))}; 
-	\addplot[color=green!50!black,samples=300,domain=-40:-0.001] {exp(ln(100)*(1/x))}; 
-	\addplot[color=red!50!black,samples=300,domain=-40:-0.001] {exp(ln(1000)*(1/x))}; 
-	\legend{$\mu=10$,$\mu=100$,$\mu=1000$};
+	\addplot[color=green!50!black,samples=300,domain=-40:-0.001] {exp(ln(1000)*(1/x))}; 
+	\addplot[color=red!50!black,samples=300,domain=-40:-0.001]
+	{exp(ln(100000)*(1/x))}; 
+	\legend{$\mu=10$,$\mu=10^3$,$\mu=10^6$};
 	\end{axis} \end{tikzpicture} 

### 2013-06-24 network-science/paper.tex

@@
 \begin{equation}
-c.c=\frac{\#\text{closed paths of len 2}}{\#\text{paths of len 2}},
-\end{equation}
-for a typical social network is a possitive
-number, which means people are more willing to make interactions with close
-related people than unfamiliars.
+c.c=\frac{\#\text{closed paths of length 2}}{\#\text{paths of length 2}},
+\end{equation}
+for a typical social network is a positive number, which means people are more
+willing to make interactions with close related people than unfamiliar ones.
 

### 2013-06-24 network-science/paper.tex

@@
 The quantity of actions for a node over time is a discrete function, so we
-cannot define its deriviation $f(t,v)=\frac{\mathrm{d}}{\mathrm{d}t}k(G_t,v)$
+cannot define its derivation $f(t,v)=\frac{\mathrm{d}}{\mathrm{d}t}k(G_t,v)$
 directly. However, we reverse this property, and let $\int_{-\infty}^t
@@
 of a node in social networks by counting the total number of walks between a pair of
-node. We try to combine the activity and the clasical centrality metric and
+node. We try to combine the activity and the classical centrality metric and
 expect to define a new centrality model that is mode sensitive to immediate
@@
 
-Denote the sum of weights of these new edges by $w(t_i)$, so $z$ decreases to $-\eta w(t_i)$ from 0.
-By the definition of $z$, we write $z$ as the function of $t$, which is $z(t)=t-t_i-\eta w(t_i)$.
-For simplify we choose $\mu=e$ here, it's similar to prove for other values of $\mu$.
-Now the integrity is as follows:
+Denote the sum of weights of these new edges by $w(t_i)$, so $z$ decreases to
+$-\eta w(t_i)$ from 0. By the definition of $z$, we write $z$ as the function
+of $t$, which is $z(t)=t-t_i-\eta w(t_i)$. For simplify we choose $\mu=e$ here,
+it's similar to prove for other values of $\mu$. Now the integrity is as
+follows:
 
@@
 
-Define $f(x)=\int_{-x}^{0} e^{1/t} \mathrm{d}t - \frac{x}{10}$, from $f'(x)=e^{-1/x}-\frac{1}{10}$, at least we can see $f(x)$ increases when $x\ge 1$. So $f(x)\ge f(1)\approx 0.05>0$.
+Define $f(x)=\int_{-x}^{0} e^{1/t} \mathrm{d}t - \frac{x}{10}$, from
+$f'(x)=e^{-1/x}-\frac{1}{10}$, at least we can see $f(x)$ increases when $x\ge
+1$. So $f(x)\ge f(1)\approx 0.05>0$.
 
@@
 
-We show the theorem holds for each "phase", where we call the period of time when $z<0$ a "phase" and a "phase" starts and ends both with $z=0$.
-Consider a "phase" starting from $t_i$ and ending at $t_j$, some edges whose sum of weights is $w(t_k)$ are added to $v$ at time $t_k(i\le k\le j)$, so $z$ decreases from $z(t_k)$ to $z(t_k)-\eta w(t_k)$ sharply.
+We show the theorem holds for each "phase", where we call the period of time
+when $z<0$ a "phase" and a "phase" starts and ends both with $z=0$. Consider a
+"phase" starting from $t_i$ and ending at $t_j$, some edges whose sum of
+weights is $w(t_k)$ are added to $v$ at time $t_k(i\le k\le j)$, so $z$
+decreases from $z(t_k)$ to $z(t_k)-\eta w(t_k)$ sharply.
 
@@
 As for the other direction, notice that at time $t_{k+1}$, there are two cases.
-One is that $z(t_{k+1})$ has increased equal or above $z(t_k)$, namely we can find some $t_k^*\in (t_k, t_{k+1})$, where $t_k^*$ is defined to satisfy that $z(t_k)=z(t_k^*)$ for all $k$.
-So we have
-\begin{equation}
+One is that $z(t_{k+1})$ has increased equal or above $z(t_k)$, namely we can
+find some $t_k^*\in (t_k, t_{k+1})$, where $t_k^*$ is defined to satisfy that
+$z(t_k)=z(t_k^*)$ for all $k$. So we have \begin{equation}
 \int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t)}} \mathrm{d}t \ge \int_{t_k}^{t_k^*}
@@
 \end{equation}
-The other case is that $z(t_{k+1})$ is still less than $z(t_{k})$, in other words, we will find $t_k^*>t_{k+1}$.
+The other case is that $z(t_{k+1})$ is still less than $z(t_{k})$, in other
+words, we will find $t_k^*>t_{k+1}$.
 
@@
 z(t_k)+t-t_k&  t\in (t_k, t_{k+1})\\
-z(t_{k+1})+t-t_{k+1}& t\in (t_{k+1}, t_{k+2})
+z(t_{k+1})+t-t_{k+1}& t\in (t_{k+1}, t_{k+2}),
 \end{cases}
 \end{equation}
-
 we have:
@@
 
-\item \textit{father}[$1\dots|V|$], an array exploited by the historicall
+\item \textit{father}[$1\dots|V|$], an array exploited by the historical
 union-find algorithm\cite{tarjan1975efficiency} (a weakened model), which
@@
 \begin{algorithmic}[1]
-\State $\eta\gets\eta'$;\State\Comment{Imcompatible with historical queries.
+\State $\eta\gets\eta'$;\State\Comment{Incompatible with historical queries.
 The alternative is to rebuild the whole graph.}
@@
 \Require $0<\alpha<\lambda_1(A^\bullet(G_t))^{-1}$ and $\beta>0$ and $m>0$. Here
-$\lambda_1(A)$ is the maximal possitive eigenvalue of matrix $A$.
+$\lambda_1(A)$ is the maximal positive eigenvalue of matrix $A$.
 \Ensure return the active centrality $\mathbf{x}(G_t)$.
@@
 \item The time delay of two adjacent new edges is inversely proportional to the
-size of the giant component. So the average activity of any indivitual node do
-not change tremendously.
+size of the giant component. So the average activity of any individual node
+would not change tremendously.
 \end{itemize}

### 2013-06-24 network-science/paper.tex

@@
 node. We try to combine the activity and the classical centrality metric and
-expect to define a new centrality model that is mode sensitive to immediate
+expect to define a new centrality model that is more sensitive to immediate
 effect.
@@
 \item $u$, the identity of $v_i$'s father node if $u>0$, otherwise $v_i$
-is a root node, and $-u$ is the size of the tree.
+is a root node, and $(-u)$ is the size of the tree.
 \item $t$, the time when $u$ becomes non-zero.
@@
 \State $t_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.t$;
+\State $s_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.s$;
 \State $z_2\gets z_2+\mathit{currentTime}-t_2$;
-\State $s_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.s$;
 \If {$z_2>0$} \State $z_2\gets 0$;\EndIf
@@
 \If {$\mathit{father}[i].u>0$ and $\mathit{father}[i].t\leq t$}
-	\State \Return{\Call{FindRoot}{$\mathit{father}[i].u$}};
+	\State \Return{\Call{FindRoot}{$\mathit{father}[i].u$, $t$}};
 \Else
@@
 \State $a[i]\gets \Call{Query Activity}{t,v_i}$;
-\State $d[i]\gets \mathrm{size}(\mathit{edgeListReduced}[i])$;
+\State $k[i]\gets \mathrm{size}(\mathit{edgeListReduced}[i])$;
 \State $\mathbf{x}[i]\gets \mathbf{x}_0[i]$;
@@
 \State $\mathbf{x'}[i]\gets \mathbf{x'}[i]+\alpha\cdot
-a[j]\cdot\mathbf{x}[j]/d[j]$
+a[j]\cdot\mathbf{x}[j]/k[j]$
 \EndFor\EndFor

### 2013-06-24 trunk/network-science/paper.tex

@@
 of a node in social networks by counting the total number of walks between a pair of
-node. We try to combine the activity and the clasical centrality metric and
-expect to define a new centrality model that is mode sensitive to immediate
+node. We try to combine the activity and the classical centrality metric and
+expect to define a new centrality model that is more sensitive to immediate
 effect.
@@
 We have implemented the algorithms using C++ language without compiler
-optimization, and all execution is done under a typical PC with 
+optimization, and all executions are done under a typical PC with 
 Intel (R) Core (TM) i3 CPU M380  @ 2.53GHz, 2GB RAM.
@@
 
-The centrality trace graph for some representative node, when $\mu=4096$ and
+\begin{itemize}
+\item The centrality trace graph for some representative node, when $\mu=4096$ and
 $\eta=1000$:
@@
 \end{tikzpicture} \end{center}
-
+Evolving centrality is smaller then static one, because we applied the
+activity coefficients which is less than $1$. The overall tendency of those
+traces are similar, but the evolving centrality declines more quickly.
 \begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
@@
 \end{tikzpicture} \end{center}
-
-The centrality trace graph for some representative node, when $\mu=2^{20}$ and
+We can observe that two centralities can react quite differently to changes.
+
+\item The centrality trace graph for some representative node, when $\mu=2^{20}$ and
 $\eta=2000$:
@@
 \end{tikzpicture} \end{center}
+By elongating the activity delay, the declination becomes slower for evolving
+centrality. However, it still declines faster than the static one.
 \begin{center} \begin{tikzpicture}[y=.4cm, x=.5cm, font=\sffamily]
@@
 \end{tikzpicture} \end{center}
+We observe a clear concave in evolving centrality from time $12\,000$ to
+$16\,000$. Perhaps the reason for that is the neighbors of the vertex becomes
+less active, despite the static structural centrality is high.
+\end{itemize}
 
@@
 issues that are once very popular. Those fields such as web-page search
-engine[?], ranking of movie actors[?], seeking hot scholar topics, etc.
+engine, ranking of movie actors, seeking hot scholar topics, etc.
 By using evolving centrality, the increment of actions of a node and its
 closely related region will be more notable in increment of its ranking of
-influence, whereas the static centrality is more likely to trigger cascade on
-social preference[?] because people will have less chance to see and rate new
-information. The cascade may prevent high quality information from being
-popular, and even worse, hasten the monopolization in the commercial aspect.
+influence, whereas the static centrality is more likely to trigger
+conformity on social preference\cite{cialdini2004social} because people will
+have less chance to see and rate new information, which may prevent high
+quality information from getting popular, and even worse, hasten the
+monopolization in the commercial
+aspect.
 

### 2014-01-13 trunk/machine-learning/cifar-project/codes/common/lib-matrix.cpp
modify codes

@@ -1,0 +1,1 @@
+#include "lib-matrix.h"

### 2014-01-13 trunk/machine-learning/cifar-project/codes/common/lib-matrix.h

@@ -1,0 +1,199 @@
+#pragma once
+
+#include <cstring>
+#include <cassert>
+#include <iostream>
+#include "common.h"
+
+#pragma warning(disable: 4996)
+
+
+#include "mkl.h"
+#pragma message(" - Linking with mkl_intel_lp64.lib")
+#pragma comment(lib,            "mkl_intel_lp64.lib")	
+
+#pragma message(" - Linking with mkl_intel_thread.lib")
+#pragma comment(lib,            "mkl_intel_thread.lib")	
+
+#pragma message(" - Linking with mkl_solver_lp64.lib")
+#pragma comment(lib,            "mkl_solver_lp64.lib")
+
+#pragma message(" - Linking with mkl_core.lib")
+#pragma comment(lib,            "mkl_core.lib")
+
+#pragma message(" - Linking with libguide.lib")
+#pragma comment(lib,            "libguide.lib")
+
+class matrix
+{
+	double *a;
+	int h, w;
+
+public:
+	matrix()
+	{
+		h = w = 0;
+		a = NULL;
+	}
+
+	bool exists() const
+	{
+		return a != NULL;
+	}
+
+	void copy(const matrix &t)
+	{
+__mat_cnt++;
+		assert(t.a != NULL);
+		h = t.h;
+		w = t.w;
+		//a = new double[h * w];
+		a = (double*)MKL_malloc(h * w * sizeof(double), 64);
+		memmove(a, t.a, sizeof(double) * h * w);
+	}
+
+	double* get_buf() const
+	{
+		return a;
+	}
+
+	double* get_row_buf(int i) const
+	{
+		assert(i >= 0 && i < h);
+		return &a[i * w];
+	}
+
+	void clear()
+	{
+		assert(a != NULL);
+		memset(a, 0, sizeof(double) * h * w);
+	}
+
+	void mult(double c)
+	{
+		assert(a != NULL);
+		for (int i = 0; i < h * w; ++i)
+			a[i] *= c;
+	}
+
+	void create(int h, int w)
+	{
+__mat_cnt++;
+		assert(a == NULL);
+		this->h = h;
+		this->w = w;
+		//a = new double[h * w];
+		a = (double*)MKL_malloc(h * w * sizeof(double), 64);
+		memset(a, 0, sizeof(double) * h * w);
+	}
+
+	void free()
+	{
[…]

### 2014-01-13 trunk/machine-learning/cifar-project/codes/mk-kmeans/mk-kmeans.cpp

@@ -1,0 +1,724 @@
+#include <cstdlib>
+#include <cstdio>
+#include <ctime>
+#include "../common/common.h"
+#include "../common/lib-matrix.h"
+#include "../common/lib-image.h"
+#include "rica.h"
+#include "mk-centroids.h"
+#include <Windows.h>
+using namespace std;
+
+#include "mpi.h"
+#pragma comment(lib, "msmpi.lib")
+
+#define _USE_LOG_FILE
+//#define _PSEUDO_RAND
+
+
+void autoenc_save_patches(const mk_config &config, matrix &patches)
+{
+	assert(config.learn_proc == LPROC_AUTOENC);
+
+	int patch_n = patches.rows();
+	int patch_size = patches.cols();
+	string fname_whitening = config.cen_file + "-whitening.txt";
+	string fname_patch_bin = config.cen_file + "-patches.bin";
+	string fname_patch_txt = config.cen_file + "-patches.txt";
+
+	// Normalize Patches
+	printf("save_patches: normalizing patches...\n"); fflush(stdout);
+	printf("  - memory: %.3lf GB\n", system_info().memory()); fflush(stdout);
+	for (int i = 0; i < patch_n; ++i)
+		normalize_patch(patches.get_row_buf(i), patch_size);
+	printf("  - memory: %.3lf GB\n", system_info().memory()); fflush(stdout);
+	printf("\n");
+
+	// Whitening
+	printf("save_patches: whitening...\n"); fflush(stdout);
+	printf("  - memory: %.3lf GB\n", system_info().memory()); fflush(stdout);
+	mk_centroids centroids(config.learn_proc);
+	centroids.initialize();
+	if (config.whitening) {
+		if (!centroids.run_whitening(patches))
+			assert(false);
+		printf("waiting...\n"); fflush(stdout);
+		printf("  - memory: %.3lf GB\n", system_info().memory()); fflush(stdout);
+		MPI_Barrier(MPI_COMM_WORLD);
+		printf("save_patches: all finished whitening.\n"); fflush(stdout);
+		printf("\n");
+	} else {
+		printf("save_patches: well i do not need whitening~\n"); fflush(stdout);
+		printf("\n");
+	}
+	
+	if (config.rank == 0) {
[…]

### 2014-01-13 machine-learning/cifar-project/codes/common/common.cpp
modify codes

@@ -1,0 +1,239 @@
+#include "common.h"
+#include <Windows.h>
+#include <cassert>
+#include <cstdio>
+using namespace std;
+
+int images_per_thread;
+int __mat_cnt;
+
+string str_extr_ext(string fname)
+{
+	string s = "";
+	for (int i = 0; i < (int)fname.size(); ++i) {
+		if (fname[i] == '.')
+			s = ".";
+		else
+			s = s + fname[i];
+	}
+	if (s.size() > 0 && s[0] != '.')
+		s = "";
+	return s;
+}
+
+double sqr(double x)
+{
+	return x * x;
+}
+
+double randn()
+{
+	double x1, x2, w, y1;
+	do {
+		x1 = 2.0 * (double)rand()/RAND_MAX - 1.0;
+		x2 = 2.0 * (double)rand()/RAND_MAX - 1.0;
+		w = x1 * x1 + x2 * x2;
+	} while (w >= 1.0);
+	w = sqrt((-2.0 * log(w)) / w);
+	y1 = x1 * w;
+	return y1;
+}
+
+string i_to_s(int x)
+{
+	char buf[99];
+	sprintf(buf, "%d", x);
+	return string(buf);
+}
+
+string read_ini_str(string ini_file, string section, string key, string def_val)
+{
+	char buf[MAX_PATH];
+	GetPrivateProfileString(section.c_str(), key.c_str(), def_val.c_str(),
+		buf, MAX_PATH, ini_file.c_str());
+	//printf("ini=%s sec=%s key=%s buf=%s\n",ini_file.c_str(),section.c_str(),key.c_str(),def_val.c_str());
+	return string(buf);
+}
+
+int read_ini_int(string ini_file, string section, string key, int def_val)
+{
+	int v = GetPrivateProfileInt(section.c_str(), key.c_str(), def_val, ini_file.c_str());
+	return v;
+}
+
+double read_ini_double(string ini_file, string section, string key, string def_val)
+{
+	char buf[MAX_PATH];
+	GetPrivateProfileString(section.c_str(), key.c_str(), def_val.c_str(),
+		buf, MAX_PATH, ini_file.c_str());
+	return atof(buf);
+}
+
+void write_ini_int(string ini_file, string section, string key, int val)
+{
+	char buf[99];
+	sprintf(buf, " %d", val);
+	WritePrivateProfileString(section.c_str(), key.c_str(), buf, ini_file.c_str());
+}
+
[…]

### 2014-01-13 machine-learning/cifar-project/codes/common/common.h

@@ -1,0 +1,191 @@
+#pragma once
+#include <cstdlib>
+#include <string>
+#include <vector>
+#include <ctime>
+#include <cassert>
+#include <iostream>
+#include <algorithm>
+#include <Windows.h>
+#include <psapi.h>
+
+#pragma warning(disable: 4996)
+#pragma comment(lib, "psapi.lib")
+
+typedef long long LL;
+
+std::string str_extr_ext(std::string fname);
+
+bool load_image_list(std::string file_name, int size, int rank, std::vector<std::string> &list, bool _keep_whole = false);
+std::string i_to_s(int x);
+
+double randn();
+double sqr(double x);
+
+extern int images_per_thread;
+
+extern int __mat_cnt;
+
+
+struct mk_config
+{
+	// MPI
+	int size, rank;
+
+	// Common
+	std::string path;
+	std::string log_path;
+	int log_count;
+	int io_limit;
+	std::string learn_proc; // KMeans/Rica
+	//int extr_bin;
+
+	// KMeans
+	std::string kmeans_imgpath;
+	std::string kmeans_imglst;
+	std::string kmeans_lablst;
+	std::string cen_file;
+	int cen_round_src;
+	int cen_round_tar;
+	//int max_scale;
+	int patch_num;
+	int rf_size;
+	int centroid_num;
+	int mil_neg_cen;
+	int whitening;
+	int kmeans_iterations;
+	int kmeans_batch;
+
+	// Rica
+	double rica_lambda;
+	double rica_epsilon;
+	int rica_max_iterations;
+	double rica_lbfgs_ftol;
+	double rica_lbfgs_epsilon;
+
+	// Extract
+	int ext_cub_pool;
+	int ext_fea_pool;
+	int ext_largeimg_d;
+	int ext_largeimg_w;
+	std::string ext_field;
+	std::string extract_imgpath;
+	std::string extract_imglst;
+	std::string extract_lablst;
+	std::string fea_list;
+	std::string fea_file;
+	std::string fea_folder;
+
+	mk_config() : ext_field("") {}
+	//mk_config(std::string ext_field) : ext_field(ext_field) {}
+
+	bool load_from_ini(std::string ini_file, int size, int rank);
[…]

### 2014-01-13 machine-learning/cifar-project/codes/common/lib-image.h

@@ -1,0 +1,323 @@
+#pragma once
+
+#include "lib-image.h"
+#include "opencv\cv.h"
+#include "opencv\highgui.h"
+#include <vector>
+#include <cassert>
+#include <direct.h>
+using namespace cv;
+
+#pragma comment(lib, "opencv_core242.lib")
+#pragma comment(lib, "opencv_imgproc242.lib")
+#pragma comment(lib, "opencv_highgui242.lib")
+#pragma comment(lib, "opencv_objdetect242.lib")
+#pragma comment(lib, "opencv_features2d242.lib")
+
+
+
+class cuboid
+{
+	double ***a;
+	int h, w, d;
+public:
+	static int __cub_cur;
+
+	double __get(int i, int j, int k) const
+	{
+		return a[i][j][k];
+	}
+	cuboid()
+	{
+		h = w = d = 0;
+		a = NULL;
+	}
+	void create(int rows, int cols, int len)
+	{
+++__cub_cur;
+		assert(a == NULL);
+		h = rows;
+		w = cols;
+		d = len;
+		a = new double**[rows];
+		//a = (double***)malloc(sizeof(double**) * rows);
+		for (int i = 0; i < rows; ++i) {
+			a[i] = new double*[cols];
+			//a[i] = (double**)malloc(sizeof(double*) * cols);
+			for (int j = 0; j < cols; ++j) {
+				a[i][j] = new double[len];
+				//a[i][j] = (double*)malloc(sizeof(double) * len);
+				memset(a[i][j], 0, sizeof(double) * len);
+			}
+		}
+	}
+	/*
+	void create_empty(int rows, int cols)
+	{
+		assert(a == NULL);
+		h = rows;
+		w = cols;
+		d = 0;
+		//a = new double**[rows];
+		a = (double***)malloc(sizeof(double**) * rows);
+		for (int i = 0; i < rows; ++i) {
+			//a[i] = new double*[cols];
+			a[i] = (double**)malloc(sizeof(double*) * cols);
+			for (int j = 0; j < cols; ++j)
+				a[i][j] = NULL;
+		}
+	}
+	*/
+	void pool_from(const cuboid &cub, int p)
+	{
+		assert(a == NULL);
+		int ph = (cub.rows() - 1) / p + 1;
+		int pw = (cub.cols() - 1) / p + 1;
+		create(p, p, cub.len());
[…]

### 2014-01-13 machine-learning/cifar-project/codes/mk-extract/mk-extract.cpp

@@ -1,0 +1,704 @@
+#include <cstdlib>
+#include <cstdio>
+#include <ctime>
+#include <mkl.h>
+#include "..\common\common.h"
+#include "..\common\lib-matrix.h"
+#include "..\common\lib-image.h"
+#include "..\mk-kmeans\mk-centroids.h"
+#include <Windows.h>
+#include <set>
+using namespace std;
+
+#include "mpi.h"
+#pragma comment(lib, "msmpi.lib")
+
+#define _USE_LOG_FILE
+
+const int MAX_THREAD_N = 8;
+int THREAD_N = MAX_THREAD_N;
+double min_memory;
+
+FILE *global_log;
+
+//int matrix::__cnt = 0;
+
+
+bool extract_feature(const cuboid &img, const mk_config &config, const mk_centroids &centroids, cuboid &cub)
+{
+	printf("    extract_feature img=(%d, %d) cen_n=%d...\n", img.rows(), img.cols(), config.centroid_num); fflush(stdout);
+	printf("       - memory: %.3lf GB\n", system_info().memory()); fflush(stdout);
+	// Initialize
+	int rf_size = config.rf_size;
+	int patch_size = rf_size * rf_size * img.len();
+	int centroid_n = config.centroid_num;
+	
+	int rows = img.rows() - rf_size + 1;
+	int cols = img.cols() - rf_size + 1;
+	int num = rows * cols;
+
+	// Extract Patches
+	//printf("    extract: make patches...\n"); fflush(stdout);
+	matrix patches;
+	patches.create(num, patch_size);
+	for (int x = 0; x < rows; ++x)
+		for (int y = 0; y < cols; ++y) {
+			int i = x * cols + y;
+			img.extract_patch(x, y, rf_size, patches.get_row_buf(i));
+			//if (config.learn_proc == LPROC_KMEANS || config.learn_proc == LPROC_RICA)
+			normalize_patch(patches.get_row_buf(i), patch_size);
+		}
+	printf("     - finished extracting - memory: %.3lf GB\n", system_info().memory()); fflush(stdout);
+
+	// Whitening
+	if (config.whitening) {
+		//printf("    extract: whitening patches...\n");
+		_timer timer;
+		centroids.do_whitening(patches);
+		//printf("    whitening time: %s\n", timer.total());
[…]

### 2014-01-13 machine-learning/cifar-project/codes/mk-kmeans/mk-centroids.cpp

@@ -1,0 +1,363 @@
+#include "mk-centroids.h"
+using namespace std;
+
+
+mk_centroids::mk_centroids(string learn_proc)
+{
+	this->learn_proc = learn_proc;
+}
+
+
+void mk_centroids::initialize()
+{
+	whitening = 0;
+	inds.clear();
+	cens.clear();
+}
+
+
+void mk_centroids::save(std::string fname) const
+{
+	printf("\n");
+	printf("mk_centroids: saving...\n"); fflush(stdout);
+
+	if (learn_proc == LPROC_KMEANS || learn_proc == LPROC_RICA) {
+		FILE *f = fopen(fname.c_str(), "w");
+		assert(f != NULL);
+	
+		fprintf(f, "%d\n", whitening);
+		fprintf(f, "\n");
+		if (whitening) {
+			M.write(f);
+			P.write(f);
+		}
+		fprintf(f, "\n");
+		fprintf(f, "%d\n", inds.size());
+		fprintf(f, "\n");
+		for (size_t i = 0; i < inds.size(); ++i) {
+			fprintf(f, "%d\n", inds[i].size());
+			for (size_t j = 0; j < inds[i].size(); ++j)
+				fprintf(f, "%d ", inds[i][j]);
+			fprintf(f, "\n");
+			cens[i].write(f);
+		}
+		fclose(f);
+	}
+	if (learn_proc == LPROC_AUTOENC) {
+		FILE *f = fopen(fname.c_str(), "w");
+		assert(f != NULL);
+		fprintf(f, "%d\n", whitening);
+		fprintf(f, "\n");
+		if (whitening) {
+			M.write(f);
+			P.write(f);
+		}
+		fclose(f);
+	//	printf("CANNOT Save centroids with learn_proc = %s!!!\n", LPROC_AUTOENC.c_str());
+	}
+}
+
+
+bool mk_centroids::load(std::string fname)
+{
+	printf("mk_centroids: loading...\n"); fflush(stdout);
+
+	if (learn_proc == LPROC_KMEANS || learn_proc == LPROC_RICA) {
+		FILE *f = fopen(fname.c_str(), "r");
+		if (f == NULL)
+			return false;
+		fscanf(f, "%d", &whitening);
+		if (whitening) {
+			M.read(f);
+			P.read(f);
+		}
+		int n;
+		fscanf(f, "%d", &n);
+		inds.resize(n);
+		cens.resize(n);
[…]

### 2014-01-13 machine-learning/cifar-project/codes/mk-kmeans/mk-centroids.h

@@ -1,0 +1,109 @@
+#pragma once
+#include <string>
+#include <vector>
+#include "..\common\common.h"
+#include "..\common\lib-matrix.h"
+
+
+#include "mpi.h"
+#pragma comment(lib, "msmpi.lib")
+
+
+const std::string LPROC_KMEANS = "KMeans";
+const std::string LPROC_RICA = "Rica";
+const std::string LPROC_AUTOENC = "AutoEnc";
+
+
+class mk_centroids
+{
+	std::string learn_proc;
+
+	int whitening;
+	matrix M, P;
+	std::vector<std::vector<int> > inds;
+	std::vector<matrix> cens;
+
+	int ae_layers;
+	std::vector<matrix> ae_w, ae_b;
+
+	void map_comm(std::string learn_proc, matrix &patches) const;
+	void map_autoenc(std::string learn_proc, matrix &patches) const;
+public:
+	mk_centroids(std::string learn_proc);
+	void initialize();
+	void save(std::string fname) const;
+	bool load(std::string fname);
+	bool run_whitening(matrix &patches);
+	void do_whitening(matrix &patches) const;
+	void add(const std::vector<int> &ind, const matrix &cen);
+	void map(std::string learn_proc, matrix &patches) const;
+};
+
+
+//	if (config.learn_proc == "KMeans") {
+//	} else if (config.learn_proc == "Rica") {
+//		// !!!!!!!!!!!!!!!!!!!!!
+//		// !!!!!!!!!!!!!!!!!!!!!
+//		// !!!!!!!!!!!!!!!!!!!!!
+//	} else {
+//		printf("Cannot find learn_proc %s!\n", config.learn_proc.c_str());
+//	}
+
+
+
+
+
+
+//bool load_data(const mk_config &config, matrix &centroids_T, matrix &w_M, matrix &w_P)
+//{
+//	// Lock It: allow only io_limit threads to read at the same time
+//	int flag;
+//	MPI_Status status;
+//	if (config.rank >= config.io_limit)		
+//		MPI_Recv(&flag, 1, MPI_INT, config.rank - config.io_limit, 0, MPI_COMM_WORLD, &status);
+//
+//	FILE *f = fopen(config.cen_file.c_str(), "r");
+//	if (f == NULL) {
+//		printf("cannot open cen_file!\n");
+//		return false;
+//	}
+//	int centroid_n;
+//	int patch_size;
[…]

### 2014-01-13 machine-learning/cifar-project/codes/mk-kmeans/rica.cpp

@@ -1,0 +1,348 @@
+#include "rica.h"
+
+namespace rica
+{
+
+matrix	patches;
+int patch_n;
+int patch_size;
+int centroid_n;
+double lambda;
+double epsilon;
+int rank;
+int size;
+
+double sqr(double x)
+{
+	return x * x;
+}
+
+matrix inverse(matrix& M)
+{
+	matrix MT;
+
+	MT.create(M.cols(),M.rows());
+	for(int i=0;i<M.rows();i++)
+		for(int j=0;j<M.cols();j++)
+			MT.val(j,i)=M.val(i,j);
+	
+	return MT;
+}
+
+bool rica_proc(const mk_config &config, matrix &patches, matrix &centroids)
+{
+	lbfgs_parameter_t param;
+	int ret;
+	double fx;
+
+	printf("initializing rica...\n");fflush(stdout);
+
+	srand((unsigned)time(NULL));
+//	srand(1);
+
+	lbfgs_parameter_init(&param);
+
+	patch_n = patches.rows();
+	patch_size = patches.cols();
+	centroid_n = config.centroid_num;
+	lambda = config.rica_lambda;
+	epsilon = config.rica_epsilon;
+	rank=config.rank;
+	size=config.size;
+
+	param.max_iterations = config.rica_max_iterations;
+	param.ftol=config.rica_lbfgs_ftol;
+	param.epsilon=config.rica_lbfgs_epsilon;
+//	param.m=100;
+//	param.linesearch=LBFGS_LINESEARCH_BACKTRACKING_STRONG_WOLFE;
+//	param.max_step=1;
+
+	rica::patches=inverse(patches);
+	
+	for(int i=0;i<(rica::patches).cols();i++)
+	{	
+		double sum=0;
+		for(int j=0;j<(rica::patches).rows();j++)
+			sum+=sqr((rica::patches).val(j,i));
+		sum=sqrt(sum+1e-8);
+		for(int j=0;j<(rica::patches).rows();j++)
+			(rica::patches).val(j,i)/=sum;
+	}
+		
+
+	centroids.create(centroid_n, patch_size);
+
+	printf("generating initial solution...\n");fflush(stdout);
+	
+	if(rank==0)
+	{
+		for(int i=0;i<centroid_n;i++)
+		{
[…]

### 2014-01-13 machine-learning/cifar-project/codes/mk-kmeans/rica.h

@@ -1,0 +1,51 @@
+#include "..\common\lib-matrix.h"
+#include "..\common\common.h"
+#include <stdio.h>
+#include <lbfgs.h>
+#include <cmath>
+#include "mpi.h"
+
+namespace rica
+{
+	extern	matrix	patches;
+	extern	int patch_n;
+	extern	int patch_size;
+	extern	int centroid_n;
+	extern	double lambda;
+	extern	double epsilon;
+
+	double sqr(double x);
+	matrix inverse(matrix& M);
+	bool rica_proc(const mk_config &config, matrix &patches, matrix &centroids);
+	void l2rowscaledg(matrix &x, matrix &y, matrix &outderv,double alpha);
+	void l2rowscaled(matrix &x, double alpha);
+	
+	static lbfgsfloatval_t softICACost(
+    void *instance,
+    const lbfgsfloatval_t *theta,
+    lbfgsfloatval_t *g,
+    const int n,
+    const lbfgsfloatval_t step
+    );
+
+	static int progress(
+    void *instance,
+    const lbfgsfloatval_t *x,
+    const lbfgsfloatval_t *g,
+    const lbfgsfloatval_t fx,
+    const lbfgsfloatval_t xnorm,
+    const lbfgsfloatval_t gnorm,
+    const lbfgsfloatval_t step,
+    int n,
+    int k,
+    int ls
+    );
+
+	lbfgsfloatval_t debug_softICACost(
+    void *instance,
+    const lbfgsfloatval_t *theta,
+    lbfgsfloatval_t *g,
+    const int n,
+    const lbfgsfloatval_t step
+    );
+}

### 2014-01-13 machine-learning/cifar-project/report/report.tex
add report

\documentclass[12pt,abstract=true]{scrartcl}

\usepackage{tikz}
\usepackage{array}
\usepackage{pifont}
\usepackage{engord}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[plain]{fancyref}
\usepackage[unicode]{hyperref}
\usepackage{graphicx,tabularx}
\usepackage[shortlabels]{enumitem}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{amsmath,amssymb,amsthm,amscd,amstext}
\usepackage{mathtools}
\usepackage{exscale}
\usepackage{relsize}
\usepackage{mathrsfs}
\usepackage{tocloft}

\usepackage{setspace}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}

\usepackage{charter}

%\pgfplotsset{compat=1.6}
\usetikzlibrary{arrows}
\usetikzlibrary{patterns}
\usetikzlibrary{positioning}
\usetikzlibrary{automata}
\usetikzlibrary{plotmarks}
\usepackage{tikz-3dplot}

\tikzset{ alert/.style={ very thick, draw=red!80, fill=red!20 } }
\tikzset{ fancy/.style={ very thick, draw=blue!80, fill=blue!20 } }
\tikzset{
  dot/.style={
    very thick,circle,draw=black,fill=black,inner sep=0,minimum size=5pt
  }
}
\tikzset { every state/.style={fancy} }
\tikzset {
  general/.style = {
    shorten >=2pt, node distance=2.5cm, on grid, thick,>=stealth', auto
  }
}
\newcommand{\mathhuge}[1]{\mathlarger{\mathlarger{\mathlarger{#1}}}}
\newcommand{\mathtiny}[1]{\mathsmaller{\mathlarger{\mathlarger{#1}}}}

\renewcommand\cftsecfont{\normalsize}
\renewcommand\cftsecpagefont{\normalsize}
\renewcommand\cftsecafterpnum{\par}
\setlength{\cftbeforesecskip}{0.2em}

\renewcommand\cftsubsecfont{\small}
\renewcommand\cftsubsecpagefont{\small}
\renewcommand\cftsubsecafterpnum{\par}

\newcommand\upper[1]{\textsuperscript#1}
\numberwithin{equation}{section}
\mathtoolsset{centercolon}
\bibliographystyle{plain}

% Theorem environment <<<
\theoremstyle{definition}   \newtheorem{definition}{Definition}[section]
\theoremstyle{plain}        \newtheorem{theorem}{Theorem}[section]
\theoremstyle{plain}        \newtheorem{observation}{Observation}[section]
\theoremstyle{plain}        \newtheorem{fact}{Fact}[section]
\theoremstyle{plain}        \newtheorem{claim}{Claim}[section]
\theoremstyle{plain}        \newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{plain}        \newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{remark}       \newtheorem{example}{Example}[section]
\theoremstyle{remark}       \newtheorem{remark}{Remark}[section]
\newcommand*{\fancyrefdeflabelprefix}{def}
\newcommand*{\fancyrefthmlabelprefix}{thm}
\newcommand*{\fancyreflemlabelprefix}{lem}
\newcommand*{\fancyrefcorlabelprefix}{cor}
\newcommand*{\fancyrefalglabelprefix}{alg}
\newcommand*{\fancyreflnlabelprefix}{ln}
\frefformat{plain}{\fancyreflnlabelprefix}{line #1}
\Frefformat{plain}{\fancyreflnlabelprefix}{Line #1}
\frefformat{plain}{\fancyrefalglabelprefix}{algorithm (#1)}
\Frefformat{plain}{\fancyrefalglabelprefix}{Algorithm (#1)}
\frefformat{plain}{\fancyrefdeflabelprefix}{definition (#1)}
\Frefformat{plain}{\fancyrefdeflabelprefix}{Definition (#1)}
\frefformat{plain}{\fancyrefthmlabelprefix}{theorem (#1)}
\Frefformat{plain}{\fancyrefthmlabelprefix}{Theorem (#1)}
\frefformat{plain}{\fancyreflemlabelprefix}{lemma (#1)}
\Frefformat{plain}{\fancyreflemlabelprefix}{Lemma (#1)}
\frefformat{plain}{\fancyrefcorlabelprefix}{corollary (#1)}
\Frefformat{plain}{\fancyrefcorlabelprefix}{Corollary (#1)}
%>>>
% Alter some LaTeX Float for better treatment of figures: <<<
% See p.105 of "TeX Unbound" for suggested values.
% See pp. 199-200 of Lamport's "LaTeX" book for details.
%   General parameters, for ALL pages:
\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages

\newcommand{\scorebest}{$83.59\%$}
\newcommand{\scorebasic}{$78.37\%$}
\newcommand{\rankbest}{$9$}

\allowdisplaybreaks[4]

\begin{document}

\begin{center} %<<< Title
	\textsc{
		\LARGE Machine Learning Project Report
	} \\[1em]

	\textrm{
		{\Large CIFAR-10}
	} \\[2em]

	\textit{
		Kaggle ID: bug-fixer
	} \\[1em]

	\normalsize 
		Yuxing Zhang\upper{1}, Qipeng Liu\upper{2},
		Yuan Deng\upper{3},	Qiwei Feng\upper{4}\\[1.5em]
	\small
	\begin{tabular}{*{2}{>{\centering}p{.32\textwidth}}}
		\upper{1}\small\href{mailto:saintmakarovski@gmail.com}{saintmakarovski@gmail.com} &%
		\upper{2}\href{mailto:lqp1831@gmail.com}{lqp1831@gmail.com}
		\tabularnewline
		\tabularnewline
		\upper{3}\href{mailto:deng1227yuan@163.com}{deng1227yuan@163.com} &
		\upper{4}\href{mailto:caiwaifung@gmail.com}{caiwaifung@gmail.com} 
		%\upper{4}\href{mailto:lqp1831@gmail.com}{lqp1831@gmail.com}% \tabularnewline
	\end{tabular} \\[1.5em]

	\normalsize Institute for Interdisciplinary Information Sciences,
	Tsinghua University \\[2em]

	\normalsize
\end{center} \par %>>>

\tableofcontents
\newpage

\section{Introduction}
	We worked on the CIFAR-10 competetion on
		\href{http://www.kaggle.com/c/cifar-10}{www.kaggle.com}.
	A series of algorithms were used by us and we get the best result of \scorebest,
		which toke the \rankbest-th place on Kaggle.
	(Here is a link of the
		\href{http://www.kaggle.com/c/cifar-10/leaderboard}{ranklist}.)

	The main method we use is K-Means clustering.
	We use linear SVM for later model training and query answering.
	We also use a lot of libraries to accelerate our program.
	The details of the project would be discuss in later sections.

	\subsection{About Makarovski}
		Well I think that you should notice Makarovski.
		{\color{red}TODO: Mention some junk!}

\section{Algorithms}

	\subsection{K-Means Clustering}
		{\color{red}TODO: Mention classical K-Means algorithm!}

	\subsection{Feature Extracting}
		The algorithm we used to extracting features is nearly the same
			as A. Coates done in his 2010 NIPS paper \cite{singlelayer}.
		It contains two parts.
		First, we would calculate the "centroids" of the pictures by extracting
			random patches from them and run K-Means on these patches.
		Second, we would compute the feature vector of each picture using the centroids.
		After these, we can get the features of all picture and we can label them for furthur usage.

		We define a patch as a $d*d$ sub-picture of a large $h*w$ picture
			(then the picture has $(h-d+1)*(w-d+1)$ patches totally).
		For a three-channel (RGB) picture, a patch of it can be described as a vector in $R^{3d^2}$.
		First step of the algorithm is to generate the "centroids" of the data set.
		A centroid is also a vector in $R^{3d^2}$ and the centroids are the
			"most common patches" in all the pictures.
		We randomly extract $n$ patches from the picture set to get matrix $P$,
			and then run the K-Means process to generate $k$ centroids $C_1,...,C_k$.
		The K-Means algorithm contains $t$ iterations.
		In each iteration, we just find the closest centroid for each patch in $P$,
			then assign the patch to the centroid.
		For each centroid $C_i$,
			we take all patches that assigned to this centroid in the current iteration,
			and modify the centroid into a new one $C'_i$ which is the mean of all these patches.
		After running such iteration for $t$ rounds,
			our centroids are supposed to well described the 'common features' of the patches.

		Next, we can extract feature from a picture using the centroids.
		Suppose the picture has dimension of $h*w$.
		Know that it has $(h-d+1)*(w-d+1)$ patches.
		For one patch $p\in R^{3d^2}$, we can map it to a $R^k$ vector $f(p)$,
		where
			$$ f_i(p) = \max \{0, \mu - z_i\}, $$
		and $z_i = ||p-C^{(i)}||_2$, $\mu = (\sum_i z_i) / k$.
		Thus we have $(h-d+1)*(w-d+1)$ vectors of dimension $k$.
		We just divide the $(h-d+1)*(w-d+1)$ grids into four equal parts,
			each contains $(h-d+1)*(w-d+1)/4$ grids.
		By summing up all the vectors in each part,
			we get $4$ vectors in $R^k$ which can be merge into a $4k$-dimension vector.
		This vector is used as the feature of this picture.

	\subsection{SVM Classifier}
		{\color{red}TODO: Mention some junk!}

\section{Implements}

	\subsection{Feature Extracting}
		All codes for feature extracting are written in C++.
		The codes are shown in /codes/.
		We use a lot of libraries including MKL (Intel Math Kernel Library)
			for matrix multiplying and eigen-value calculating,
			and OpenCV for image processing.
		Moreover, we use MPI as the framework of the project
			in order to run the algorithm parallelly.

		\subsubsection{MPI Framework}
			The Message Passing Interface Standard (MPI) is a message passing library standard.
			We used Microsoft MPI (MS-MPI),
				which is a Microsoft implementation of the MPI standard,
				to develop and runn parallel applications on the Windows platform.
			For the K-Means clustering part,
				we communicate between nodes while summing the centroid matrix,
				thus the centroids can be calculating quickly.
			For the feature extracting part,
				we just assign the extracting tasks to each node
				and then the nodes extract them respectively.
			The parallel implementation truly accelerate the program.
			It took us about half an hour to get the features,
				while it takes days if only one machine is used.

		\subsubsection{MKL Library}
			The Intel Math Kernel Library (MKL) is a
				fast and widely used math library for Intel and compatible processors.
			We use this library for matrix multiplication and computing eigen-vectors.
			It is so fast that it takes only about $1/50$ times of hand-written version.
			Since we have met a lot of problems	while using this library,
				it is still a good tool for basic math computations.

	\subsection{SVM Training and Testing}
		All our SVM codes are written in MATLAB.
		The code are written by standford as demo of their papers \cite{rf}\cite{singlelayer}.
		It just write a loss function and use the minFunc library
			to minimize the function,
			thus get the support vectors as the model.
		Since CIFAR-10 has 10 categories,
			it just train $\binom{10}{2}$ 1-vs-1 models
			in order to get the most-possible label for a picture.
		MATLAB use MKL as its kernel thus it is fast and reliable.
		We like it.

\section{Results}
	\subsection{Most Basic Results}
		We run the code and train SVM with $C\in[1,100000]$,
			and get results from $70\%$ to about $78\%$.
		In this short range,
			the performance increase when $C$ increase.
		The best result, \scorebasic, comes from $C=100000$.

	\subsection{Major Results}
		Since we have run the codes for several times with different parameters,
			we get a number of result lists.
		An idea is that, for a test picture, we can get the major answer from
			these basic answers.
		We do this and adjust some parameters, and get our
			best result, \scorebest.

\section{Conclusion}
		{\color{red}TODO: Mention some junk!}

\bibliography{report}
\end{document}

### 2014-01-14 machine-learning/cifar-project/report/report.tex
mod reports

@@
 \usepackage[shortlabels]{enumitem}
-\usepackage[retainorgcmds]{IEEEtrantools}
+%\usepackage[retainorgcmds]{IEEEtrantools}
 \usepackage{amsmath,amssymb,amsthm,amscd,amstext}
@@
 
-	\subsection{About Makarovski}
-		Well I think that you should notice Makarovski.
-		{\color{red}TODO: Mention some junk!}
+	%\subsection{About Makarovski}
+		%Well I think that you should notice Makarovski.
+		%{\color{red}TODO: Mention some junk!}
 
@@
 	\subsection{K-Means Clustering}
-		{\color{red}TODO: Mention classical K-Means algorithm!}
+		K-means clustering is a method of vector quantization, originally from signal processing, that is popular for cluster analysis in data mining. k-means
+        clustering aims to partition n observations into k clusters in which each observation belongs to the cluster with the nearest mean, serving as a prototype of the cluster.
 
@@
 	\subsection{SVM Classifier}
-		{\color{red}TODO: Mention some junk!}
+		In machine learning, support vector machines (SVMs, also support vector networks) are supervised learning models with associated learning algorithms
+        that analyze data and recognize patterns, used for classification and regression analysis.
+Given a set of training examples, each marked as belonging to one of two categories, an SVM training algorithm builds a model that assigns new examples into one category or the other, making it a non-probabilistic binary linear classifier.
 
@@
 
-\section{Conclusion}
-		{\color{red}TODO: Mention some junk!}
+%\section{Conclusion}
+		%{\color{red}TODO: Mention some junk!}
 

### 2014-01-14 trunk/ray-tracing/fqw-mesh-simplifier/simplifier.cpp
add mesh simplifier

@@ -1,0 +1,333 @@
+#include <algorithm>
+#include <sstream>
+#include <cstring>
+#include <cstdio>
+#include <vector>
+#include <cmath>
+using namespace std;
+
+#define MAX_LINE_CHARS 512
+
+inline double GetCostLimit(int meshes, double min_cost) {
+	/*
+	   if (min_cost <= 0) {
+	   printf("min_cost = %.9lf <= 0!\n", min_cost);
+	   return 1E-6;
+	   }*/
+	if (meshes > 100000) return 5.0 * min_cost;
+	if (meshes > 10000) return 2.0 * min_cost;
+	if (meshes > 5000) return 1.5 * min_cost;
+	if (meshes > 1000) return 1.2 * min_cost;
+	return (1.0 + 1E-6) * min_cost;
+}
+
+struct Point {
+	double x, y, z;
+	Point(double x = 0.0, double y = 0.0, double z = 0.0) :
+		x(x), y(y), z(z) { }
+	friend Point operator *(const Point &p, double a) {
+		return Point(p.x*a, p.y*a, p.z*a);
+	}
+	friend Point operator +(const Point &p1, const Point &p2) {
+		return Point(p1.x+p2.x, p1.y+p2.y, p1.z+p2.z);
+	}
+	friend Point operator -(const Point &p1, const Point &p2) {
+		return Point(p1.x-p2.x, p1.y-p2.y, p1.z-p2.z);
+	}
+	friend Point Cross(const Point &p1, const Point &p2) {
+		return Point(p1.y*p2.z-p1.z*p2.y, p1.z*p2.x-p1.x*p2.z, p1.x*p2.y-p1.y*p2.x);
+	}
+};
+
+struct Mesh {
+	int i[3];
+};
+
+struct Matrix4 {
+	double a[4][4];
+	void Clear() {
+		for (int i = 0; i < 4; ++ i)
+			for (int j = 0; j < 4; ++ j)
+				a[i][j] = 0.0;
+	}
+	void Add(const Matrix4 &tmp) {
+		for (int i = 0; i < 4; ++ i)
+			for (int j = 0; j < 4; ++ j)
+				a[i][j] += tmp.a[i][j];	
+	}
+};
+
+struct Vector4 {
+	double a[4];
+	void Clear() {
+		a[0] = a[1] = a[2] = a[3] = 0.0;
+	}
[…]
